---
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  word_document: default
---

```{r setup, include=FALSE}
library(here)
library(huxtable)
library(tidyverse)
library(fs)
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
# Set a root directory for all chunks to be evaluated relative to rather than the document location
knitr::opts_knit$set(root.dir = here())
```

```{r source, include=FALSE}
here("DataBook", "Modules", "BiochemicalMeasurements") %>% 
  # list all R files in the directory
  fs::dir_ls(regexp = "\\.R$") %>% 
  # scale up to all R files with a map function from purrr
  map(source, encoding = "UTF-8", local = knitr::knit_global())
```

---
title: "`r set_title`"
author: "`r set_author`"
---


# Biochemical Measurements

**Mean fasting blood glucose**

Description: mean fasting blood glucose results including those currently on medication for diabetes (non-fasting recipients excluded).

Instrument questions:

- During the last 12 hours have you had anything to eat or drink, other than water?
- Blood glucose measurement

```{r bglucose_b5_b5mg_tbls}
# column names to use with huxtable
bglucose_b5_col_names <- c("Age Group (years)", "n", "Mean", "95% CI")
bglucose_b5_reg_col_names <- c("Region", "n", "Mean", "95% CI")

# 1 - Mean fasting blood glucose (mmol/L)
# men, women, both sexes
bglucose_b5_m_w_b <- join_tbls(bglucose_b5, m_w_b, 1, bglucose_b5_col_names)

# 2 - Mean fasting blood glucose (mg/dl)
# men, women, both sexes
bglucose_b5mg_m_w_b <- join_tbls(bglucose_b5mg, m_w_b, 1, bglucose_b5_col_names)
```
```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# urban, rural
# 1 - Mean fasting blood glucose (mmol/L)
bglucose_b5_u_r <- join_tbls(bglucose_b5, u_r, 1, bglucose_b5_col_names)
# 2 - Mean fasting blood glucose (mg/dl)
bglucose_b5mg_u_r <- join_tbls(bglucose_b5mg, u_r, 1, bglucose_b5_col_names)
```

<br>

```{r}
# 1
cbind(bglucose_b5_m_w_b$m, select(bglucose_b5_m_w_b$w, -agerange), select(bglucose_b5_m_w_b$b, -agerange)) %>% final_tbl(.disaggregation = m_w_b, .s_amount = 3, .title = "Mean fasting blood glucose (mmol/L)", .colspan_val = 10)
```

<br>

```{r}
# 2
cbind(bglucose_b5mg_m_w_b$m, select(bglucose_b5mg_m_w_b$w, -agerange), select(bglucose_b5mg_m_w_b$b, -agerange)) %>% final_tbl(.disaggregation = m_w_b, .s_amount = 3, .title = "Mean fasting blood glucose (mg/dl)", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 1
tbl_m_u_r <- rbind(bglucose_b5_u_r$m_u, bglucose_b5_u_r$m_r)
tbl_w_u_r <- rbind(bglucose_b5_u_r$w_u, bglucose_b5_u_r$w_r)
tbl_b_u_r <- rbind(bglucose_b5_u_r$b_u, bglucose_b5_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_tbl(.disaggregation = u_r, .s_amount = 3, .title = "Mean fasting blood glucose (mmol/L) by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 2
tbl_m_u_r <- rbind(bglucose_b5mg_u_r$m_u, bglucose_b5mg_u_r$m_r)
tbl_w_u_r <- rbind(bglucose_b5mg_u_r$w_u, bglucose_b5mg_u_r$w_r)
tbl_b_u_r <- rbind(bglucose_b5mg_u_r$b_u, bglucose_b5mg_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_tbl(.disaggregation = u_r, .s_amount = 3, .title = "Mean fasting blood glucose (mg/dl) by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 1
bglucose_b5$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = bglucose_b5_reg_col_names) %>% final_tbl(.disaggregation = reg, 1, "Both sexes", "Mean fasting blood glucose (mmol/L) by region", 4)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 2
bglucose_b5mg$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = bglucose_b5_reg_col_names) %>% final_tbl(.disaggregation = reg, 1, "Both sexes", "Mean fasting blood glucose (mg/dl) by region", 4)
```

<br>

**Analysis information**:

-   Questions used: B1, B5
-   R script name: Bglucose

***

**Raised blood glucose**

Description: Categorization of respondents into blood glucose level categories and percentage of respondents currently on medication for raised blood glucose (non-fasting recipients excluded).

Instrument questions:

- In the past two weeks, have you taken any drugs (medication) for diabetes prescribed by a doctor or other health worker?
- Are you currently taking insulin for diabetes prescribed by a doctor or other health worker?
- During the last 12 hours have you had anything to eat or drink, other than water?
- Blood glucose measurement 
- Today, have you taken insulin or other drugs (medication) that have been prescribed by a doctor or other health worker?

```{r bglucose_ifg_rbg_or_meds_medstext_tbls}
# column names to use with huxtable
bglucose_ifg_rbg_or_meds_medstext_col_names <- c("Age Group (years)", "n", "%", "95% CI")
bglucose_ifg_rbg_or_meds_medstext_reg_col_names <- c("Region", "n", "%", "95% CI")

# prep titles
.title_m_w_b <- "Impaired Fasting Glycaemia*"
.title_u_r <- "by type of settlement"
.title_reg <- "by region"

# men, women, both sexes
# 1 (a) - Impaired Fasting Glycaemia*
bglucose_ifg_d_m_w_b <- join_tbls(bglucose_ifg_d, m_w_b, 1, bglucose_ifg_rbg_or_meds_medstext_col_names)

# 2 (b) - Raised blood glucose or currently on medication for diabetes**
bglucose_rbg_or_meds_d_m_w_b <- join_tbls(bglucose_rbg_or_meds_d, m_w_b, 1, bglucose_ifg_rbg_or_meds_medstext_col_names)

# 3 (c) - Currently on medication for diabetes
bglucose_medstext_m_w_b <- join_tbls(bglucose_medstext, m_w_b, 1, bglucose_ifg_rbg_or_meds_medstext_col_names)
```
```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# urban, rural
# 1 - Impaired Fasting Glycaemia*
bglucose_ifg_d_u_r <- join_tbls(bglucose_ifg_d, u_r, 1, bglucose_ifg_rbg_or_meds_medstext_col_names)
# 2 - Raised blood glucose or currently on medication for diabetes**
bglucose_rbg_or_meds_d_u_r <- join_tbls(bglucose_rbg_or_meds_d, u_r, 1, bglucose_ifg_rbg_or_meds_medstext_col_names)
# 3 - Currently on medication for diabetes
bglucose_medstext_u_r <- join_tbls(bglucose_medstext, u_r, 1, bglucose_ifg_rbg_or_meds_medstext_col_names)
```

<br>

```{r}
# 1
cbind(bglucose_ifg_d_m_w_b$m, select(bglucose_ifg_d_m_w_b$w, -agerange), select(bglucose_ifg_d_m_w_b$b, -agerange)) %>% final_tbl(.disaggregation = m_w_b, .s_amount = 3, .title = paste(.title_m_w_b), .colspan_val = 10)
```

<br>

```{r}
# 2
cbind(bglucose_rbg_or_meds_d_m_w_b$m, select(bglucose_rbg_or_meds_d_m_w_b$w, -agerange), select(bglucose_rbg_or_meds_d_m_w_b$b, -agerange)) %>% final_tbl(.disaggregation = m_w_b, .s_amount = 3, .title = "Raised blood glucose or currently on medication for diabetes**", .colspan_val = 10)
```

<br>

```{r}
# 3
cbind(bglucose_medstext_m_w_b$m, select(bglucose_medstext_m_w_b$w, -agerange), select(bglucose_medstext_m_w_b$b, -agerange)) %>% final_tbl(.disaggregation = m_w_b, .s_amount = 3, .title = "Currently on medication for diabetes", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 1
tbl_m_u_r <- rbind(bglucose_ifg_d_u_r$m_u, bglucose_ifg_d_u_r$m_r)
tbl_w_u_r <- rbind(bglucose_ifg_d_u_r$w_u, bglucose_ifg_d_u_r$w_r)
tbl_b_u_r <- rbind(bglucose_ifg_d_u_r$b_u, bglucose_ifg_d_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_tbl(.disaggregation = u_r, .s_amount = 3, .title = paste(.title_m_w_b, .title_u_r), .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 2
tbl_m_u_r <- rbind(bglucose_rbg_or_meds_d_u_r$m_u, bglucose_rbg_or_meds_d_u_r$m_r)
tbl_w_u_r <- rbind(bglucose_rbg_or_meds_d_u_r$w_u, bglucose_rbg_or_meds_d_u_r$w_r)
tbl_b_u_r <- rbind(bglucose_rbg_or_meds_d_u_r$b_u, bglucose_rbg_or_meds_d_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_tbl(.disaggregation = u_r, .s_amount = 3, .title = "Raised blood glucose or currently on medication for diabetes** by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 3
tbl_m_u_r <- rbind(bglucose_medstext_u_r$m_u, bglucose_medstext_u_r$m_r)
tbl_w_u_r <- rbind(bglucose_medstext_u_r$w_u, bglucose_medstext_u_r$w_r)
tbl_b_u_r <- rbind(bglucose_medstext_u_r$b_u, bglucose_medstext_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_tbl(.disaggregation = u_r, .s_amount = 3, .title = "Currently on medication for diabetes by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 1
bglucose_ifg_d$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = bglucose_ifg_rbg_or_meds_medstext_reg_col_names) %>% final_tbl(.disaggregation = reg, 1, "Both sexes", "Impaired Fasting Glycaemia* by region", 4)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 2
bglucose_rbg_or_meds_d$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = bglucose_ifg_rbg_or_meds_medstext_reg_col_names) %>% final_tbl(.disaggregation = reg, 1, "Both sexes", "Raised blood glucose or currently on medication for diabetes** by region", 4)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 3
bglucose_medstext$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = bglucose_ifg_rbg_or_meds_medstext_reg_col_names) %>% final_tbl(.disaggregation = reg, 1, "Both sexes", "Currently on medication for diabetes by region", 4)
```

<br>

*Impaired fasting glycaemia is defined as either
  
- plasma venous value: ≥6.1mmol/L (110mg/dl) and  <7.0mmol/L (126mg/dl)
- capillary whole blood value: ≥5.6mmol/L (100mg/dl) and  <6.1mmol/L (110mg/dl)

**Raised blood glucose is defined as either
  
- plasma venous value: ≥ 7.0 mmol/L (126 mg/dl)
- capillary whole blood value: ≥ 6.1 mmol/L (110 mg/dl)

**Analysis information**:

-   Questions used: H8, H9, B1, B5, B6
-   R script name: Bglucose

***


**Blood glucose diagnosis and treatment**

Description: Raised blood glucose diagnosis and treatment among all respondents.

Instrument questions:

- Have you ever had your blood sugar measured by a doctor or other health worker?
- Have you ever been told by a doctor or other health worker that you have raised blood sugar or diabetes?
- In the past two weeks, have you taken any drugs (medication) for diabetes prescribed by a doctor or other health worker?
- Are you currently taking insulin for diabetes prescribed by a doctor or other health worker?
- During the last 12 hours have you had anything to eat or drink, other than water?
- Blood glucose measurement 
- Today, have you taken insulin or other drugs (medication) that have been prescribed by a doctor or other health worker?

```{r bglucose_diagn_tbls}
# column names to use with huxtable
bglucose_diagn_col_names <- 
  c("Age Group (years)", "n", "% with raised blood glucose, not previously diagnosed", "95% CI", 
    "% with previously diagnosed raised blood glucose, not on medication", "95% CI", 
    "% with previously diagnosed raised blood glucose, on medication", "95% CI")

# column names for region to use with huxtable
bglucose_diagn_reg_col_names <- 
  c("Region", "n", "% with raised blood glucose, not previously diagnosed", "95% CI", 
    "% with previously diagnosed raised blood glucose, not on medication", "95% CI", 
    "% with previously diagnosed raised blood glucose, on medication", "95% CI")

# men, women, both sexes
bglucose_diagn_m_w_b <- join_tbls(bglucose_diagn, m_w_b, 3, bglucose_diagn_col_names)
```
```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# urban, rural
bglucose_diagn_u_r <- join_tbls(bglucose_diagn, u_r, 3, bglucose_diagn_col_names)
```

<br>

```{r}
bglucose_diagn_m_w_b$m %>% final_tbl(.disaggregation = m_w_b, 1, "Men", "Raised blood glucose diagnosis and treatment among all respondents", 8)
```

<br>

```{r}
bglucose_diagn_m_w_b$w %>% final_tbl(.disaggregation = m_w_b, 1, "Women", "Raised blood glucose diagnosis and treatment among all respondents", 8)
```

<br>

```{r}
bglucose_diagn_m_w_b$b %>% final_tbl(.disaggregation = m_w_b, 1, "Both sexes", "Raised blood glucose diagnosis and treatment among all respondents", 8)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
rbind(bglucose_diagn_u_r$m_u, bglucose_diagn_u_r$m_r) %>% 
  final_tbl(.disaggregation = u_r, 1, "Men", "Raised blood glucose diagnosis and treatment among all respondents by type of settlement", 8)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
rbind(bglucose_diagn_u_r$w_u, bglucose_diagn_u_r$w_r) %>% 
  final_tbl(.disaggregation = u_r, 1, "Women", "Raised blood glucose diagnosis and treatment among all respondents by type of settlement", 8)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
rbind(bglucose_diagn_u_r$b_u, bglucose_diagn_u_r$b_r) %>% 
  final_tbl(.disaggregation = u_r, 1, "Both sexes", "Raised blood glucose diagnosis and treatment among all respondents by type of settlement", 8)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# region
bglucose_diagn$b_reg %>% unite_ci(.ci_amount = 3) %>% apply_hux(.col_names = bglucose_diagn_reg_col_names) %>% 
  final_tbl(.disaggregation = reg, 1, "Both sexes", "Raised blood glucose diagnosis and treatment among all respondents by region", 8) 
```

<br>

**Analysis information**:

-   Questions used: H6, H7a, H8, H9, B1, B5, B6
-   R script name: Bglucose

***


**Total cholesterol**

Description: Mean total cholesterol among all respondents including those currently on medication for raised cholesterol.

Instrument questions:

- Total cholesterol measurement

```{r btotallipids_b8_b8mg_tbls}
# column names to use with huxtable
btotallipids_b8_b8mg_col_names <- c("Age Group (years)", "n", "Mean", "95% CI")
btotallipids_b8_b8mg_reg_col_names <- c("Region", "n", "Mean", "95% CI")

# prep titles
.title_m_w_b <- "Mean total cholesterol (mmol/L)"
.title_u_r <- "by type of settlement"
.title_reg <- "by region"

# men, women, both sexes
# 1 - Mean total cholesterol (mmol/L)
btotallipids_b8_m_w_b <- join_tbls(btotallipids_b8, m_w_b, 1, btotallipids_b8_b8mg_col_names)

# 2 - Mean total cholesterol (mg/dl)
btotallipids_b8mg_m_w_b <- join_tbls(btotallipids_b8mg, m_w_b, 1, btotallipids_b8_b8mg_col_names)
```
```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# urban, rural
# 1 - Mean total cholesterol (mmol/L)
btotallipids_b8_u_r <- join_tbls(btotallipids_b8, u_r, 1, btotallipids_b8_b8mg_col_names)
# 2 - Mean total cholesterol (mg/dl)
btotallipids_b8mg_u_r <- join_tbls(btotallipids_b8mg, u_r, 1, btotallipids_b8_b8mg_col_names)
```

<br>

```{r}
# 1
cbind(btotallipids_b8_m_w_b$m, select(btotallipids_b8_m_w_b$w, -agerange), select(btotallipids_b8_m_w_b$b, -agerange)) %>% final_tbl(.disaggregation = m_w_b, .s_amount = 3, .title = paste(.title_m_w_b), .colspan_val = 10)
```

<br>

```{r}
# 2
cbind(btotallipids_b8mg_m_w_b$m, select(btotallipids_b8mg_m_w_b$w, -agerange), select(btotallipids_b8mg_m_w_b$b, -agerange)) %>% final_tbl(.disaggregation = m_w_b, .s_amount = 3, .title = "Mean total cholesterol (mg/dl)", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 1
tbl_m_u_r <- rbind(btotallipids_b8_u_r$m_u, btotallipids_b8_u_r$m_r)
tbl_w_u_r <- rbind(btotallipids_b8_u_r$w_u, btotallipids_b8_u_r$w_r)
tbl_b_u_r <- rbind(btotallipids_b8_u_r$b_u, btotallipids_b8_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_tbl(.disaggregation = u_r, .s_amount = 3, .title = paste(.title_m_w_b, .title_u_r), .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 2
tbl_m_u_r <- rbind(btotallipids_b8mg_u_r$m_u, btotallipids_b8mg_u_r$m_r)
tbl_w_u_r <- rbind(btotallipids_b8mg_u_r$w_u, btotallipids_b8mg_u_r$w_r)
tbl_b_u_r <- rbind(btotallipids_b8mg_u_r$b_u, btotallipids_b8mg_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_tbl(.disaggregation = u_r, .s_amount = 3, .title = "Mean total cholesterol (mg/dl) by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 1
btotallipids_b8$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = btotallipids_b8_b8mg_reg_col_names) %>% final_tbl(.disaggregation = reg, 1, "Both sexes", "Mean total cholesterol (mmol/L) by region", 4)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 2
btotallipids_b8mg$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = btotallipids_b8_b8mg_reg_col_names) %>% final_tbl(.disaggregation = reg, 1, "Both sexes", "Mean total cholesterol (mg/dl) by region", 4)
```

<br>

**Analysis information**:

-   Questions used: B8
-   R script name: Btotallipids

***


**Raised total cholesterol**

Description: Percentage of respondents with raised total cholesterol.

Instrument questions:

- Total cholesterol measurement

```{r btotallipids_e_f_tbls}
# column names to use with huxtable
btotallipids_e_f_col_names <- c("Age Group (years)", "n", "%", "95% CI")
btotallipids_e_f_reg_col_names <- c("Region", "n", "%", "95% CI")

# men, women, both sexes
# 1 - Total cholesterol ≥ 5.0 mmol/L or ≥ 190 mg/dl
btotallipids_e_m_w_b <- join_tbls(btotallipids_e, m_w_b, 1, btotallipids_e_f_col_names)

# 2 - Total cholesterol ≥ 6.2 mmol/L or ≥ 240 mg/dl
btotallipids_f_m_w_b <- join_tbls(btotallipids_f, m_w_b, 1, btotallipids_e_f_col_names)
```
```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# urban, rural
# 1 - Total cholesterol ≥ 5.0 mmol/L or ≥ 190 mg/dl
btotallipids_e_u_r <- join_tbls(btotallipids_e, u_r, 1, btotallipids_e_f_col_names)
# 2 - Total cholesterol ≥ 6.2 mmol/L or ≥ 240 mg/dl
btotallipids_f_u_r <- join_tbls(btotallipids_f, u_r, 1, btotallipids_e_f_col_names)
```

<br>

```{r}
# 1
cbind(btotallipids_e_m_w_b$m, select(btotallipids_e_m_w_b$w, -agerange), select(btotallipids_e_m_w_b$b, -agerange)) %>% final_tbl(.disaggregation = m_w_b, .s_amount = 3, .title = "Total cholesterol ≥ 5.0 mmol/L or ≥ 190 mg/dl", .colspan_val = 10)
```

<br>

```{r}
# 2 NOTE: PRODUCES SLIGHTLY DIFFERENT NUMBERS
cbind(btotallipids_f_m_w_b$m, select(btotallipids_f_m_w_b$w, -agerange), select(btotallipids_f_m_w_b$b, -agerange)) %>% final_tbl(.disaggregation = m_w_b, .s_amount = 3, .title = "Total cholesterol ≥ 6.2 mmol/L or ≥ 240 mg/dl", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 1
tbl_m_u_r <- rbind(btotallipids_e_u_r$m_u, btotallipids_e_u_r$m_r)
tbl_w_u_r <- rbind(btotallipids_e_u_r$w_u, btotallipids_e_u_r$w_r)
tbl_b_u_r <- rbind(btotallipids_e_u_r$b_u, btotallipids_e_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_tbl(.disaggregation = u_r, .s_amount = 3, .title = paste("Total cholesterol ≥ 5.0 mmol/L or ≥ 190 mg/dl by type of settlement"), .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 2
tbl_m_u_r <- rbind(btotallipids_f_u_r$m_u, btotallipids_f_u_r$m_r)
tbl_w_u_r <- rbind(btotallipids_f_u_r$w_u, btotallipids_f_u_r$w_r)
tbl_b_u_r <- rbind(btotallipids_f_u_r$b_u, btotallipids_f_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_tbl(.disaggregation = u_r, .s_amount = 3, .title = "Total cholesterol ≥ 6.2 mmol/L or ≥ 240 mg/dl by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 1
btotallipids_e$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = btotallipids_e_f_reg_col_names) %>% final_tbl(.disaggregation = reg, 1, "Both sexes", "Total cholesterol ≥ 5.0 mmol/L or ≥ 190 mg/dl by region", 4)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 2 NOTE: PRODUCES SLIGHTLY DIFFERENT NUMBERS
btotallipids_f$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = btotallipids_e_f_reg_col_names) %>% final_tbl(.disaggregation = reg, 1, "Both sexes", "Total cholesterol ≥ 6.2 mmol/L or ≥ 240 mg/dl by region", 4)
```

<br>

**Analysis information**:

-   Questions used: B8
-   R script name: Btotallipids

***

**Raised total cholesterol**

Description: Percentage of respondents with raised total cholesterol and percentage of respondents currently on medication for raised cholesterol.

Instrument questions:

- Total cholesterol measurement
- During the past two weeks, have you been treated for raised cholesterol with drugs (medication) prescribed by a doctor or other health worker?

```{r btotallipids_c_d_tbls}
# column names to use with huxtable
btotallipids_c_d_col_names <- c("Age Group (years)", "n", "%", "95% CI")
btotallipids_c_d_reg_col_names <- c("Region", "n", "%", "95% CI")

# men, women, both sexes
# 1 - Total cholesterol ≥ 5.0 mmol/L or ≥ 190 mg/dl or currently on medication for raised cholesterol
btotallipids_c_m_w_b <- join_tbls(btotallipids_c, m_w_b, 1, btotallipids_c_d_col_names)

# 2 - Total cholesterol ≥ 6.2 mmol/L or ≥ 240 mg/dl or currently on medication for raised cholesterol
btotallipids_d_m_w_b <- join_tbls(btotallipids_d, m_w_b, 1, btotallipids_c_d_col_names)
```
```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# urban, rural
# 1 - Total cholesterol ≥ 5.0 mmol/L or ≥ 190 mg/dl or currently on medication for raised cholesterol
btotallipids_c_u_r <- join_tbls(btotallipids_c, u_r, 1, btotallipids_c_d_col_names)
# 2 - Total cholesterol ≥ 6.2 mmol/L or ≥ 240 mg/dl or currently on medication for raised cholesterol
btotallipids_d_u_r <- join_tbls(btotallipids_d, u_r, 1, btotallipids_c_d_col_names)
```

<br>

```{r}
# 1
cbind(btotallipids_c_m_w_b$m, select(btotallipids_c_m_w_b$w, -agerange), select(btotallipids_c_m_w_b$b, -agerange)) %>% final_tbl(.disaggregation = m_w_b, .s_amount = 3, .title = "Total cholesterol ≥ 5.0 mmol/L or ≥ 190 mg/dl or currently on medication for raised cholesterol", .colspan_val = 10)
```

<br>

```{r}
# 2 NOTE: PRODUCES SLIGHTLY DIFFERENT NUMBERS
cbind(btotallipids_d_m_w_b$m, select(btotallipids_d_m_w_b$w, -agerange), select(btotallipids_d_m_w_b$b, -agerange)) %>% final_tbl(.disaggregation = m_w_b, .s_amount = 3, .title = "Total cholesterol ≥ 6.2 mmol/L or ≥ 240 mg/dl or currently on medication for raised cholesterol", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 1
tbl_m_u_r <- rbind(btotallipids_c_u_r$m_u, btotallipids_c_u_r$m_r)
tbl_w_u_r <- rbind(btotallipids_c_u_r$w_u, btotallipids_c_u_r$w_r)
tbl_b_u_r <- rbind(btotallipids_c_u_r$b_u, btotallipids_c_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_tbl(.disaggregation = u_r, .s_amount = 3, .title = paste("Total cholesterol ≥ 5.0 mmol/L or ≥ 190 mg/dl or currently on medication for raised cholesterol by type of settlement"), .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 2
tbl_m_u_r <- rbind(btotallipids_d_u_r$m_u, btotallipids_d_u_r$m_r)
tbl_w_u_r <- rbind(btotallipids_d_u_r$w_u, btotallipids_d_u_r$w_r)
tbl_b_u_r <- rbind(btotallipids_d_u_r$b_u, btotallipids_d_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_tbl(.disaggregation = u_r, .s_amount = 3, .title = "Total cholesterol ≥ 6.2 mmol/L or ≥ 240 mg/dl or currently on medication for raised cholesterol by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 1
btotallipids_c$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = btotallipids_c_d_reg_col_names) %>% final_tbl(.disaggregation = reg, 1, "Both sexes", "Total cholesterol ≥ 5.0 mmol/L or ≥ 190 mg/dl or currently on medication for raised cholesterol by region", 4)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 2 NOTE: PRODUCES SLIGHTLY DIFFERENT NUMBERS
btotallipids_d$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = btotallipids_c_d_reg_col_names) %>% final_tbl(.disaggregation = reg, 1, "Both sexes", "Total cholesterol ≥ 6.2 mmol/L or ≥ 240 mg/dl or currently on medication for raised cholesterol by region", 4)
```

<br>

**Analysis information**:

-   Questions used: B8, B9
-   R script name: Btotallipids

***


**High density lipoprotein (HDL)**

Description: Mean HDL among all respondents and percentage of respondents with low HDL.

Instrument questions:

- HDL cholesterol measurement

```{r bhdlipids_b17_b17mg_tbls}
# column names to use with huxtable
bhdlipids_b17_col_names <- c("Age Group (years)", "n", "Mean", "95% CI")
bhdlipids_b17_reg_col_names <- c("Region", "n", "Mean", "95% CI")
bhdlipids_c_d_col_names <- c("Age Group (years)", "n", "%", "95% CI")
bhdlipids_c_d_reg_col_names <- c("Region", "n", "%", "95% CI")

# men, women, both sexes 
# 1 - Mean HDL (mmol/L)
bhdlipids_b17_m_w_b <- join_tbls(bhdlipids_b17, m_w_b, 1, bhdlipids_b17_col_names)
# 2 - Mean HDL (mg/dl)
bhdlipids_b17mg_m_w_b <- join_tbls(bhdlipids_b17mg, m_w_b, 1, bhdlipids_b17_col_names)

# men, women, both sexes
# 3 - Percentage of respondents with HDL <1.03mmol/L or <40 mg/dl (USE MEN ONLY)
bhdlipids_c_m_w_b <- join_tbls(bhdlipids_c, m_w_b, 1, bhdlipids_c_d_col_names)
# 4 - Percentage of respondents with HDL <1.29mmol/L or <50 mg/dl (USE WOMEN ONLY)
bhdlipids_d_m_w_b <- join_tbls(bhdlipids_d, m_w_b, 1, bhdlipids_c_d_col_names)
```
```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# urban, rural
# 1 - Mean HDL (mmol/L)
bhdlipids_b17_u_r <- join_tbls(bhdlipids_b17, u_r, 1, bhdlipids_b17_col_names)
# 2 - Mean HDL (mg/dl)
bhdlipids_b17mg_u_r <- join_tbls(bhdlipids_b17mg, u_r, 1, bhdlipids_b17_col_names)

# 3 - Percentage of respondents with HDL <1.03mmol/L or <40 mg/dl (USE MEN ONLY)
bhdlipids_c_u_r <- join_tbls(bhdlipids_c, u_r, 1, bhdlipids_c_d_col_names)
# 4 - Percentage of respondents with HDL <1.29mmol/L or <50 mg/dl (USE WOMEN ONLY)
bhdlipids_d_u_r <- join_tbls(bhdlipids_d, u_r, 1, bhdlipids_c_d_col_names)
```

<br>

```{r}
# 1
cbind(bhdlipids_b17_m_w_b$m, select(bhdlipids_b17_m_w_b$w, -agerange), select(bhdlipids_b17_m_w_b$b, -agerange)) %>% final_tbl(.disaggregation = m_w_b, .s_amount = 3, .title = "Mean HDL (mmol/L)", .colspan_val = 10)
```

<br>

```{r}
# 2
cbind(bhdlipids_b17mg_m_w_b$m, select(bhdlipids_b17mg_m_w_b$w, -agerange), select(bhdlipids_b17mg_m_w_b$b, -agerange)) %>% final_tbl(.disaggregation = m_w_b, .s_amount = 3, .title = "Mean HDL (mg/dl)", .colspan_val = 10)
```

<br>

```{r}
# 3
# ONLY MEN INCLUDED
bhdlipids_c$m %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = bhdlipids_c_d_col_names) %>% final_tbl(.disaggregation = m_w_b, 1, "Men", "Percentage of respondents with HDL <1.03mmol/L or <40 mg/dl", 4)
```

<br>

```{r}
# 4
# ONLY WOMEN INCLUDED
bhdlipids_d$w %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = bhdlipids_c_d_col_names) %>% final_tbl(.disaggregation = m_w_b, 1, "Women", "Percentage of respondents with HDL <1.29mmol/L or <50 mg/dl", 4)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 1
tbl_m_u_r <- rbind(bhdlipids_b17_u_r$m_u, bhdlipids_b17_u_r$m_r)
tbl_w_u_r <- rbind(bhdlipids_b17_u_r$w_u, bhdlipids_b17_u_r$w_r)
tbl_b_u_r <- rbind(bhdlipids_b17_u_r$b_u, bhdlipids_b17_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_tbl(.disaggregation = u_r, .s_amount = 3, .title = "Mean HDL (mmol/L) by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 2
tbl_m_u_r <- rbind(bhdlipids_b17mg_u_r$m_u, bhdlipids_b17mg_u_r$m_r)
tbl_w_u_r <- rbind(bhdlipids_b17mg_u_r$w_u, bhdlipids_b17mg_u_r$w_r)
tbl_b_u_r <- rbind(bhdlipids_b17mg_u_r$b_u, bhdlipids_b17mg_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_tbl(.disaggregation = u_r, .s_amount = 3, .title = "Mean HDL (mg/dl) by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 3
# ONLY MEN INCLUDED
tbl_m_u_r <- rbind(bhdlipids_c_u_r$m_u, bhdlipids_c_u_r$m_r)
tbl_w_u_r <- rbind(bhdlipids_c_u_r$w_u, bhdlipids_c_u_r$w_r)
tbl_b_u_r <- rbind(bhdlipids_c_u_r$b_u, bhdlipids_c_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_tbl(.disaggregation = u_r, .s_amount = 3, .title = "Percentage of respondents with HDL <1.03mmol/L or <40 mg/dl by type of settlement", .colspan_val = 4) %>% select(c(1:4))
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 4
# ONLY WOMEN INCLUDED
tbl_m_u_r <- rbind(bhdlipids_d_u_r$m_u, bhdlipids_d_u_r$m_r)
tbl_w_u_r <- rbind(bhdlipids_d_u_r$w_u, bhdlipids_d_u_r$w_r)
tbl_b_u_r <- rbind(bhdlipids_d_u_r$b_u, bhdlipids_d_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_tbl(.disaggregation = u_r, .s_amount = 3, .title = "Percentage of respondents with HDL <1.29mmol/L or <50 mg/dl by type of settlement", .colspan_val = 7) %>% select(c(1,5:7))
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 1
bhdlipids_b17$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = bhdlipids_b17_reg_col_names) %>% final_tbl(.disaggregation = reg, 1, "Both sexes", "Mean HDL (mmol/L) by region", 4)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 2
bhdlipids_b17mg$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = bhdlipids_b17_reg_col_names) %>% final_tbl(.disaggregation = reg, 1, "Both sexes", "Mean HDL (mg/dl) by region", 4)
```

<br>


**Analysis information**:

-   Questions used: B17
-   R script name: Bhdlipids

***


<br> 

<br>
