---
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  word_document: default
---

```{r setup, include=FALSE}
library(here)
library(huxtable)
library(tidyverse)
library(fs)
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
# Set a root directory for all chunks to be evaluated relative to rather than the document location
knitr::opts_knit$set(root.dir = here())
```

```{r source, include=FALSE}
here("DataBook", "Modules", "CardiovascularDiseaseRisk") %>% 
  # list all R files in the directory
  fs::dir_ls(regexp = "\\.R$") %>% 
  # scale up to all R files with a map function from purrr
  map(source, encoding = "UTF-8", local = knitr::knit_global())
```

---
title: "`r set_title`"
author: "`r set_author`"
---


# Cardiovascular disease risk

**CVD risk of ≥30% or existing CVD**

Description: Percentage of respondents aged 40–69 years with a 10-year cardiovascular disease (CVD) risk* ≥30% or with existing CVD.

Instrument questions: combined from Step 1, 2 and 3

- Gender, age
- Current and former smoking
- History of diabetes, CVD
- Systolic blood pressure measurements
- Fasting status, glucose and total cholesterol measurements.

```{r cvdrisk_c_tbls}
# column names to use with huxtable
cvdrisk_c_col_names <- c("Age Group (years)", "n", "%", "95% CI")
cvdrisk_c_reg_col_names <- c("Region", "n", "%", "95% CI")

# men, women, both sexes
cvdrisk_c_m_w_b <- join_tbls(cvdrisk_c, m_w_b, 1, cvdrisk_c_col_names)
```
```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# urban, rural
cvdrisk_c_u_r <- join_tbls(cvdrisk_c, u_r, 1, cvdrisk_c_col_names)
```

<br>

```{r}
cbind(cvdrisk_c_m_w_b$m, select(cvdrisk_c_m_w_b$w, -1), select(cvdrisk_c_m_w_b$b, -1)) %>% 
  final_tbl(.disaggregation = m_w_b, .s_amount = 3, .title = "Percentage of respondents with a 10-year CVD risk ≥30% or with existing CVD", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
tbl_m_u_r <- rbind(cvdrisk_c_u_r$m_u, cvdrisk_c_u_r$m_r)
tbl_w_u_r <- rbind(cvdrisk_c_u_r$w_u, cvdrisk_c_u_r$w_r)
tbl_b_u_r <- rbind(cvdrisk_c_u_r$b_u, cvdrisk_c_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -1), select(tbl_b_u_r, -1)) %>% 
  final_tbl(.disaggregation = u_r, .s_amount = 3, .title = "Percentage of respondents with a 10-year CVD risk ≥30% or with existing CVD by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
cvdrisk_c$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = cvdrisk_c_reg_col_names) %>% 
  final_tbl(.disaggregation = reg, 1, "Both sexes", "Percentage of respondents with a 10-year CVD risk ≥30% or with existing CVD by region", 4)
```


* A 10-year CVD risk of ≥30% is defined according to age, sex, blood pressure, smoking status (current smokers OR those who quit smoking less than 1 year before the assessment), total cholesterol, and diabetes (previously diagnosed OR a fasting plasma glucose concentration >7.0 mmol/l (126 mg/dl)). 

<br>

**Analysis information**:

-   Questions used: C1, C2, C3, T1, T8T10, T11a-c, H6, H7a, H17, M4a, M5a, M6a, M7, B1, B5, B8
-   R script name: CVDrisk

***


**Drug therapy and counseling for those with CVD risk ≥30% or existing CVD**

Description: Percentage of eligible persons (defined as aged 40–69 years with a 10-year cardiovascular disease (CVD) risk* ≥30%, including those with existing CVD) receiving drug therapy and counseling** (including glycaemic control) to prevent heart attacks and strokes.

Instrument questions: combined from Step 1, 2 and 3

- Gender, age
- Current and former smoking
- History of diabetes, CVD
- Lifestyle advice
- Systolic blood pressure measurements
- Fasting status, glucose and total cholesterol measurements.

```{r cvdrisk_d_tbls}
# column names to use with huxtable
cvdrisk_d_col_names <- c("Age Group (years)", "n", "%", "95% CI")
cvdrisk_d_reg_col_names <- c("Region", "n", "%", "95% CI")

# men, women, both sexes
cvdrisk_d_m_w_b <- join_tbls(cvdrisk_d, m_w_b, 1, cvdrisk_d_col_names)
```
```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# urban, rural
cvdrisk_d_u_r <- join_tbls(cvdrisk_d, u_r, 1, cvdrisk_d_col_names)
```

<br>

```{r}
cbind(cvdrisk_d_m_w_b$m, select(cvdrisk_d_m_w_b$w, -1), select(cvdrisk_d_m_w_b$b, -1)) %>% 
  final_tbl(.disaggregation = m_w_b, .s_amount = 3, .title = "Percentage of eligible persons receiving drug therapy and counseling to prevent heart attacks and strokes", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
tbl_m_u_r <- rbind(cvdrisk_d_u_r$m_u, cvdrisk_d_u_r$m_r)
tbl_w_u_r <- rbind(cvdrisk_d_u_r$w_u, cvdrisk_d_u_r$w_r)
tbl_b_u_r <- rbind(cvdrisk_d_u_r$b_u, cvdrisk_d_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -1), select(tbl_b_u_r, -1)) %>% 
  final_tbl(.disaggregation = u_r, .s_amount = 3, .title = "Percentage of eligible persons receiving drug therapy and counseling to prevent heart attacks and strokes by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
cvdrisk_d$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = cvdrisk_d_reg_col_names) %>% 
  final_tbl(.disaggregation = reg, 1, "Both sexes", "Percentage of eligible persons receiving drug therapy and counseling to prevent heart attacks and strokes by region", 4)
```

<br>

* A 10-year CVD risk of ≥30% is defined according to age, sex, blood pressure, smoking status (current smokers OR those who quit smoking less than 1 year before the assessment), total cholesterol, and diabetes (previously diagnosed OR a fasting plasma glucose concentration >7.0 mmol/l (126 mg/dl)). 

**Counseling is defined as receiving advice from a doctor or other health worker to quit using tobacco or not start, reduce salt in diet, eat at least five servings of fruit and/or vegetables per day, reduce fat in diet, start or do more physical activity, maintain a healthy body weight or lose weight.


**Analysis information**:

-   Questions used: C1, C2, C3, T1, T8T10, T11a-c, H6, H7a, H8, H9, H13a, H14, H17, H18, H19, H20a-f, M4a, M5a, M6a, M7, B1, B5, B8
-   R script name: CVDrisk

***

<br> 

<br>
