---
title: "STEPS MDA Data Book"
author: "WHO NCD Office Moscow"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  word_document: default
  html_document:
    css: style.css
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
library(here)
library(huxtable)
library(tidyverse)
library(fs)
```

```{r source, include=FALSE}
cervical_cancer_data_dir <- here::here("DataBook", "Modules", "CervicalCancerScreening")

# list all files in the directory
# fs::dir_ls(cervical_cancer_data_dir)

# only R files
r_files <- fs::dir_ls(cervical_cancer_data_dir, regexp = "\\.R$") 
# r_files

# read in just one R file for testing
# source(r_files[1])

# scale up to all R files with a map function from purrr
r_files %>% 
  map(source, encoding = "UTF-8", local = knitr::knit_global())
```

```{r databook_functions, echo=FALSE}
source(here("DataBook", "databook_functions.R"), encoding = "UTF-8", local = knitr::knit_global())
```

```{r}
m_w_b <- c("m","w","b")
u_r <- c("m_u","w_u","b_u","m_r","w_r","b_r")
```

# Cervical Cancer Screening

**Cervical cancer screening**

Description: Percentage of female respondents who have ever had a screening test for cervical cancer among all female respondents.

Instrument questions:

- Have you ever had a screening test for cervical cancer, using any of these methods described above?

```{r hcervcancer_c_duration_tbls}
# column names to use with huxtable
hcervcancer_c_col_names <- c("Age Group (years)", "n", "% Ever tested", "95% CI")
hcervcancer_c_reg_col_names <- c("Region", "n", "% Ever tested", "95% CI")

# women
hcervcancer_c_w$w %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = hcervcancer_c_col_names) %>% 
  final_m_w_b_tbl(1, "Women", "Cervical cancer screening", 4)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
rbind(unite_ci(hcervcancer_c_w$w_u, .ci_amount = 1) %>% 
        apply_hux(.col_names = hcervcancer_c_col_names), 
      unite_ci(hcervcancer_c_w$w_r, .ci_amount = 1) %>% 
        apply_hux(.col_names = hcervcancer_c_col_names)) %>% 
  final_u_r_tbl(1, "Women", "Cervical cancer screening by type of settlement", 4)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
hcervcancer_c_w$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = hcervcancer_c_col_names) %>% 
  final_m_w_b_tbl(1, "Women", "Cervical cancer screening by region", 4)
```

<br>

**Analysis information**:

-   Questions used: CX1
-   R script name: Hcervcancer

***


**Cervical cancer screening among women aged 30-49 years**

Description: Percentage of female respondents aged 30-49 years who have ever had a screening test for cervical cancer among all female respondents aged 30-49 years.

Instrument questions:

- Have you ever had a screening test for cervical cancer, using any of these methods described above?

```{r hcervcancer_c2_duration_tbls}
# column names to use with huxtable
hcervcancer_c2_col_names <- c("Age Group (years)", "n", "% Ever tested", "95% CI")
hcervcancer_c2_reg_col_names <- c("Region", "n", "% Ever tested", "95% CI")

# women
hcervcancer_c2_w_t %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = hcervcancer_c2_col_names) %>% 
  final_m_w_b_tbl(1, "Women", "Cervical cancer screening among women aged 30-49 years", 4)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
rbind(unite_ci(hcervcancer_c2_w$w_u %>% filter(agerange2 == "18–69"), .ci_amount = 1) %>% 
        apply_hux(.col_names = hcervcancer_c2_col_names), 
      unite_ci(hcervcancer_c2_w$w_r %>% filter(agerange2 == "18–69"), .ci_amount = 1) %>% 
        apply_hux(.col_names = hcervcancer_c2_col_names)) %>% 
  final_m_w_b_tbl(1, "Women", "Cervical cancer screening among women aged 30-49 years by type of settlement", 4) %>% 
  # add urban and rural rows
  insert_row("Urban", after = 3, fill = "", colspan = 4) %>%
  set_bottom_border(row = c(4,6), everywhere, value = 0) %>% 
  set_contents(row = 6, col = 1, value = "Rural") %>% 
  merge_cells(row = 6, col = c(1:4)) %>% 
  set_right_border(row = c(4, 6), col = 1) %>%
  set_left_padding(row = c(4, 6), col = 1, value = 8) %>% 
  # align left urban and rural
  set_align(row = 4, value = "left") %>%
  set_align(row = 6, value = "left") %>%
  set_bold(row = c(4, 6), everywhere)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
hcervcancer_c2_w$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = hcervcancer_c2_col_names) %>% 
  final_m_w_b_tbl(1, "Women", "Cervical cancer screening among women aged 30-49 years by region", 4)
```

<br>

**Analysis information**:

-   Questions used: CX1
-   R script name: Hcervcancer

***


<br> 

<br>
