---
title: "STEPS MDA Data Book"
author: "WHO NCD Office Moscow"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  word_document: default
  html_document:
    css: style.css
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
library(here)
library(huxtable)
library(tidyverse)
library(fs)
```

```{r source, include=FALSE}
demog_info_data_dir <- here::here("DataBook", "Modules", "DemographicInformation")

# list all files in the directory
# fs::dir_ls(demog_info_data_dir)

# only R files
r_files <- fs::dir_ls(demog_info_data_dir, regexp = "\\.R$") 
# r_files

# read in just one R file for testing
# source(r_files[1])

# scale up to all R files with a map function from purrr
r_files %>% 
  map(source, encoding = "UTF-8", local = knitr::knit_global())
```

```{r databook_functions, echo=FALSE}
source(here("DataBook", "databook_functions.R"), encoding = "UTF-8", local = knitr::knit_global())
```

```{r}
m_w_b <- c("m","w","b")
u_r <- c("m_u","w_u","b_u","m_r","w_r","b_r")
```

# Demographic Information Results

**Age group by sex**

Description: Summary information by age group and sex of the respondents.

Instrument questions:

- Sex
- What is your date of birth?

```{r cagesex_tbls}
# column names to use with huxtable
cagesex_col_names <- c("Age Group (years)", "n", "%")
cagesex_reg_col_names <- c("Region", "n", "%")

# men, women, both sexes
cagesex_m_w_b <- join_m_w_b(cagesex, 0, cagesex_col_names)
```
```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# urban, rural
cagesex_u_r <- join_u_r(cagesex, 0, cagesex_col_names)
```

<br>

```{r}
cbind(cagesex_m_w_b$m, select(cagesex_m_w_b$w, -agerange), select(cagesex_m_w_b$b, -agerange)) %>% 
  final_m_w_b_tbl(.s_amount = "unwt_3", .title = "Age group and sex of respondents", .colspan_val = 7)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
tbl_m_u_r <- rbind(cagesex_u_r$m_u, cagesex_u_r$m_r)
tbl_w_u_r <- rbind(cagesex_u_r$w_u, cagesex_u_r$w_r)
tbl_b_u_r <- rbind(cagesex_u_r$b_u, cagesex_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_u_r_tbl(.s_amount = "unwt_3", .title = "Age group and sex of respondents by type of settlement", .colspan_val = 7)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
cagesex$b_reg %>% apply_hux(.col_names = cagesex_reg_col_names) %>% 
  final_m_w_b_tbl(.s_amount = 1, .s_val = "Both sexes", .title = "Age group and sex of respondents by region", .colspan_val = 3) 
```

<br>

**Analysis information**:

- Questions used: C1, C2, C3
- R script name: Cagesex

***

**Education**

Description: Mean number of years of education among respondents.

Instrument questions:

- In total, how many years have you spent at school or in full-time study (excluding pre-school)?

```{r ceduyears_tbls}
# column names to use with huxtable
ceduyears_col_names <- c("Age Group (years)", "n", "Mean")
ceduyears_reg_col_names <- c("Region", "n", "Mean")

# men, women, both sexes
ceduyears_m_w_b <- join_m_w_b(ceduyears, 0, ceduyears_col_names)
```
```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# urban, rural
ceduyears_u_r <- join_u_r(ceduyears, 0, ceduyears_col_names)
```

<br>

```{r}
cbind(ceduyears_m_w_b$m, select(ceduyears_m_w_b$w, -agerange), select(ceduyears_m_w_b$b, -agerange)) %>% 
  final_m_w_b_tbl(.s_amount = "unwt_3", .title = "Mean number of years of education", .colspan_val = 7)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
tbl_m_u_r <- rbind(ceduyears_u_r$m_u, ceduyears_u_r$m_r)
tbl_w_u_r <- rbind(ceduyears_u_r$w_u, ceduyears_u_r$w_r)
tbl_b_u_r <- rbind(ceduyears_u_r$b_u, ceduyears_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_u_r_tbl(.s_amount = "unwt_3", .title = "Mean number of years of education by type of settlement", .colspan_val = 7)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
ceduyears$b_reg %>% apply_hux(.col_names = ceduyears_reg_col_names) %>% 
  final_m_w_b_tbl(.s_amount = 1, .s_val = "Both sexes", .title = "Mean number of years of education by region", .colspan_val = 3) 
```

<br>

**Analysis information**:

- Questions used: C4
- R script name: Ceduyears

***


**Highest level of education**

Description: Highest level of education achieved by the survey respondents.

Instrument questions:

- What is the highest level of education you have completed?

```{r ceduhigh_c_tbls}
# column names to use with huxtable
ceduhigh_c_col_names <- 
  c("Age Group (years)", "n", "% No formal schooling", "% Less than primary school", 
    "% Primary school completed", "% Secondary school completed", "% High school completed", 
    "% College/ University completed", "% Post graduate degree completed")

# column names for region to use with huxtable
ceduhigh_c_reg_col_names <- 
  c("Region", "n", "% No formal schooling", "% Less than primary school", 
    "% Primary school completed", "% Secondary school completed", "% High school completed", 
    "% College/ University completed", "% Post graduate degree completed")

# men, women, both sexes
ceduhigh_c_m_w_b <- join_m_w_b(ceduhigh_c, 0, ceduhigh_c_col_names)
```
```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# urban, rural
ceduhigh_c_u_r <- join_u_r(ceduhigh_c, 0, ceduhigh_c_col_names)
```

<br>

```{r}
ceduhigh_c_m_w_b$m %>% final_m_w_b_tbl(1, "Men", "Highest level of education", 9)
```

<br>

```{r}
ceduhigh_c_m_w_b$w %>% final_m_w_b_tbl(1, "Women", "Highest level of education", 9)
```

<br>

```{r}
ceduhigh_c_m_w_b$b %>% final_m_w_b_tbl(1, "Both sexes", "Highest level of education", 9)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
rbind(ceduhigh_c_u_r$m_u, ceduhigh_c_u_r$m_r) %>% 
  final_u_r_tbl(1, "Men", "Highest level of education by type of settlement", 9)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
rbind(ceduhigh_c_u_r$w_u, ceduhigh_c_u_r$w_r) %>% 
  final_u_r_tbl(1, "Women", "Highest level of education by type of settlement", 9)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
rbind(ceduhigh_c_u_r$b_u, ceduhigh_c_u_r$b_r) %>% 
  final_u_r_tbl(1, "Both sexes", "Highest level of education by type of settlement", 9)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# region
ceduhigh_c$b_reg %>% apply_hux(.col_names = ceduhigh_c_reg_col_names) %>% 
  final_m_w_b_tbl(1, "Both sexes", "Highest level of education by region", 9) 
```

<br>

**Analysis information**:

- Questions used: C5
- R script name: Ceduhigh

***


**Martial status**

Description: Marital status of survey respondents.

Instrument questions:

- What is your marital status?

```{r cmaritalstatus_c_tbls}
# column names to use with huxtable
cmaritalstatus_c_col_names <- 
  c("Age Group (years)", "n", "% Never married", "% Currently married", 
    "% Separated", "% Divorced", "% Widowed", "% Cohabiting")

# column names for region to use with huxtable
cmaritalstatus_c_reg_col_names <- 
  c("Region", "n", "% Never married", "% Currently married", 
    "% Separated", "% Divorced", "% Widowed", "% Cohabiting")

# men, women, both sexes
cmaritalstatus_c_m_w_b <- join_m_w_b(cmaritalstatus_c, 0, cmaritalstatus_c_col_names)
```
```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# urban, rural
cmaritalstatus_c_u_r <- join_u_r(cmaritalstatus_c, 0, cmaritalstatus_c_col_names)
```

<br>

```{r}
cmaritalstatus_c_m_w_b$m %>% final_m_w_b_tbl(1, "Men", "Marital status", 8)
```

<br>

```{r}
cmaritalstatus_c_m_w_b$w %>% final_m_w_b_tbl(1, "Women", "Marital status", 8)
```

<br>

```{r}
cmaritalstatus_c_m_w_b$b %>% final_m_w_b_tbl(1, "Both sexes", "Marital status", 8)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
rbind(cmaritalstatus_c_u_r$m_u, cmaritalstatus_c_u_r$m_r) %>% 
  final_u_r_tbl(1, "Men", "Marital status by type of settlement", 8)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
rbind(cmaritalstatus_c_u_r$w_u, cmaritalstatus_c_u_r$w_r) %>% 
  final_u_r_tbl(1, "Women", "Marital status by type of settlement", 8)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
rbind(cmaritalstatus_c_u_r$b_u, cmaritalstatus_c_u_r$b_r) %>% 
  final_u_r_tbl(1, "Both sexes", "Marital status by type of settlement", 8)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# region
cmaritalstatus_c$b_reg %>% apply_hux(.col_names = cmaritalstatus_c_reg_col_names) %>% 
  final_m_w_b_tbl(1, "Both sexes", "Marital status by region", 8) 
```

<br>

**Analysis information**:

- Questions used: C7
- R script name: Cmaritalstatus

***


**Employment  status**

Description: Proportion of respondents in paid employment and those who are unpaid. Unpaid includes persons who are non-paid, students, homemakers, retired, and unemployed.

Instrument questions:

- Which of the following best describes your main work status over the past 12 months?

```{r cworkpaid_c_tbls}
# column names to use with huxtable
cworkpaid_c_col_names <- 
  c("Age Group (years)", "n", "% Government employee", "% Non-government employee", "% Self-employed", "% Unpaid")

# column names for region to use with huxtable
cworkpaid_c_reg_col_names <- 
  c("Region", "n", "% Government employee", "% Non-government employee", "% Self-employed", "% Unpaid")

# men, women, both sexes
cworkpaid_c_m_w_b <- join_m_w_b(cworkpaid_c, 0, cworkpaid_c_col_names)
```
```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# urban, rural
cworkpaid_c_u_r <- join_u_r(cworkpaid_c, 0, cworkpaid_c_col_names)
```

<br>

```{r}
cworkpaid_c_m_w_b$m %>% final_m_w_b_tbl(1, "Men", "Employment status", 6)
```

<br>

```{r}
cworkpaid_c_m_w_b$w %>% final_m_w_b_tbl(1, "Women", "Employment status", 6)
```

<br>

```{r}
cworkpaid_c_m_w_b$b %>% final_m_w_b_tbl(1, "Both sexes", "Employment status", 6)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
rbind(cworkpaid_c_u_r$m_u, cworkpaid_c_u_r$m_r) %>% 
  final_u_r_tbl(1, "Men", "Employment status by type of settlement", 6)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
rbind(cworkpaid_c_u_r$w_u, cworkpaid_c_u_r$w_r) %>% 
  final_u_r_tbl(1, "Women", "Employment status by type of settlement", 6)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
rbind(cworkpaid_c_u_r$b_u, cworkpaid_c_u_r$b_r) %>% 
  final_u_r_tbl(1, "Both sexes", "Employment status by type of settlement", 6)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# region
cworkpaid_c$b_reg %>% apply_hux(.col_names = cworkpaid_c_reg_col_names) %>% 
  final_m_w_b_tbl(1, "Both sexes", "Employment status by region", 6) 
```

<br>

**Analysis information**:

- Questions used: C8
- R script name: Cworkpaid

***


**Unpaid work and unemployed**

Description: Proportion of respondents in unpaid work.

Instrument questions:

- Which of the following best describes your main work status over the past 12 months?

```{r cworknotpaid_c_tbls}
# column names to use with huxtable
cworknotpaid_c_col_names <- 
  c("Age Group (years)", "n", "% Non-paid", "% Student", "% Home-maker", "% Retired", 
    "% Unemployed (Able to work)", "% Unemployed (Not able to work)")

# column names for region to use with huxtable
cworknotpaid_c_reg_col_names <- 
  c("Region", "n", "% Non-paid", "% Student", "% Home-maker", "% Retired", 
    "% Unemployed (Able to work)", "% Unemployed (Not able to work)")

# men, women, both sexes
cworknotpaid_c_m_w_b <- join_m_w_b(cworknotpaid_c, 0, cworknotpaid_c_col_names)
```
```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# urban, rural
cworknotpaid_c_u_r <- join_u_r(cworknotpaid_c, 0, cworknotpaid_c_col_names)
```

<br>

```{r}
cworknotpaid_c_m_w_b$m %>% final_m_w_b_tbl(1, "Men", "Unpaid work and unemployed", 8) #%>% 
  # insert_row(c("","","","","","","Unemployed",""), after = 2) %>% 
  # merge_cells(row = 3, col = c(7:8)) %>% merge_cells(row = 3, col = c(1:6))
```

<br>

```{r}
cworknotpaid_c_m_w_b$w %>% final_m_w_b_tbl(1, "Women", "Unpaid work and unemployed", 8)
```

<br>

```{r}
cworknotpaid_c_m_w_b$b %>% final_m_w_b_tbl(1, "Both sexes", "Unpaid work and unemployed", 8)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
rbind(cworknotpaid_c_u_r$m_u, cworknotpaid_c_u_r$m_r) %>% 
  final_u_r_tbl(1, "Men", "Unpaid work and unemployed by type of settlement", 8)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
rbind(cworknotpaid_c_u_r$w_u, cworknotpaid_c_u_r$w_r) %>% 
  final_u_r_tbl(1, "Women", "Unpaid work and unemployed by type of settlement", 8)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
rbind(cworknotpaid_c_u_r$b_u, cworknotpaid_c_u_r$b_r) %>% 
  final_u_r_tbl(1, "Both sexes", "Unpaid work and unemployed by type of settlement", 8)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# region
cworknotpaid_c$b_reg %>% apply_hux(.col_names = cworknotpaid_c_reg_col_names) %>% 
  final_m_w_b_tbl(1, "Both sexes", "Unpaid work and unemployed by region", 8) 
```

<br>

**Analysis information**:

- Questions used: C8
- R script name: Cworknotpaid

***

<br>
<br>
