---
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  word_document: default
---

```{r setup, include=FALSE}
library(here)
library(huxtable)
library(tidyverse)
library(fs)
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
# Set a root directory for all chunks to be evaluated relative to rather than the document location
knitr::opts_knit$set(root.dir = here())
```

```{r source, include=FALSE}
here("DataBook", "Modules", "DepressionModuleWHS") %>% 
  # list all R files in the directory
  fs::dir_ls(regexp = "\\.R$") %>% 
  # scale up to all R files with a map function from purrr
  map(source, encoding = "UTF-8", local = knitr::knit_global())
```

---
title: "`r set_title`"
author: "`r set_author`"
---


# Depression

**WHS algorithm**

Description: Percentage of respondents who have depressive symptoms based on the World Health Survey (WHS) algorithm/cascade.

Instrument questions:

- Have you ever been told by a doctor or other health worker that you have depression?
- When were you diagnosed?
- How many years passed since your doctor or health care provider told you for the first time that you have depression?
- Have you been taking any medications or other treatment, like counseling or psychotherapy, either alone or in group, for depression in the last 12 months?
- Have you been taking any medications or other treatment, like counseling or psychotherapy, either alone or in group, for depression in the last 2 weeks?
- During the last 12 months, have you had a period lasting several days when you felt sad, empty or depressed?
- During the last 12 months, have you had a period lasting several days when you lost interest in most things you usually enjoy such as personal relationships, work or hobbies/recreation?
- During the last 12 months, have you had a period lasting several days when you have been feeling your energy decreased or that you are tired all the time?
- Was this period of sadness, loss of interest or low energy for more than 2 weeks?
- Was this period of sadness, loss of interest or low energy most of the day, nearly every day?

During this period:

- Did you lose your appetite?
- Did you notice any slowing down in your thinking?
- Did you notice any problems falling asleep?
- Did you notice any problems waking up too early?
- Did you have any difficulties concentrating; for example, listening to others, working, watching TV, listening to the radio?
- Did you notice any slowing down in your moving around?
- Did you feel anxious and worried most days?
- Were you so restless or jittery nearly every day that you paced up and down and couldn’t sit still?
- Did you feel negative about yourself or like you had lost confidence?
- Did you frequently feel hopeless – that there was no way to improve things?
- Did your interest in sex decrease?
- Did you think of death, or wish you were dead?
- During this period, did you ever try to end your life?

```{r whs_depression_c_tbls}
# column names to use with huxtable
whs_depression_c_col_names <- c("Age Group (years)", "n", "%", "95% CI")
whs_depression_c_reg_col_names <- c("Region", "n", "%", "95% CI")

# men, women, both sexes
whs_depression_c_m_w_b <- join_tbls(whs_depression_c, m_w_b, 1, whs_depression_c_col_names)
```
```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# urban, rural
whs_depression_c_u_r <- join_tbls(whs_depression_c, u_r, 1, whs_depression_c_col_names)
```

<br>

```{r}
cbind(whs_depression_c_m_w_b$m, select(whs_depression_c_m_w_b$w, -agerange), select(whs_depression_c_m_w_b$b, -agerange)) %>% 
  final_tbl(.disaggregation = m_w_b, .s_amount = 3, .title = "Prevalence of depressive symptoms using established WHS algorithm", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
tbl_m_u_r <- rbind(whs_depression_c_u_r$m_u, whs_depression_c_u_r$m_r)
tbl_w_u_r <- rbind(whs_depression_c_u_r$w_u, whs_depression_c_u_r$w_r)
tbl_b_u_r <- rbind(whs_depression_c_u_r$b_u, whs_depression_c_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_tbl(.disaggregation = u_r, .s_amount = 3, .title = "Prevalence of depressive symptoms using established WHS algorithm by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
whs_depression_c$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = whs_depression_c_reg_col_names) %>% 
  final_tbl(.disaggregation = reg, .s_amount = 1, .s_val = "Both sexes", .title = "Prevalence of depressive symptoms using established WHS algorithm by region", .colspan_val = 4) 
```

<br>

**Analysis information**:

- Questions used: DA1-DA23
- R script name: WHSdepression 

***


**History of depression based on WHS algorithm**

Description: Percentage of population who have been diagnosed with depression by a physician or health care professional among those that are depressed based on the WHS algorithm.

Instrument questions:

- Have you ever been told by a doctor or health care professional that you have depression?
- Various depressive symptoms

```{r da1_d_whs_tbls}
# column names to use with huxtable
da1_d_whs_col_names <- c("Age Group (years)", "n", "% Told", "95% CI")
da1_d_whs_reg_col_names <- c("Region", "n", "% Told", "95% CI")

# men, women, both sexes
da1_d_whs_m_w_b <- join_tbls(da1_d_whs, m_w_b, 1, da1_d_whs_col_names)
```
```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# urban, rural
da1_d_whs_u_r <- join_tbls(da1_d_whs, u_r, 1, da1_d_whs_col_names)
```

<br>

```{r}
cbind(da1_d_whs_m_w_b$m, select(da1_d_whs_m_w_b$w, -agerange), select(da1_d_whs_m_w_b$b, -agerange)) %>% 
  final_tbl(.disaggregation = m_w_b, .s_amount = 3, .title = "Told by a doctor or health worker that have a depression (from those that are depressed based on WHS algorithm)", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
tbl_m_u_r <- rbind(da1_d_whs_u_r$m_u, da1_d_whs_u_r$m_r)
tbl_w_u_r <- rbind(da1_d_whs_u_r$w_u, da1_d_whs_u_r$w_r)
tbl_b_u_r <- rbind(da1_d_whs_u_r$b_u, da1_d_whs_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_tbl(.disaggregation = u_r, .s_amount = 3, .title = "Told by a doctor or health worker that have a depression (from those that are depressed based on WHS algorithm) by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
da1_d_whs$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = da1_d_whs_reg_col_names) %>% 
  final_tbl(.disaggregation = reg, .s_amount = 1, .s_val = "Both sexes", .title = "Told by a doctor or health worker that have a depression (from those that are depressed based on WHS algorithm) by region", .colspan_val = 4) 
```

<br>

**Analysis information**:

- Questions used: DA1-DA23
- R script name: WHSdepression 

***


**History of depression**

Description: Percentage of the general population who have been diagnosed with depression by a physician or health care professional.

Instrument questions:

- Have you ever been told by a doctor or health care professional that you have depression?

```{r da1_d_all_tbls}
# column names to use with huxtable
da1_d_all_col_names <- c("Age Group (years)", "n", "% Told", "95% CI")
da1_d_all_reg_col_names <- c("Region", "n", "% Told", "95% CI")

# men, women, both sexes
da1_d_all_m_w_b <- join_tbls(da1_d_all, m_w_b, 1, da1_d_all_col_names)
```
```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# urban, rural
da1_d_all_u_r <- join_tbls(da1_d_all, u_r, 1, da1_d_all_col_names)
```

<br>

```{r}
cbind(da1_d_all_m_w_b$m, select(da1_d_all_m_w_b$w, -agerange), select(da1_d_all_m_w_b$b, -agerange)) %>% 
  final_tbl(.disaggregation = m_w_b, .s_amount = 3, .title = "Told by a doctor or health worker that have a depression", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
tbl_m_u_r <- rbind(da1_d_all_u_r$m_u, da1_d_all_u_r$m_r)
tbl_w_u_r <- rbind(da1_d_all_u_r$w_u, da1_d_all_u_r$w_r)
tbl_b_u_r <- rbind(da1_d_all_u_r$b_u, da1_d_all_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_tbl(.disaggregation = u_r, .s_amount = 3, .title = "Told by a doctor or health worker that have a depression by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
da1_d_all$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = da1_d_all_reg_col_names) %>% 
  final_tbl(.disaggregation = reg, .s_amount = 1, .s_val = "Both sexes", .title = "Told by a doctor or health worker that have a depression by region", .colspan_val = 4) 
```

<br>

**Analysis information**:

- Questions used: DA1
- R script name: WHSdepression

***


**Treatment of depression**

Description: Percentage of population who have been treated for depression among those with depression diagnosed by a health care worker.

Instrument questions:

- Have you been taking any medications or other treatment, like counseling or psychotherapy, either alone or in group, for depression in the last **12 months**?
- Have you been taking any medications or other treatment, like counseling or psychotherapy, either alone or in group, for depression in the last **2 weeks**?

```{r da4_e_da5_f_all_tbls}
# column names to use with huxtable
da4_e_da5_f_all_col_names <- c("Age Group (years)", "n", "% On medication", "95% CI")
da4_e_da5_f_all_reg_col_names <- c("Region", "n", "% On medication", "95% CI")

# men, women, both sexes
# 1 - Have been taking medications or other treatment for depression in the last 12 months
da4_e_all_m_w_b <- join_tbls(da4_e_all, m_w_b, 1, da4_e_da5_f_all_col_names)
# 2 - Have been taking medications or other treatment for depression in the last 2 weeks
da5_f_all_m_w_b <- join_tbls(da5_f_all, m_w_b, 1, da4_e_da5_f_all_col_names)
```
```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# urban, rural
# 1
da4_e_all_u_r <- join_tbls(da4_e_all, u_r, 1, da4_e_da5_f_all_col_names)
# 2
da5_f_all_u_r <- join_tbls(da5_f_all, u_r, 1, da4_e_da5_f_all_col_names)
```

<br>

```{r}
# 1
cbind(da4_e_all_m_w_b$m, select(da4_e_all_m_w_b$w, -agerange), select(da4_e_all_m_w_b$b, -agerange)) %>% 
  final_tbl(.disaggregation = m_w_b, .s_amount = 3, .title = "Have been taking medications or other treatment for depression in the last 12 months", .colspan_val = 10)
```

<br>

```{r}
# 2
cbind(da5_f_all_m_w_b$m, select(da5_f_all_m_w_b$w, -agerange), select(da5_f_all_m_w_b$b, -agerange)) %>% 
  final_tbl(.disaggregation = m_w_b, .s_amount = 3, .title = "Have been taking medications or other treatment for depression in the last 2 weeks", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 1
tbl_m_u_r <- rbind(da4_e_all_u_r$m_u, da4_e_all_u_r$m_r)
tbl_w_u_r <- rbind(da4_e_all_u_r$w_u, da4_e_all_u_r$w_r)
tbl_b_u_r <- rbind(da4_e_all_u_r$b_u, da4_e_all_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_tbl(.disaggregation = u_r, .s_amount = 3, .title = "Have been taking medications or other treatment for depression in the last 12 months by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 2
tbl_m_u_r <- rbind(da5_f_all_u_r$m_u, da5_f_all_u_r$m_r)
tbl_w_u_r <- rbind(da5_f_all_u_r$w_u, da5_f_all_u_r$w_r)
tbl_b_u_r <- rbind(da5_f_all_u_r$b_u, da5_f_all_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_tbl(.disaggregation = u_r, .s_amount = 3, .title = "Have been taking medications or other treatment for depression in the last 2 weeks by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 1
da4_e_all$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = da4_e_da5_f_all_reg_col_names) %>% 
  final_tbl(.disaggregation = reg, .s_amount = 1, .s_val = "Both sexes", .title = "Have been taking medications or other treatment for depression in the last 12 months by region", .colspan_val = 4) 
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 2
da5_f_all$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = da4_e_da5_f_all_reg_col_names) %>% 
  final_tbl(.disaggregation = reg, .s_amount = 1, .s_val = "Both sexes", .title = "Have been taking medications or other treatment for depression in the last 2 weeks by region", .colspan_val = 4) 
```

<br>

**Analysis information**:

- Questions used: DA4, DA5
- R script name: WHSdepression

***


**Suicidal thoughts based on WHS algorithm**

Description: Percentage of population who have thought of death, or wished they were dead, during the last 12 months among those that are depressed based on the WHS algorithm.

Instrument questions:

- Did you think of death, or wish you were dead?

```{r da22_g_whs_tbls}
# column names to use with huxtable
da22_g_whs_col_names <- c("Age Group (years)", "n", "% Thought", "95% CI")
da22_g_whs_reg_col_names <- c("Region", "n", "% Thought", "95% CI")

# men, women, both sexes
da22_g_whs_m_w_b <- join_tbls(da22_g_whs, m_w_b, 1, da22_g_whs_col_names)
```
```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# urban, rural
da22_g_whs_u_r <- join_tbls(da22_g_whs, u_r, 1, da22_g_whs_col_names)
```

<br>

```{r}
cbind(da22_g_whs_m_w_b$m, select(da22_g_whs_m_w_b$w, -agerange), select(da22_g_whs_m_w_b$b, -agerange)) %>% 
  final_tbl(.disaggregation = m_w_b, .s_amount = 3, .title = "Thought of death, or wished they were dead, during the last 12 months (from those that are depressed based on WHS algorithm)", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
tbl_m_u_r <- rbind(da22_g_whs_u_r$m_u, da22_g_whs_u_r$m_r)
tbl_w_u_r <- rbind(da22_g_whs_u_r$w_u, da22_g_whs_u_r$w_r)
tbl_b_u_r <- rbind(da22_g_whs_u_r$b_u, da22_g_whs_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_tbl(.disaggregation = u_r, .s_amount = 3, .title = "Thought of death, or wished they were dead, during the last 12 months (from those that are depressed based on WHS algorithm) by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
da22_g_whs$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = da22_g_whs_reg_col_names) %>% 
  final_tbl(.disaggregation = reg, .s_amount = 1, .s_val = "Both sexes", .title = "Thought of death, or wished they were dead, during the last 12 months (from those that are depressed based on WHS algorithm) by region", .colspan_val = 4) 
```

<br>

**Analysis information**:

- Questions used: DA1-DA23
- R script name: WHSdepression

***

<br>
<br>
