---
title: "STEPS MDA Data Book"
author: "WHO NCD Office Moscow"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  word_document: default
  html_document:
    css: style.css
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
library(here)
library(huxtable)
library(tidyverse)
library(fs)
```

```{r source, include=FALSE}
diet_data_dir <- here::here("DataBook", "Modules", "Diet")

# read in each R file, because in MDA not all scripts are used
source(here::here(diet_data_dir, "DX1.R"))
source(here::here(diet_data_dir, "Ddays.R"))
source(here::here(diet_data_dir, "Dservings.R"))
source(here::here(diet_data_dir, "Dfiveormore.R"))

```

```{r databook_functions, echo=FALSE}
source(here("DataBook", "databook_functions.R"), encoding = "UTF-8", local = knitr::knit_global())
```

```{r}
m_w_b <- c("m","w","b")
u_r <- c("m_u","w_u","b_u","m_r","w_r","b_r")
```

# Diet

**Mean number of days of fruit and vegetable consumption**

Description: mean number of days fruit and vegetables consumed.

Instrument questions:

- In a typical week, on how many days do you eat fruit?
- In a typical week, on how many days do you eat vegetables?

```{r ddays_tbls}

# column names to use with huxtable
ddays_col_names <- c("Age Group (years)", "n", "Mean number of days", "95% CI")
ddays_reg_col_names <- c("Region", "n", "Mean number of days", "95% CI")

# 1. Fruit
# men, women, both sexes
ddays_d1_m_w_b <- join_m_w_b(ddays_d1, 1, ddays_col_names)
# 2. Vegetables
# men, women, both sexes
ddays_d3_m_w_b <- join_m_w_b(ddays_d3, 1, ddays_col_names)
```
```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# urban, rural
# 1. Fruit
ddays_d1_u_r <- join_u_r(ddays_d1, 1, ddays_col_names)
# 2. Vegetable
ddays_d3_u_r <- join_u_r(ddays_d3, 1, ddays_col_names)
```

<br>

```{r}
# 1. Fruit
cbind(ddays_d1_m_w_b$m, select(ddays_d1_m_w_b$w, -agerange), select(ddays_d1_m_w_b$b, -agerange)) %>% 
  final_m_w_b_tbl(.s_amount = 3, .title = "Mean number of days fruit consumed in a typical week", .colspan_val = 10)
```

<br>

```{r}
# 2. Vegetables
cbind(ddays_d3_m_w_b$m, select(ddays_d3_m_w_b$w, -agerange), select(ddays_d3_m_w_b$b, -agerange)) %>% 
  final_m_w_b_tbl(.s_amount = 3, .title = "Mean number of days vegetables consumed in a typical week", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 1. Fruit
tbl_m_u_r <- rbind(ddays_d1_u_r$m_u, ddays_d1_u_r$m_r)
tbl_w_u_r <- rbind(ddays_d1_u_r$w_u, ddays_d1_u_r$w_r)
tbl_b_u_r <- rbind(ddays_d1_u_r$b_u, ddays_d1_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_u_r_tbl(.s_amount = 3, .title = "Mean number of days fruit consumed in a typical week by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 2. Vegetables
tbl_m_u_r <- rbind(ddays_d3_u_r$m_u, ddays_d3_u_r$m_r)
tbl_w_u_r <- rbind(ddays_d3_u_r$w_u, ddays_d3_u_r$w_r)
tbl_b_u_r <- rbind(ddays_d3_u_r$b_u, ddays_d3_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_u_r_tbl(.s_amount = 3, .title = "Mean number of days vegetables consumed in a typical week by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
ddays_d1$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = ddays_reg_col_names) %>% 
  final_m_w_b_tbl(1, "Both sexes", "Mean number of days fruit consumed in a typical week by region", 4) 
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
ddays_d3$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = ddays_reg_col_names) %>% 
  final_m_w_b_tbl(1, "Both sexes", "Mean number of days vegetables consumed in a typical week by region", 4) 
```

<br>

**Analysis information**:

- Questions used: D1, D3
- R script name: Ddays

***

**Mean number of servings of fruit and vegetable consumption**

Description: mean number of fruit, vegetable, and combined fruit and vegetable servings on average per day.

Instrument questions:

- In a typical week, on how many days do you eat fruit?
- How many servings of fruit do you eat on one of those days?
- In a typical week, on how many days do you eat vegetables?
- How many servings of vegetables do you eat on one of those days?

```{r dservings_tbls}

# column names to use with huxtable
dservings_col_names <- c("Age Group (years)", "n", "Mean number of servings", "95% CI")
dservings_reg_col_names <- c("Region", "n", "Mean number of servings", "95% CI")

# 1. Fruit
# men, women, both sexes
fservings_tbls_m_w_b <- join_m_w_b(fservings_tbls, 1, dservings_col_names)
# 2. Vegetables
# men, women, both sexes
vservings_tbls_m_w_b <- join_m_w_b(vservings_tbls, 1, dservings_col_names)
# 3. Fruit and/or vegetables
# men, women, both sexes
fvservings_tbls_m_w_b <- join_m_w_b(fvservings_tbls, 1, dservings_col_names)
```
```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# urban, rural
# 1. Fruit
fservings_tbls_u_r <- join_u_r(fservings_tbls, 1, dservings_col_names)
# 2. Vegetable
vservings_tbls_u_r <- join_u_r(vservings_tbls, 1, dservings_col_names)
# 3. Fruit and/or vegetables
fvservings_tbls_u_r <- join_u_r(fvservings_tbls, 1, dservings_col_names)
```

<br>

```{r}
# 1. Fruit
cbind(fservings_tbls_m_w_b$m, select(fservings_tbls_m_w_b$w, -agerange), select(fservings_tbls_m_w_b$b, -agerange)) %>% 
  final_m_w_b_tbl(.s_amount = 3, .title = "Mean number of servings of fruit on average per day", .colspan_val = 10)
```

<br>

```{r}
# 2. Vegetables
cbind(vservings_tbls_m_w_b$m, select(vservings_tbls_m_w_b$w, -agerange), select(vservings_tbls_m_w_b$b, -agerange)) %>% 
  final_m_w_b_tbl(.s_amount = 3, .title = "Mean number of servings of vegetables on average per day", .colspan_val = 10)
```

<br>

```{r}
# 3. Fruit and/or vegetables
cbind(fvservings_tbls_m_w_b$m, select(fvservings_tbls_m_w_b$w, -agerange), select(fvservings_tbls_m_w_b$b, -agerange)) %>% 
  final_m_w_b_tbl(.s_amount = 3, .title = "Mean number of servings of fruit and/or vegetables on average per day", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 1. Fruit
tbl_m_u_r <- rbind(fservings_tbls_u_r$m_u, fservings_tbls_u_r$m_r)
tbl_w_u_r <- rbind(fservings_tbls_u_r$w_u, fservings_tbls_u_r$w_r)
tbl_b_u_r <- rbind(fservings_tbls_u_r$b_u, fservings_tbls_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_u_r_tbl(.s_amount = 3, .title = "Mean number of servings of fruit on average per day by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 2. Vegetables
tbl_m_u_r <- rbind(vservings_tbls_u_r$m_u, vservings_tbls_u_r$m_r)
tbl_w_u_r <- rbind(vservings_tbls_u_r$w_u, vservings_tbls_u_r$w_r)
tbl_b_u_r <- rbind(vservings_tbls_u_r$b_u, vservings_tbls_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_u_r_tbl(.s_amount = 3, .title = "Mean number of servings of vegetables on average per day by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 3. Fruit and/or vegetables
tbl_m_u_r <- rbind(fvservings_tbls_u_r$m_u, fvservings_tbls_u_r$m_r)
tbl_w_u_r <- rbind(fvservings_tbls_u_r$w_u, fvservings_tbls_u_r$w_r)
tbl_b_u_r <- rbind(fvservings_tbls_u_r$b_u, fvservings_tbls_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_u_r_tbl(.s_amount = 3, .title = "Mean number of servings of fruit and/or vegetables on average per day by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 1. Fruit
fservings_tbls$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = dservings_reg_col_names) %>% 
  final_m_w_b_tbl(1, "Both sexes", "Mean number of servings of fruit on average per day by region", 4) 
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 2. Veges
vservings_tbls$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = dservings_reg_col_names) %>% 
  final_m_w_b_tbl(1, "Both sexes", "Mean number of servings of vegetables on average per day by region", 4) 
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 3. Fruit and/or veges
fvservings_tbls$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = dservings_reg_col_names) %>% 
  final_m_w_b_tbl(1, "Both sexes", "Mean number of servings of fruit and/or vegetables on average per day by region", 4) 
```

<br>

**Analysis information**:

- Questions used: D1, D2, D3, D4
- R script name: Dservings

***

**Fruit and vegetable consumption per day**

Description: Frequency of fruit and/or vegetable consumption.

Instrument questions:

- In a typical week, on how many days do you eat fruit?
- How many servings of fruit do you eat on one of those days?
- In a typical week, on how many days do you eat vegetables?
- How many servings of vegetables do you eat on one of those days?

```{r dfiveormore_d_tbls}

# column names to use with huxtable
dfiveormore_d_col_names <- c("Age Group (years)", "n", "% no fruit and/or vegetables", "95% CI", 
                             "% 1-2 servings", "95% CI", "% 3-4 servings ", "95% CI", "% ≥5 servings", "95% CI")

# column names for region to use with huxtable
dfiveormore_d_reg_col_names <- c("Region", "n", "% no fruit and/or vegetables", "95% CI", 
                                 "% 1-2 servings", "95% CI", "% 3-4 servings ", "95% CI", "% ≥5 servings", "95% CI")

# men, women, both sexes
dfiveormore_d_m_w_b <- join_m_w_b(dfiveormore_d, 4, dfiveormore_d_col_names)
```
```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# urban, rural
dfiveormore_d_u_r <- join_u_r(dfiveormore_d, 4, dfiveormore_d_col_names)
```

<br>

```{r}
dfiveormore_d_m_w_b$m %>% final_m_w_b_tbl(1, "Men", "Number of servings of fruit and/or vegetables on average per day", 10)
```

<br>

```{r}
dfiveormore_d_m_w_b$w %>% final_m_w_b_tbl(1, "Women", "Number of servings of fruit and/or vegetables on average per day", 10)
```

<br>

```{r}
dfiveormore_d_m_w_b$b %>% final_m_w_b_tbl(1, "Both sexes", "Number of servings of fruit and/or vegetables on average per day", 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
rbind(dfiveormore_d_u_r$m_u, dfiveormore_d_u_r$m_r) %>% 
  final_u_r_tbl(1, "Men", "Number of servings of fruit and/or vegetables on average per day by type of settlement", 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
rbind(dfiveormore_d_u_r$w_u, dfiveormore_d_u_r$w_r) %>% 
  final_u_r_tbl(1, "Women", "Number of servings of fruit and/or vegetables on average per day by type of settlement", 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
rbind(dfiveormore_d_u_r$b_u, dfiveormore_d_u_r$b_r) %>% 
  final_u_r_tbl(1, "Both sexes", "Number of servings of fruit and/or vegetables on average per day by type of settlement", 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# region
dfiveormore_d$b_reg %>% unite_ci(.ci_amount = 4) %>% apply_hux(.col_names = dfiveormore_d_reg_col_names) %>% 
  final_m_w_b_tbl(1, "Both sexes", "Number of servings of fruit and/or vegetables on average per day by region", 10) 
```

<br>

**Analysis information**:

- Questions used: D1, D2, D3, D4
- R script name: Dfiveormore

***

**Fruit and vegetable consumption per day**

Description: Percentage of those eating less than five servings of fruit and/or vegetables on average per day.

Instrument questions:

- In a typical week, on how many days do you eat fruit?
- How many servings of fruit do you eat on one of those days?
- In a typical week, on how many days do you eat vegetables?
- How many servings of vegetables do you eat on one of those days?

```{r dfiveormore_c_tbls}

# column names to use with huxtable
dfiveormore_c_col_names <- c("Age Group (years)", "n", "% < five servings per day", "95% CI")
dfiveormore_c_reg_col_names <- c("Region", "n", "% < five servings per day", "95% CI")

# men, women, both sexes
dfiveormore_c_m_w_b <- join_m_w_b(dfiveormore_c, 1, dfiveormore_c_col_names)
```
```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# urban, rural
dfiveormore_c_u_r <- join_u_r(dfiveormore_c, 1, dfiveormore_c_col_names)
```

<br>

```{r}
cbind(dfiveormore_c_m_w_b$m, select(dfiveormore_c_m_w_b$w, -agerange), select(dfiveormore_c_m_w_b$b, -agerange)) %>% 
  final_m_w_b_tbl(.s_amount = 3, .title = "Less than five servings of fruit and/or vegetables on average per day", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
tbl_m_u_r <- rbind(dfiveormore_c_u_r$m_u, dfiveormore_c_u_r$m_r)
tbl_w_u_r <- rbind(dfiveormore_c_u_r$w_u, dfiveormore_c_u_r$w_r)
tbl_b_u_r <- rbind(dfiveormore_c_u_r$b_u, dfiveormore_c_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_u_r_tbl(.s_amount = 3, .title = "Less than five servings of fruit and/or vegetables on average per day by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
dfiveormore_c$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = dfiveormore_c_reg_col_names) %>% 
  final_m_w_b_tbl(1, "Both sexes", "Less than five servings of fruit and/or vegetables on average per day by region", 4) 
```

<br>

**Analysis information**:

- Questions used: D1, D2, D3, D4
- R script name: Dfiveormore

***

**Drinking sugared soft drinks**

Description: How often people drink sugared beverages, excluding light, diet and non-sugar beverages.

Instrument questions:

- How often do you drink sugared soft drinks (for example, Coca Cola, Pepsi, Fanta, Sprite, Mirinda, Kvas, Baikal, Buratino, Tarkhun etc.), bottled ice tea (for example, Nestea, Lipton Ice Tea, etc.) and sugar sweetened compote, sweet mors? Exclude light, diet and non-sugar drinks.

```{r dx1_tbls, echo=FALSE}
# column names to use with huxtable
dx1_col_names <- c("Age Group (years)", "n", "% Once or more a day", "95% CI", "% 4 to 6 times a week", "95% CI", 
                   "% 1 to 3 times a week", "95% CI", "% Less than once a week", "95% CI", "% Never", "95% CI")

# column names for region to use with huxtable
dx1_reg_col_names <- c("Region", "n", "% Once or more a day", "95% CI", "% 4 to 6 times a week", "95% CI", 
                       "% 1 to 3 times a week", "95% CI", "% Less than once a week", "95% CI", "% Never", "95% CI")

# men, women, both sexes
dx1_c_m_w_b <- join_m_w_b(dx1_c, 5, dx1_col_names)
```
```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# urban, rural
dx1_c_u_r <- join_u_r(dx1_c, 5, dx1_col_names)
```

<br>

```{r}
dx1_c_m_w_b$m %>% final_m_w_b_tbl(.s_amount = 1, .s_val = "Men", .title = "Drinking sugared soft drinks", .colspan_val = 12)
```

<br>

```{r}
dx1_c_m_w_b$w %>% final_m_w_b_tbl(.s_amount = 1, .s_val = "Women", .title = "Drinking sugared soft drinks", .colspan_val = 12)
```

<br>

```{r}
dx1_c_m_w_b$b %>% final_m_w_b_tbl(.s_amount = 1, .s_val = "Both sexes", .title = "Drinking sugared soft drinks", .colspan_val = 12)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
rbind(dx1_c_u_r$m_u, dx1_c_u_r$m_r) %>% 
  final_u_r_tbl(.s_amount = 1, .s_val = "Men", .title = "Drinking sugared soft drinks by type of settlement", .colspan_val = 12)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
rbind(dx1_c_u_r$w_u, dx1_c_u_r$w_r) %>% 
  final_u_r_tbl(.s_amount = 1, .s_val = "Women", .title = "Drinking sugared soft drinks by type of settlement", .colspan_val = 12)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
rbind(dx1_c_u_r$b_u, dx1_c_u_r$b_r) %>% 
  final_u_r_tbl(.s_amount = 1, .s_val = "Both sexes", .title = "Drinking sugared soft drinks by type of settlement", .colspan_val = 12)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# region
dx1_c$b_reg %>% unite_ci(.ci_amount = 5) %>% apply_hux(.col_names = dx1_reg_col_names) %>% 
  final_m_w_b_tbl(.s_amount = 1, .s_val = "Both sexes", .title = "Drinking sugared soft drinks by region", .colspan_val = 12)
```

<br>

**Analysis information**:

- Questions used: DX1
- R script name: DX1

***



<br>
<br>
