---
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  word_document: default
---

```{r setup, include=FALSE}
library(here)
library(huxtable)
library(tidyverse)
library(fs)
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
# Set a root directory for all chunks to be evaluated relative to rather than the document location
knitr::opts_knit$set(root.dir = here())
```

```{r source, include=FALSE}
here("DataBook", "Modules", "HistoryofRaisedTotalCholesterol") %>% 
  # list all R files in the directory
  fs::dir_ls(regexp = "\\.R$") %>% 
  # scale up to all R files with a map function from purrr
  map(source, encoding = "UTF-8", local = knitr::knit_global())
```

---
title: "`r set_title`"
author: "`r set_author`"
---


# History of Raised Total Cholesterol

**Cholesterol measurement and diagnosis**

Description: Total cholesterol measurement and diagnosis among all respondents.

Instrument questions:

- Have you ever had your cholesterol (fat levels in your blood) measured by a doctor or other health worker?
- Have you ever been told by a doctor or other health worker that you have raised cholesterol?
- Have you been told in the past 12 months?

```{r hchol_c_tbls}

# column names to use with huxtable
hchol_c_col_names <- 
  c("Age Group (years)", "n", "% Never measured", "95% CI", "% Measured, not diagnosed", "95% CI", 
    "% Diagnosed, but not within past 12 months", "95% CI", "% Diagnosed within past 12 months", "95% CI")

# column names for region to use with huxtable
hchol_c_reg_col_names <- 
  c("Region", "n", "% Never measured", "95% CI", "% Measured, not diagnosed", "95% CI", 
    "% Diagnosed, but not within past 12 months", "95% CI", "% Diagnosed within past 12 months", "95% CI")

# men, women, both sexes
hchol_c_m_w_b <- join_tbls(hchol_c, m_w_b, 4, hchol_c_col_names)
```
```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# urban, rural
hchol_c_u_r <- join_tbls(hchol_c, u_r, 4, hchol_c_col_names)
```

<br>

```{r}
hchol_c_m_w_b$m %>% final_tbl(m_w_b, 1, "Men", "Total cholesterol measurement and diagnosis", 10)
```

<br>

```{r}
hchol_c_m_w_b$w %>% final_tbl(m_w_b, 1, "Women", "Total cholesterol measurement and diagnosis", 10)
```

<br>

```{r}
hchol_c_m_w_b$b %>% final_tbl(m_w_b, 1, "Both sexes", "Total cholesterol measurement and diagnosis", 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
rbind(hchol_c_u_r$m_u, hchol_c_u_r$m_r) %>% 
  final_u_r_tbl(1, "Men", "Total cholesterol measurement and diagnosis by type of settlement", 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
rbind(hchol_c_u_r$w_u, hchol_c_u_r$w_r) %>% 
  final_u_r_tbl(1, "Women", "Total cholesterol measurement and diagnosis by type of settlement", 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
rbind(hchol_c_u_r$b_u, hchol_c_u_r$b_r) %>% 
  final_u_r_tbl(1, "Both sexes", "Total cholesterol measurement and diagnosis by type of settlement", 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# region
hchol_c$b_reg %>% unite_ci(.ci_amount = 4) %>% apply_hux(.col_names = hchol_c_reg_col_names) %>% 
  final_tbl(reg, 1, "Both sexes", "Total cholesterol measurement and diagnosis by region", 10) 
```

<br>

**Analysis information**:

-   Questions used: H12, H13a, H13b
-   R script name: Hchol

***

**Cholesterol treatment among those diagnosed**

Description: Cholesterol treatment results among those previously diagnosed with raised cholesterol.

Instrument questions:

- Have you ever had your cholesterol (fat levels in your blood) measured by a doctor or other health worker?
- Have you ever been told by a doctor or other health worker that you have raised cholesterol?
- In the past two weeks, have you taken oral treatment (medication) for raised total cholesterol prescribed by a doctor or other health worker?

```{r hchol_d_tbls}

# column names to use with huxtable
hchol_d_col_names <- c("Age Group (years)", "n", "% Taking meds", "95% CI")
hchol_d_reg_col_names <- c("Region", "n", "% Taking meds", "95% CI")

# men, women, both sexes
hchol_d_m_w_b <- join_tbls(hchol_d, m_w_b, 1, hchol_d_col_names)
```
```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# urban, rural
hchol_d_u_r <- join_tbls(hchol_d, u_r, 1, hchol_d_col_names)
```

<br>

```{r}
cbind(hchol_d_m_w_b$m, select(hchol_d_m_w_b$w, -agerange), select(hchol_d_m_w_b$b, -agerange)) %>% 
  final_tbl(.disaggregation = m_w_b, .s_amount = 3, .title = "Currently taking oral treatment (medication) prescribed for raised total cholesterol among those previously diagnosed", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
tbl_m_u_r <- rbind(hchol_d_u_r$m_u, hchol_d_u_r$m_r)
tbl_w_u_r <- rbind(hchol_d_u_r$w_u, hchol_d_u_r$w_r)
tbl_b_u_r <- rbind(hchol_d_u_r$b_u, hchol_d_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_u_r_tbl(.s_amount = 3, .title = "Currently taking oral treatment (medication) prescribed for raised total cholesterol among those previously diagnosed by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
hchol_d$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = hchol_d_reg_col_names) %>% 
  final_tbl(reg, 1, "Both sexes", "Currently taking oral treatment (medication) prescribed for raised total cholesterol among those previously diagnosed by region", 4)
```

<br>

**Analysis information**:

-   Questions used: H12, H13a, H14
-   R script name: Hchol

***

**Cholesterol advice by traditional healer**

Description: Percentage of respondents who are have sought advice or treatment from a traditional healer for raised cholesterol among those previously diagnosed.

Instrument questions:

- Have you ever had your cholesterol (fat levels in your blood) measured by a doctor or other health worker?
- Have you ever been told by a doctor or other health worker that you have raised cholesterol?
- Have you ever seen a traditional healer for raised cholesterol?
- Are you currently taking any herbal or traditional remedy for your raised cholesterol?

```{r hcholtrad_c_d_duration_tbls}

# column names to use with huxtable
hcholtrad_c_col_names <- c("Age Group (years)", "n", "% Seen trad. healer", "95% CI")
hcholtrad_c_reg_col_names <- c("Region", "n", "% Seen trad. healer", "95% CI")
hcholtrad_d_col_names <- c("Age Group (years)", "n", "% Taking trad. meds", "95% CI")
hcholtrad_d_reg_col_names <- c("Region", "n", "% Taking trad. meds", "95% CI")

# 1 - Seen a traditional healer for raised cholesterol among those previously diagnosed
# men, women, both sexes
hcholtrad_c_m_w_b <- join_tbls(hcholtrad_c, m_w_b, 1, hcholtrad_c_col_names)

# 2 - Currently taking herbal or traditional treatment for raised cholesterol among those previously diagnosed
# men, women, both sexes
hcholtrad_d_m_w_b <- join_tbls(hcholtrad_d, m_w_b, 1, hcholtrad_d_col_names)
```
```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# urban, rural
# 1 - Seen a traditional healer for raised cholesterol among those previously diagnosed
hcholtrad_c_u_r <- join_tbls(hcholtrad_c, u_r, 1, hcholtrad_c_col_names)
# 2 - Currently taking herbal or traditional treatment for raised cholesterol among those previously diagnosed
hcholtrad_d_u_r <- join_tbls(hcholtrad_d, u_r, 1, hcholtrad_d_col_names)
```

<br>

```{r}
# 1
cbind(hcholtrad_c_m_w_b$m, select(hcholtrad_c_m_w_b$w, -agerange), select(hcholtrad_c_m_w_b$b, -agerange)) %>% final_tbl(.disaggregation = m_w_b, .s_amount = 3, .title = "Seen a traditional healer for raised cholesterol among those previously diagnosed", .colspan_val = 10)
```

<br>

```{r}
# 2
cbind(hcholtrad_d_m_w_b$m, select(hcholtrad_d_m_w_b$w, -agerange), select(hcholtrad_d_m_w_b$b, -agerange)) %>% final_tbl(.disaggregation = m_w_b, .s_amount = 3, .title = "Currently taking herbal or traditional treatment for raised cholesterol among those previously diagnosed", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 1
tbl_m_u_r <- rbind(hcholtrad_c_u_r$m_u, hcholtrad_c_u_r$m_r)
tbl_w_u_r <- rbind(hcholtrad_c_u_r$w_u, hcholtrad_c_u_r$w_r)
tbl_b_u_r <- rbind(hcholtrad_c_u_r$b_u, hcholtrad_c_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_u_r_tbl(.s_amount = 3, .title = "Seen a traditional healer for raised cholesterol among those previously diagnosed by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 2
tbl_m_u_r <- rbind(hcholtrad_d_u_r$m_u, hcholtrad_d_u_r$m_r)
tbl_w_u_r <- rbind(hcholtrad_d_u_r$w_u, hcholtrad_d_u_r$w_r)
tbl_b_u_r <- rbind(hcholtrad_d_u_r$b_u, hcholtrad_d_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_u_r_tbl(.s_amount = 3, .title = "Currently taking herbal or traditional treatment for raised cholesterol among those previously diagnosed by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 1
hcholtrad_c$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = hcholtrad_c_reg_col_names) %>% final_tbl(reg, 1, "Both sexes", "Seen a traditional healer for raised cholesterol among those previously diagnosed by region", 4)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 2
hcholtrad_d$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = hcholtrad_d_reg_col_names) %>% final_tbl(reg, 1, "Both sexes", "Currently taking herbal or traditional treatment for raised cholesterol among those previously diagnosed by region", 4)
```

<br>

**Analysis information**:

-   Questions used: H12, H13a, H15, H16
-   R script name: Hcholtrad

***

<br> 

<br>
