---
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  word_document: default
---

```{r setup, include=FALSE}
library(here)
library(huxtable)
library(tidyverse)
library(fs)
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
# Set a root directory for all chunks to be evaluated relative to rather than the document location
knitr::opts_knit$set(root.dir = here())
```

```{r source, include=FALSE}
here("DataBook", "Modules", "HistoryofCardiovascularDiseases") %>% 
  # list all R files in the directory
  fs::dir_ls(regexp = "\\.R$") %>% 
  # scale up to all R files with a map function from purrr
  map(source, encoding = "UTF-8", local = knitr::knit_global())
```

---
title: "`r set_title`"
author: "`r set_author`"
---


# History of Cardiovascular Diseases

**History of cardiovascular diseases**

Description: Percentage of respondents who have ever had a heart attack or chest pain from heart disease (angina) or a stroke among all respondents.

Instrument questions:

- Have you ever had a heart attack or chest pain from heart disease (angina) or a stroke (cerebrovascular accident or incident)?

```{r hcvd_c_tbls}

# column names to use with huxtable
hcvd_c_col_names <- c("Age Group (years)", "n", "% CVD history", "95% CI")
hcvd_c_reg_col_names <- c("Region", "n", "% CVD history", "95% CI")

# men, women, both sexes
hcvd_c_m_w_b <- join_tbls(hcvd_c, m_w_b, 1, hcvd_c_col_names)
```
```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# urban, rural
hcvd_c_u_r <- join_tbls(hcvd_c, u_r, 1, hcvd_c_col_names)
```

<br>

```{r}
cbind(hcvd_c_m_w_b$m, select(hcvd_c_m_w_b$w, -agerange), select(hcvd_c_m_w_b$b, -agerange)) %>% 
  final_tbl(.disaggregation = m_w_b, .s_amount = 3, .title = "Having ever had a heart attack or chest pain from heart disease or a stroke", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
tbl_m_u_r <- rbind(hcvd_c_u_r$m_u, hcvd_c_u_r$m_r)
tbl_w_u_r <- rbind(hcvd_c_u_r$w_u, hcvd_c_u_r$w_r)
tbl_b_u_r <- rbind(hcvd_c_u_r$b_u, hcvd_c_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_tbl(.disaggregation = u_r, .s_amount = 3, .title = "Having ever had a heart attack or chest pain from heart disease or a stroke by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
hcvd_c$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = hcvd_c_reg_col_names) %>% 
  final_tbl(.disaggregation = reg, 1, "Both sexes", "Having ever had a heart attack or chest pain from heart disease or a stroke by region", 4)
```

<br>

**Analysis information**:

-   Questions used: H17
-   R script name: Hcvd

***

**Prevention and treatment of heart disease**

Description: Percentage of respondents who are currently taking aspirin or statins regularly to prevent or treat heart disease.

Instrument questions:

- Are you currently taking aspirin regularly to prevent or treat heart disease?
- Are you currently taking statins (Lovostatin/Simvastatin/Atorvastatin or any other statin) regularly to prevent or treat heart disease?

```{r hcvdmeds_c_d_duration_tbls}

# column names to use with huxtable
hcvdmeds_c_col_names <- c("Age Group (years)", "n", "% Taking aspirin", "95% CI")
hcvdmeds_c_reg_col_names <- c("Region", "n", "% Taking aspirin", "95% CI")
hcvdmeds_d_col_names <- c("Age Group (years)", "n", "% Taking statins", "95% CI")
hcvdmeds_d_reg_col_names <- c("Region", "n", "% Taking statins", "95% CI")

# 1 - Currently taking aspirin regularly to prevent or treat heart disease
# men, women, both sexes
hcvdmeds_c_m_w_b <- join_tbls(hcvdmeds_c, m_w_b, 1, hcvdmeds_c_col_names)

# 2 - Currently taking statins regularly to prevent or treat heart disease
# men, women, both sexes
hcvdmeds_d_m_w_b <- join_tbls(hcvdmeds_d, m_w_b, 1, hcvdmeds_d_col_names)
```
```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# urban, rural
# 1 - Currently taking aspirin regularly to prevent or treat heart disease
hcvdmeds_c_u_r <- join_tbls(hcvdmeds_c, u_r, 1, hcvdmeds_c_col_names)
# 2 - Currently taking statins regularly to prevent or treat heart disease
hcvdmeds_d_u_r <- join_tbls(hcvdmeds_d, u_r, 1, hcvdmeds_d_col_names)
```

<br>

```{r}
# 1
cbind(hcvdmeds_c_m_w_b$m, select(hcvdmeds_c_m_w_b$w, -agerange), select(hcvdmeds_c_m_w_b$b, -agerange)) %>% final_tbl(.disaggregation = m_w_b, .s_amount = 3, .title = "Currently taking aspirin regularly to prevent or treat heart disease", .colspan_val = 10)
```

<br>

```{r}
# 2
cbind(hcvdmeds_d_m_w_b$m, select(hcvdmeds_d_m_w_b$w, -agerange), select(hcvdmeds_d_m_w_b$b, -agerange)) %>% final_tbl(.disaggregation = m_w_b, .s_amount = 3, .title = "Currently taking statins regularly to prevent or treat heart disease", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 1
tbl_m_u_r <- rbind(hcvdmeds_c_u_r$m_u, hcvdmeds_c_u_r$m_r)
tbl_w_u_r <- rbind(hcvdmeds_c_u_r$w_u, hcvdmeds_c_u_r$w_r)
tbl_b_u_r <- rbind(hcvdmeds_c_u_r$b_u, hcvdmeds_c_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_tbl(.disaggregation = u_r, .s_amount = 3, .title = "Currently taking aspirin regularly to prevent or treat heart disease by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 2
tbl_m_u_r <- rbind(hcvdmeds_d_u_r$m_u, hcvdmeds_d_u_r$m_r)
tbl_w_u_r <- rbind(hcvdmeds_d_u_r$w_u, hcvdmeds_d_u_r$w_r)
tbl_b_u_r <- rbind(hcvdmeds_d_u_r$b_u, hcvdmeds_d_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_tbl(.disaggregation = u_r, .s_amount = 3, .title = "Currently taking statins regularly to prevent or treat heart disease by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 1
hcvdmeds_c$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = hcvdmeds_c_reg_col_names) %>% final_tbl(.disaggregation = reg, 1, "Both sexes", "Currently taking aspirin regularly to prevent or treat heart disease by region", 4)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 2
hcvdmeds_d$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = hcvdmeds_d_reg_col_names) %>% final_tbl(.disaggregation = reg, 1, "Both sexes", "Currently taking statins regularly to prevent or treat heart disease by region", 4)
```

<br>

**Analysis information**:

-   Questions used: H18, H19
-   R script name: Hcvdmeds

***

**Prevention and treatment of heart disease**

Description: Percentage of respondents **with CVD** who are currently taking aspirin or statins regularly to prevent or treat heart disease.

Instrument questions:

- Have you ever had a heart attack or chest pain from heart disease (angina) or a stroke (cerebrovascular accident or incident)?
- Are you currently taking aspirin regularly to prevent or treat heart disease?
- Are you currently taking statins (Lovostatin/Simvastatin/Atorvastatin or any other statin) regularly to prevent or treat heart disease?

```{r hcvdmeds_h17_c_d_duration_tbls}

# column names to use with huxtable
hcvdmeds_h17_c_col_names <- c("Age Group (years)", "n", "% Taking aspirin", "95% CI")
hcvdmeds_h17_c_reg_col_names <- c("Region", "n", "% Taking aspirin", "95% CI")
hcvdmeds_h17_d_col_names <- c("Age Group (years)", "n", "% Taking statins", "95% CI")
hcvdmeds_h17_d_reg_col_names <- c("Region", "n", "% Taking statins", "95% CI")

# 1 - Respondents with CVD currently taking aspirin
# men, women, both sexes
hcvdmeds_h17_c_m_w_b <- join_tbls(hcvdmeds_h17_c, m_w_b, 1, hcvdmeds_h17_c_col_names)

# 2 - Respondents with CVD currently taking statins
# men, women, both sexes
hcvdmeds_h17_d_m_w_b <- join_tbls(hcvdmeds_h17_d, m_w_b, 1, hcvdmeds_h17_d_col_names)
```
```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# urban, rural
# 1 - Respondents with CVD currently taking aspirin
hcvdmeds_h17_c_u_r <- join_tbls(hcvdmeds_h17_c, u_r, 1, hcvdmeds_h17_c_col_names)
# 2 - Respondents with CVD currently taking statins
hcvdmeds_h17_d_u_r <- join_tbls(hcvdmeds_h17_d, u_r, 1, hcvdmeds_h17_d_col_names)
```

<br>

```{r}
# 1
cbind(hcvdmeds_h17_c_m_w_b$m, select(hcvdmeds_h17_c_m_w_b$w, -agerange), select(hcvdmeds_h17_c_m_w_b$b, -agerange)) %>% final_tbl(.disaggregation = m_w_b, .s_amount = 3, .title = "Respondents with CVD currently taking aspirin", .colspan_val = 10)
```

<br>

```{r}
# 2
cbind(hcvdmeds_h17_d_m_w_b$m, select(hcvdmeds_h17_d_m_w_b$w, -agerange), select(hcvdmeds_h17_d_m_w_b$b, -agerange)) %>% final_tbl(.disaggregation = m_w_b, .s_amount = 3, .title = "Respondents with CVD currently taking statins", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 1
tbl_m_u_r <- rbind(hcvdmeds_h17_c_u_r$m_u, hcvdmeds_h17_c_u_r$m_r)
tbl_w_u_r <- rbind(hcvdmeds_h17_c_u_r$w_u, hcvdmeds_h17_c_u_r$w_r)
tbl_b_u_r <- rbind(hcvdmeds_h17_c_u_r$b_u, hcvdmeds_h17_c_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_tbl(.disaggregation = u_r, .s_amount = 3, .title = "Respondents with CVD currently taking aspirin by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 2
tbl_m_u_r <- rbind(hcvdmeds_h17_d_u_r$m_u, hcvdmeds_h17_d_u_r$m_r)
tbl_w_u_r <- rbind(hcvdmeds_h17_d_u_r$w_u, hcvdmeds_h17_d_u_r$w_r)
tbl_b_u_r <- rbind(hcvdmeds_h17_d_u_r$b_u, hcvdmeds_h17_d_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_tbl(.disaggregation = u_r, .s_amount = 3, .title = "Respondents with CVD currently taking statins by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 1
hcvdmeds_h17_c$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = hcvdmeds_h17_c_reg_col_names) %>% final_tbl(.disaggregation = reg, 1, "Both sexes", "Respondents with CVD currently taking aspirin by region", 4)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 2
hcvdmeds_h17_d$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = hcvdmeds_h17_d_reg_col_names) %>% final_tbl(.disaggregation = reg, 1, "Both sexes", "Respondents with CVD currently taking statins by region", 4)
```

<br>

**Analysis information**:

-   Questions used: H17, H18, H19
-   R script name: Hcvdmeds

***

<br> 

<br>
