---
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  word_document: default
---

```{r setup, include=FALSE}
library(here)
library(huxtable)
library(tidyverse)
library(fs)
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
# Set a root directory for all chunks to be evaluated relative to rather than the document location
knitr::opts_knit$set(root.dir = here())
```

```{r source, include=FALSE}
here("DataBook", "Modules", "HistoryofDiabetes") %>% 
  # list all R files in the directory
  fs::dir_ls(regexp = "\\.R$") %>% 
  # scale up to all R files with a map function from purrr
  map(source, encoding = "UTF-8", local = knitr::knit_global())
```

---
title: "`r set_title`"
author: "`r set_author`"
---


# History of Diabetes

**Blood sugar measurement and diagnosis**

Description: Blood sugar measurement and diagnosis among all respondents.

Instrument questions:

- Have you ever had your blood sugar measured by a doctor or other health worker?
- Have you ever been told by a doctor or other health worker that you have raised blood sugar or diabetes?
- Have you been told in the past 12 months?

```{r hdiabetes_c_tbls}

# column names to use with huxtable
hdiabetes_c_col_names <- 
  c("Age Group (years)", "n", "% Never measured", "95% CI", "% Measured, not diagnosed", "95% CI", 
    "% Diagnosed, but not within past 12 months", "95% CI", "% Diagnosed within past 12 months", "95% CI")

# column names for region to use with huxtable
hdiabetes_c_reg_col_names <- 
  c("Region", "n", "% Never measured", "95% CI", "% Measured, not diagnosed", "95% CI", 
    "% Diagnosed, but not within past 12 months", "95% CI", "% Diagnosed within past 12 months", "95% CI")

# men, women, both sexes
hdiabetes_c_m_w_b <- join_tbls(hdiabetes_c, m_w_b, 4, hdiabetes_c_col_names)
```
```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# urban, rural
hdiabetes_c_u_r <- join_tbls(hdiabetes_c, u_r, 4, hdiabetes_c_col_names)
```

<br>

```{r}
hdiabetes_c_m_w_b$m %>% final_tbl(m_w_b, 1, "Men", "Blood sugar measurement and diagnosis", 10)
```

<br>

```{r}
hdiabetes_c_m_w_b$w %>% final_tbl(m_w_b, 1, "Women", "Blood sugar measurement and diagnosis", 10)
```

<br>

```{r}
hdiabetes_c_m_w_b$b %>% final_tbl(m_w_b, 1, "Both sexes", "Blood sugar measurement and diagnosis", 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
rbind(hdiabetes_c_u_r$m_u, hdiabetes_c_u_r$m_r) %>% 
  final_tbl(u_r, 1, "Men", "Blood sugar measurement and diagnosis by type of settlement", 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
rbind(hdiabetes_c_u_r$w_u, hdiabetes_c_u_r$w_r) %>% 
  final_tbl(u_r, 1, "Women", "Blood sugar measurement and diagnosis by type of settlement", 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
rbind(hdiabetes_c_u_r$b_u, hdiabetes_c_u_r$b_r) %>% 
  final_tbl(u_r, 1, "Both sexes", "Blood sugar measurement and diagnosis by type of settlement", 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# region
hdiabetes_c$b_reg %>% unite_ci(.ci_amount = 4) %>% apply_hux(.col_names = hdiabetes_c_reg_col_names) %>% 
  final_tbl(reg, 1, "Both sexes", "Blood sugar measurement and diagnosis by region", 10) 
```

<br>

**Analysis information**:

-   Questions used: H6, H7a, H7b
-   R script name: Hdiabetes

***

**Diabetes treatment among those diagnosed**

Description: Diabetes treatment results among those previously diagnosed with raised blood sugar or diabetes.

Instrument questions:

- Have you ever had your blood sugar measured by a doctor or other health worker?
- Have you ever been told by a doctor or other health worker that you have raised blood sugar or diabetes?
- In the past two weeks, have you taken any drugs (medication) for diabetes prescribed by a doctor or other health worker?
- Are you currently taking insulin for diabetes prescribed by a doctor or other health worker?

```{r hdiabetes_d_e_tbls}
# column names to use with huxtable
# 1 - Currently taking drugs (medication) prescribed for diabetes among those previously diagnosed
hdiabetes_d_col_names <- c("Age Group (years)", "n", "% Taking meds", "95% CI")
hdiabetes_d_reg_col_names <- c("Region", "n", "% Taking meds", "95% CI")
# 2 - Currently taking insulin prescribed for diabetes among those previously diagnosed
hdiabetes_e_col_names <- c("Age Group (years)", "n", "% Taking insulin", "95% CI")
hdiabetes_e_reg_col_names <- c("Region", "n", "% Taking insulin", "95% CI")

# men, women, both sexes
# 1
hdiabetes_d_m_w_b <- join_tbls(hdiabetes_d, m_w_b, 1, hdiabetes_d_col_names)
# 2
hdiabetes_e_m_w_b <- join_tbls(hdiabetes_e, m_w_b, 1, hdiabetes_e_col_names)
```
```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# urban, rural
# 1
hdiabetes_d_u_r <- join_tbls(hdiabetes_d, u_r, 1, hdiabetes_d_col_names)
# 2
hdiabetes_e_u_r <- join_tbls(hdiabetes_e, u_r, 1, hdiabetes_e_col_names)
```

<br>

```{r}
# 1
cbind(hdiabetes_d_m_w_b$m, select(hdiabetes_d_m_w_b$w, -agerange), select(hdiabetes_d_m_w_b$b, -agerange)) %>% 
  final_tbl(.disaggregation = m_w_b, .s_amount = 3, .title = "Currently taking drugs (medication) prescribed for diabetes among those previously diagnosed", .colspan_val = 10)
```

<br>

```{r}
# 2
cbind(hdiabetes_e_m_w_b$m, select(hdiabetes_e_m_w_b$w, -agerange), select(hdiabetes_e_m_w_b$b, -agerange)) %>% 
  final_tbl(.disaggregation = m_w_b, .s_amount = 3, .title = "Currently taking insulin prescribed for diabetes among those previously diagnosed", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 1
tbl_m_u_r <- rbind(hdiabetes_d_u_r$m_u, hdiabetes_d_u_r$m_r)
tbl_w_u_r <- rbind(hdiabetes_d_u_r$w_u, hdiabetes_d_u_r$w_r)
tbl_b_u_r <- rbind(hdiabetes_d_u_r$b_u, hdiabetes_d_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_tbl(.disaggregation = u_r, .s_amount = 3, .title = "Currently taking drugs (medication) prescribed for diabetes among those previously diagnosed by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 2
tbl_m_u_r <- rbind(hdiabetes_e_u_r$m_u, hdiabetes_e_u_r$m_r)
tbl_w_u_r <- rbind(hdiabetes_e_u_r$w_u, hdiabetes_e_u_r$w_r)
tbl_b_u_r <- rbind(hdiabetes_e_u_r$b_u, hdiabetes_e_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_tbl(.disaggregation = u_r, .s_amount = 3, .title = "Currently taking insulin prescribed for diabetes among those previously diagnosed by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 1
hdiabetes_d$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = hdiabetes_d_reg_col_names) %>% 
  final_tbl(reg, 1, "Both sexes", "Currently taking drugs (medication) prescribed for diabetes among those previously diagnosed by region", 4)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
hdiabetes_e$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = hdiabetes_e_reg_col_names) %>% 
  final_tbl(reg, 1, "Both sexes", "Currently taking insulin prescribed for diabetes among those previously diagnosed by region", 4)
```

<br>

**Analysis information**:

-   Questions used: H6, H7a, H8, H9
-   R script name: Hdiabetes

***

**Diabetes advice by traditional healer**

Description: Percentage of respondents who are have sought advice or treatment from a traditional healer for diabetes among those previously diagnosed.

Instrument questions:

- Have you ever had your blood sugar measured by a doctor or other health worker?
- Have you ever been told by a doctor or other health worker that you have raised blood sugar or diabetes?
- Have you ever seen a traditional healer for diabetes or raised blood sugar?
- Are you currently taking any herbal or traditional remedy for your diabetes?

```{r hdiabetestrad_c_d_duration_tbls}

# column names to use with huxtable
hdiabetestrad_c_col_names <- c("Age Group (years)", "n", "% Seen trad. healer", "95% CI")
hdiabetestrad_c_reg_col_names <- c("Region", "n", "% Seen trad. healer", "95% CI")
hdiabetestrad_d_col_names <- c("Age Group (years)", "n", "% Taking trad. meds ", "95% CI")
hdiabetestrad_d_reg_col_names <- c("Region", "n", "% Taking trad. meds ", "95% CI")

# 1 - Seen a traditional healer for diabetes among those previously diagnosed
# men, women, both sexes
hdiabetestrad_c_m_w_b <- join_tbls(hdiabetestrad_c, m_w_b, 1, hdiabetestrad_c_col_names)

# 2 - Currently taking herbal or traditional treatment for diabetes among those previously diagnosed
# men, women, both sexes
hdiabetestrad_d_m_w_b <- join_tbls(hdiabetestrad_d, m_w_b, 1, hdiabetestrad_d_col_names)
```
```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# urban, rural
# 1 - Seen a traditional healer for diabetes among those previously diagnosed
hdiabetestrad_c_u_r <- join_tbls(hdiabetestrad_c, u_r, 1, hdiabetestrad_c_col_names)
# 2 - Currently taking herbal or traditional treatment for diabetes among those previously diagnosed
hdiabetestrad_d_u_r <- join_tbls(hdiabetestrad_d, u_r, 1, hdiabetestrad_d_col_names)
```

<br>

```{r}
# 1
cbind(hdiabetestrad_c_m_w_b$m, select(hdiabetestrad_c_m_w_b$w, -agerange), select(hdiabetestrad_c_m_w_b$b, -agerange)) %>% final_tbl(.disaggregation = m_w_b, .s_amount = 3, .title = "Seen a traditional healer for diabetes among those previously diagnosed", .colspan_val = 10)
```

<br>

```{r}
# 2
cbind(hdiabetestrad_d_m_w_b$m, select(hdiabetestrad_d_m_w_b$w, -agerange), select(hdiabetestrad_d_m_w_b$b, -agerange)) %>% final_tbl(.disaggregation = m_w_b, .s_amount = 3, .title = "Currently taking herbal or traditional treatment for diabetes among those previously diagnosed", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 1
tbl_m_u_r <- rbind(hdiabetestrad_c_u_r$m_u, hdiabetestrad_c_u_r$m_r)
tbl_w_u_r <- rbind(hdiabetestrad_c_u_r$w_u, hdiabetestrad_c_u_r$w_r)
tbl_b_u_r <- rbind(hdiabetestrad_c_u_r$b_u, hdiabetestrad_c_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_tbl(.disaggregation = u_r, .s_amount = 3, .title = "Seen a traditional healer for diabetes among those previously diagnosed by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 2
tbl_m_u_r <- rbind(hdiabetestrad_d_u_r$m_u, hdiabetestrad_d_u_r$m_r)
tbl_w_u_r <- rbind(hdiabetestrad_d_u_r$w_u, hdiabetestrad_d_u_r$w_r)
tbl_b_u_r <- rbind(hdiabetestrad_d_u_r$b_u, hdiabetestrad_d_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_tbl(.disaggregation = u_r, .s_amount = 3, .title = "Currently taking herbal or traditional treatment for diabetes among those previously diagnosed by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 1
hdiabetestrad_c$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = hdiabetestrad_c_reg_col_names) %>% final_tbl(reg, 1, "Both sexes", "Seen a traditional healer for diabetes among those previously diagnosed by region", 4)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 2
hdiabetestrad_d$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = hdiabetestrad_d_reg_col_names) %>% final_tbl(reg, 1, "Both sexes", "Currently taking herbal or traditional treatment for diabetes among those previously diagnosed by region", 4)
```

<br>

**Analysis information**:

-   Questions used: H6, H7a, H10, H11
-   R script name: Hdiabetestrad

***

**Diabetes control via HbA1C tests**

Description: Percentage of respondents who received at least 2 HbA1C (glycated haemoglobin) tests in the past year as part of diabetes control.

Instrument questions:

- Have you ever had your blood sugar measured by a doctor or other health worker?
- Have you ever been told by a doctor or other health worker that you have raised blood sugar or diabetes?
- Have you received at least 2 HbA1C (glycated haemoglobin) tests in the past year as part of your diabetes control?

```{r hdiabetescontrol_c_tbls}

# column names to use with huxtable
hdiabetescontrol_c_col_names <- c("Age Group (years)", "n", "%", "95% CI")
hdiabetescontrol_c_reg_col_names <- c("Region", "n", "%", "95% CI")

# men, women, both sexes
hdiabetescontrol_c_m_w_b <- join_tbls(hdiabetescontrol_c, m_w_b, 1, hdiabetescontrol_c_col_names)
```
```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# urban, rural
hdiabetescontrol_c_u_r <- join_tbls(hdiabetescontrol_c, u_r, 1, hdiabetescontrol_c_col_names)
```

<br>

```{r}
cbind(hdiabetescontrol_c_m_w_b$m, select(hdiabetescontrol_c_m_w_b$w, -agerange), select(hdiabetescontrol_c_m_w_b$b, -agerange)) %>% 
  final_tbl(.disaggregation = m_w_b, .s_amount = 3, .title = "Received at least 2 HbA1C (glycated haemoglobin) tests in the past year", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
tbl_m_u_r <- rbind(hdiabetescontrol_c_u_r$m_u, hdiabetescontrol_c_u_r$m_r)
tbl_w_u_r <- rbind(hdiabetescontrol_c_u_r$w_u, hdiabetescontrol_c_u_r$w_r)
tbl_b_u_r <- rbind(hdiabetescontrol_c_u_r$b_u, hdiabetescontrol_c_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_tbl(.disaggregation = u_r, .s_amount = 3, .title = "Received at least 2 HbA1C (glycated haemoglobin) tests in the past year by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
hdiabetescontrol_c$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = hdiabetescontrol_c_reg_col_names) %>% 
  final_tbl(reg, 1, "Both sexes", "Received at least 2 HbA1C (glycated haemoglobin) tests in the past year by region", 4)
```
<br>

**Analysis information**:

-   Questions used: H6, H7a, HX1
-   R script name: Hdiabetescontrol

***


**Last examination of eyes**

Description: Last time eyes were examined as part of diabetes control.

Instrument questions:

- Have you ever had your blood sugar measured by a doctor or other health worker?
- Have you ever been told by a doctor or other health worker that you have raised blood sugar or diabetes?
- When was the last time your eyes were examined as part of your diabetes control?

```{r hdiabetescontrol_d_tbls, echo=FALSE}

# column names to use with huxtable
hdiabetescontrol_d_col_names <- c("Age Group (years)", "n", "% within the past 2 years", "95% CI",
                                  "% more than 2 years ago", "95% CI", "% never", "95% CI")

# column names for region to use with huxtable
hdiabetescontrol_d_reg_col_names <- c("Region", "n", "% within the past 2 years", "95% CI",
                                      "% more than 2 years ago", "95% CI", "% never", "95% CI")

# men, women, both sexes
hdiabetescontrol_d_m_w_b <- join_tbls(hdiabetescontrol_d, m_w_b, 3, hdiabetescontrol_d_col_names)
```
```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# urban, rural
hdiabetescontrol_d_u_r <- join_tbls(hdiabetescontrol_d, u_r, 3, hdiabetescontrol_d_col_names)
```

<br>

```{r}
hdiabetescontrol_d_m_w_b$m %>% final_tbl(.disaggregation = m_w_b, .s_amount = 1, .s_val = "Men", .title = "Last time eyes were examined as part of diabetes control", .colspan_val = 8)
```

<br>

```{r}
hdiabetescontrol_d_m_w_b$w %>% final_tbl(.disaggregation = m_w_b, .s_amount = 1, .s_val = "Women", .title = "Last time eyes were examined as part of diabetes control", .colspan_val = 8)
```

<br>

```{r}
hdiabetescontrol_d_m_w_b$b %>% final_tbl(.disaggregation = m_w_b, .s_amount = 1, .s_val = "Both sexes", .title = "Last time eyes were examined as part of diabetes control", .colspan_val = 8)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
rbind(hdiabetescontrol_d_u_r$m_u, hdiabetescontrol_d_u_r$m_r) %>% 
  final_tbl(.disaggregation = u_r, .s_amount = 1, .s_val = "Men", .title = "Last time eyes were examined as part of diabetes control by type of settlement", .colspan_val = 8) 
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
rbind(hdiabetescontrol_d_u_r$w_u, hdiabetescontrol_d_u_r$w_r) %>% 
  final_tbl(.disaggregation = u_r, .s_amount = 1, .s_val = "Women", .title = "Last time eyes were examined as part of diabetes control by type of settlement", .colspan_val = 8) 
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
rbind(hdiabetescontrol_d_u_r$b_u, hdiabetescontrol_d_u_r$b_r) %>% 
  final_tbl(.disaggregation = u_r, .s_amount = 1, .s_val = "Both sexes", .title = "Last time eyes were examined as part of diabetes control by type of settlement", .colspan_val = 8) 
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# region
hdiabetescontrol_d$b_reg %>% unite_ci(.ci_amount = 3) %>% apply_hux(.col_names = hdiabetescontrol_d_reg_col_names) %>% 
  final_tbl(.disaggregation = reg, .s_amount = 1, .s_val = "Both sexes", .title = "Last time eyes were examined as part of diabetes control by region", .colspan_val = 8)
```
<br>

**Analysis information**:

-   Questions used: H6, H7a, HX2
-   R script name: Hdiabetescontrol

***


**Last examination of feet**

Description: Last time feet were examined as part of diabetes control.

Instrument questions:

- Have you ever had your blood sugar measured by a doctor or other health worker?
- Have you ever been told by a doctor or other health worker that you have raised blood sugar or diabetes?
- When was the last time your feet were examined as part of your diabetes control?

```{r hdiabetescontrol_e_tbls, echo=FALSE}

# column names to use with huxtable
hdiabetescontrol_e_col_names <- c("Age Group (years)", "n", "% within the past 2 years", "95% CI",
                                  "% more than 2 years ago", "95% CI", "% never", "95% CI")

# column names for region to use with huxtable
hdiabetescontrol_e_reg_col_names <- c("Region", "n", "% within the past 2 years", "95% CI",
                                      "% more than 2 years ago", "95% CI", "% never", "95% CI")

# men, women, both sexes
hdiabetescontrol_e_m_w_b <- join_tbls(hdiabetescontrol_e, m_w_b, 3, hdiabetescontrol_e_col_names)
```
```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# urban, rural
hdiabetescontrol_e_u_r <- join_tbls(hdiabetescontrol_e, u_r, 3, hdiabetescontrol_e_col_names)
```

<br>

```{r}
hdiabetescontrol_e_m_w_b$m %>% final_tbl(.disaggregation = m_w_b, .s_amount = 1, .s_val = "Men", .title = "Last time feet were examined as part of diabetes control", .colspan_val = 8)
```

<br>

```{r}
hdiabetescontrol_e_m_w_b$w %>% final_tbl(.disaggregation = m_w_b, .s_amount = 1, .s_val = "Women", .title = "Last time feet were examined as part of diabetes control", .colspan_val = 8)
```

<br>

```{r}
hdiabetescontrol_e_m_w_b$b %>% final_tbl(.disaggregation = m_w_b, .s_amount = 1, .s_val = "Both sexes", .title = "Last time feet were examined as part of diabetes control", .colspan_val = 8)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
rbind(hdiabetescontrol_e_u_r$m_u, hdiabetescontrol_e_u_r$m_r) %>% 
  final_tbl(.disaggregation = u_r, .s_amount = 1, .s_val = "Men", .title = "Last time feet were examined as part of diabetes control by type of settlement", .colspan_val = 8) 
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
rbind(hdiabetescontrol_e_u_r$w_u, hdiabetescontrol_e_u_r$w_r) %>% 
  final_tbl(.disaggregation = u_r, .s_amount = 1, .s_val = "Women", .title = "Last time feet were examined as part of diabetes control by type of settlement", .colspan_val = 8) 
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
rbind(hdiabetescontrol_e_u_r$b_u, hdiabetescontrol_e_u_r$b_r) %>% 
  final_tbl(.disaggregation = u_r, .s_amount = 1, .s_val = "Both sexes", .title = "Last time feet were examined as part of diabetes control by type of settlement", .colspan_val = 8) 
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# region
hdiabetescontrol_e$b_reg %>% unite_ci(.ci_amount = 3) %>% apply_hux(.col_names = hdiabetescontrol_e_reg_col_names) %>% 
  final_tbl(.disaggregation = reg, .s_amount = 1, .s_val = "Both sexes", .title = "Last time feet were examined as part of diabetes control by region", .colspan_val = 8)
```
<br>

**Analysis information**:

-   Questions used: H6, H7a, HX3
-   R script name: Hdiabetescontrol

***

<br> 

<br>
