---
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  word_document: default
---

```{r setup, include=FALSE}
library(here)
library(huxtable)
library(tidyverse)
library(fs)
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
# Set a root directory for all chunks to be evaluated relative to rather than the document location
knitr::opts_knit$set(root.dir = here())
```

```{r source, include=FALSE}
here("DataBook", "Modules", "HistoryofRaisedBloodPressure") %>% 
  # list all R files in the directory
  fs::dir_ls(regexp = "\\.R$") %>% 
  # scale up to all R files with a map function from purrr
  map(source, encoding = "UTF-8", local = knitr::knit_global())
```

---
title: "`r set_title`"
author: "`r set_author`"
---


# History of Raised Blood Pressure

**Blood pressure measurement and diagnosis**

Description: Blood pressure measurement and diagnosis among all respondents.

Instrument questions:

- Have you ever had your blood pressure measured by a doctor or other health worker?
- Have you ever been told by a doctor or other health worker that you have raised blood pressure or hypertension?
- Have you been told in the past 12 months?

```{r hbloodpressure_c_tbls}

# column names to use with huxtable
hbloodpressure_c_col_names <- 
  c("Age Group (years)", "n", "% Never measured", "95% CI", "% Measured, not diagnosed", "95% CI", 
    "% Diagnosed, but not within past 12 months", "95% CI", "% Diagnosed within past 12 months", "95% CI")

# column names for region to use with huxtable
hbloodpressure_c_reg_col_names <- 
  c("Region", "n", "% Never measured", "95% CI", "% Measured, not diagnosed", "95% CI", 
    "% Diagnosed, but not within past 12 months", "95% CI", "% Diagnosed within past 12 months", "95% CI")

# men, women, both sexes
hbloodpressure_c_m_w_b <- join_tbls(hbloodpressure_c, m_w_b, 4, hbloodpressure_c_col_names)
```
```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# urban, rural
hbloodpressure_c_u_r <- join_tbls(hbloodpressure_c, u_r, 4, hbloodpressure_c_col_names)
```

<br>

```{r}
hbloodpressure_c_m_w_b$m %>% final_tbl(m_w_b, 1, "Men", "Blood pressure measurement and diagnosis", 10)
```

<br>

```{r}
hbloodpressure_c_m_w_b$w %>% final_tbl(m_w_b, 1, "Women", "Blood pressure measurement and diagnosis", 10)
```

<br>

```{r}
hbloodpressure_c_m_w_b$b %>% final_tbl(m_w_b, 1, "Both sexes", "Blood pressure measurement and diagnosis", 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
rbind(hbloodpressure_c_u_r$m_u, hbloodpressure_c_u_r$m_r) %>% 
  final_tbl(u_r, 1, "Men", "Blood pressure measurement and diagnosis by type of settlement", 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
rbind(hbloodpressure_c_u_r$w_u, hbloodpressure_c_u_r$w_r) %>% 
  final_tbl(u_r, 1, "Women", "Blood pressure measurement and diagnosis by type of settlement", 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
rbind(hbloodpressure_c_u_r$b_u, hbloodpressure_c_u_r$b_r) %>% 
  final_tbl(u_r, 1, "Both sexes", "Blood pressure measurement and diagnosis by type of settlement", 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# region
hbloodpressure_c$b_reg %>% unite_ci(.ci_amount = 4) %>% apply_hux(.col_names = hbloodpressure_c_reg_col_names) %>% 
  final_tbl(reg, 1, "Both sexes", "Blood pressure measurement and diagnosis by region", 10) 
```

<br>

**Analysis information**:

-   Questions used: H1, H2a, H2b
-   R script name: Hbloodpressure

***

**Blood pressure treatment among those diagnosed**

Description: Raised blood pressure treatment results among those previously diagnosed with raised blood pressure.

Instrument questions:

- Have you ever had your blood pressure measured by a doctor or other health worker?
- Have you ever been told by a doctor or other health worker that you have raised blood pressure or hypertension?
- In the past two weeks, have you taken any drugs (medication) for raised blood pressure prescribed by a doctor or other health worker?

```{r hbloodpressure_d_tbls}

# column names to use with huxtable
hbloodpressure_d_col_names <- c("Age Group (years)", "n", "% Taking meds", "95% CI")
hbloodpressure_d_reg_col_names <- c("Region", "n", "% Taking meds", "95% CI")

# men, women, both sexes
hbloodpressure_d_m_w_b <- join_tbls(hbloodpressure_d, m_w_b, 1, hbloodpressure_d_col_names)
```
```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# urban, rural
hbloodpressure_d_u_r <- join_tbls(hbloodpressure_d, u_r, 1, hbloodpressure_d_col_names)
```

<br>

```{r}
cbind(hbloodpressure_d_m_w_b$m, select(hbloodpressure_d_m_w_b$w, -agerange), select(hbloodpressure_d_m_w_b$b, -agerange)) %>% 
  final_tbl(.disaggregation = m_w_b, .s_amount = 3, .title = "Currently taking drugs (medication) for raised blood pressure prescribed by doctor or health worker among those diagnosed", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
tbl_m_u_r <- rbind(hbloodpressure_d_u_r$m_u, hbloodpressure_d_u_r$m_r)
tbl_w_u_r <- rbind(hbloodpressure_d_u_r$w_u, hbloodpressure_d_u_r$w_r)
tbl_b_u_r <- rbind(hbloodpressure_d_u_r$b_u, hbloodpressure_d_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_tbl(.disaggregation = u_r, .s_amount = 3, .title = "Currently taking drugs (medication) for raised blood pressure prescribed by doctor or health worker among those diagnosed by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
hbloodpressure_d$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = hbloodpressure_d_reg_col_names) %>% 
  final_tbl(reg, 1, "Both sexes", "Currently taking drugs (medication) for raised blood pressure prescribed by doctor or health worker among those diagnosed by region", 4)
```

<br>

**Analysis information**:

-   Questions used: H1, H2a, H3
-   R script name: Hbloodpressure

***

**Blood pressure advice by a traditional healer**

Description: Percentage of respondents who have sought advice or received treatment from a traditional healer for raised blood pressure among those previously diagnosed with raised blood pressure.

Instrument questions:

- Have you ever had your blood pressure measured by a doctor or other health worker?
- Have you ever been told by a doctor or other health worker that you have raised blood pressure or hypertension?
- Have you ever seen a traditional healer for raised blood pressure?
- Are you currently taking any herbal or traditional remedy for your high blood pressure?

```{r hraisedbptrad_c_d_duration_tbls}

# column names to use with huxtable
hraisedbptrad_c_col_names <- c("Age Group (years)", "n", "% Seen trad. healer", "95% CI")
hraisedbptrad_c_reg_col_names <- c("Region", "n", "% Seen trad. healer", "95% CI")
hraisedbptrad_d_col_names <- c("Age Group (years)", "n", "% Taking trad. meds ", "95% CI")
hraisedbptrad_d_reg_col_names <- c("Region", "n", "% Taking trad. meds ", "95% CI")

# 1 - Seen a traditional healer among those previously diagnosed
# men, women, both sexes
hraisedbptrad_c_m_w_b <- join_tbls(hraisedbptrad_c, m_w_b, 1, hraisedbptrad_c_col_names)

# 2 - Currently taking herbal or traditional remedy for raised blood pressure among those previously diagnosed
# men, women, both sexes
hraisedbptrad_d_m_w_b <- join_tbls(hraisedbptrad_d, m_w_b, 1, hraisedbptrad_d_col_names)
```
```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# urban, rural
# 1 - Seen a traditional healer among those previously diagnosed
hraisedbptrad_c_u_r <- join_tbls(hraisedbptrad_c, u_r, 1, hraisedbptrad_c_col_names)
# 2 - Currently taking herbal or traditional remedy for raised blood pressure among those previously diagnosed
hraisedbptrad_d_u_r <- join_tbls(hraisedbptrad_d, u_r, 1, hraisedbptrad_d_col_names)
```

<br>

```{r}
# 1
cbind(hraisedbptrad_c_m_w_b$m, select(hraisedbptrad_c_m_w_b$w, -agerange), select(hraisedbptrad_c_m_w_b$b, -agerange)) %>% final_tbl(.disaggregation = m_w_b, .s_amount = 3, .title = "Seen a traditional healer among those previously diagnosed", .colspan_val = 10)
```

<br>

```{r}
# 2
cbind(hraisedbptrad_d_m_w_b$m, select(hraisedbptrad_d_m_w_b$w, -agerange), select(hraisedbptrad_d_m_w_b$b, -agerange)) %>% final_tbl(.disaggregation = m_w_b, .s_amount = 3, .title = "Currently taking herbal or traditional remedy for raised blood pressure among those previously diagnosed", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 1
tbl_m_u_r <- rbind(hraisedbptrad_c_u_r$m_u, hraisedbptrad_c_u_r$m_r)
tbl_w_u_r <- rbind(hraisedbptrad_c_u_r$w_u, hraisedbptrad_c_u_r$w_r)
tbl_b_u_r <- rbind(hraisedbptrad_c_u_r$b_u, hraisedbptrad_c_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_tbl(.disaggregation = u_r, .s_amount = 3, .title = "Seen a traditional healer among those previously diagnosed by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 2
tbl_m_u_r <- rbind(hraisedbptrad_d_u_r$m_u, hraisedbptrad_d_u_r$m_r)
tbl_w_u_r <- rbind(hraisedbptrad_d_u_r$w_u, hraisedbptrad_d_u_r$w_r)
tbl_b_u_r <- rbind(hraisedbptrad_d_u_r$b_u, hraisedbptrad_d_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_tbl(.disaggregation = u_r, .s_amount = 3, .title = "Currently taking herbal or traditional remedy for raised blood pressure among those previously diagnosed by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 1
hraisedbptrad_c$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = hraisedbptrad_c_reg_col_names) %>% final_tbl(reg, 1, "Both sexes", "Seen a traditional healer among those previously diagnosed by region", 4)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 2
hraisedbptrad_d$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = hraisedbptrad_d_reg_col_names) %>% final_tbl(reg, 1, "Both sexes", "Currently taking herbal or traditional remedy for raised blood pressure among those previously diagnosed by region", 4)
```

<br>

**Analysis information**:

-   Questions used: H1, H2a, H4, H5
-   R script name: Hraisedbptrad

***

<br> 

<br>
