---
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  word_document: default
---

```{r setup, include=FALSE}
library(here)
library(huxtable)
library(tidyverse)
library(fs)
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
# Set a root directory for all chunks to be evaluated relative to rather than the document location
knitr::opts_knit$set(root.dir = here())
```

```{r source, include=FALSE}
here("DataBook", "Modules", "LifestyleAdvice") %>% 
  # list all R files in the directory
  fs::dir_ls(regexp = "\\.R$") %>% 
  # scale up to all R files with a map function from purrr
  map(source, encoding = "UTF-8", local = knitr::knit_global())
```

---
title: "`r set_title`"
author: "`r set_author`"
---


# Lifestyle Advice

**Lifestyle advice**

Description: Percentage of respondents who received lifestyle advice from a doctor or health worker during the past three years among all respondents.

Instrument questions:

- During the past three years, has a doctor or other health worker advised you to do any of the following?

```{r hlifestyle_tbls}
# column names to use with huxtable
hlifestyle_col_names <- c("Age Group (years)", "n", "% Advised", "95% CI")
hlifestyle_reg_col_names <- c("Region", "n", "% Advised", "95% CI")

# men, women, both sexes
# 1 (a) - Advised by doctor or health worker to quit using tobacco or don’t start
hlifestyle_a_m_w_b <- join_tbls(hlifestyle_a, m_w_b, 1, hlifestyle_col_names)

# 2 (b) - Advised by doctor or health worker to reduce salt in the diet
hlifestyle_b_m_w_b <- join_tbls(hlifestyle_b, m_w_b, 1, hlifestyle_col_names)

# 3 (c) - Advised by doctor or health worker to eat at least five servings of fruit and/or vegetables each day
hlifestyle_c_m_w_b <- join_tbls(hlifestyle_c, m_w_b, 1, hlifestyle_col_names)

# 4 (d) - Advised by doctor or health worker to reduce fat in the diet
hlifestyle_d_m_w_b <- join_tbls(hlifestyle_d, m_w_b, 1, hlifestyle_col_names)

# 5 (e) - Advised by doctor or health worker to start or do more physical activity
hlifestyle_e_m_w_b <- join_tbls(hlifestyle_e, m_w_b, 1, hlifestyle_col_names)

# 6 (f) - Advised by doctor or health worker to maintain a healthy body weight or to lose weight
hlifestyle_f_m_w_b <- join_tbls(hlifestyle_f, m_w_b, 1, hlifestyle_col_names)

# 7 (g) - Advised by doctor or health worker to reduce sugary beverages in diet
hlifestyle_g_m_w_b <- join_tbls(hlifestyle_g, m_w_b, 1, hlifestyle_col_names)
```
```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# urban, rural
# 1 - Advised by doctor or health worker to quit using tobacco or don’t start
hlifestyle_a_u_r <- join_tbls(hlifestyle_a, u_r, 1, hlifestyle_col_names)
# 2 - Advised by doctor or health worker to reduce salt in the diet
hlifestyle_b_u_r <- join_tbls(hlifestyle_b, u_r, 1, hlifestyle_col_names)
# 3 - Advised by doctor or health worker to eat at least five servings of fruit and/or vegetables each day
hlifestyle_c_u_r <- join_tbls(hlifestyle_c, u_r, 1, hlifestyle_col_names)
# 4 - Advised by doctor or health worker to reduce fat in the diet
hlifestyle_d_u_r <- join_tbls(hlifestyle_d, u_r, 1, hlifestyle_col_names)
# 5 - Advised by doctor or health worker to start or do more physical activity
hlifestyle_e_u_r <- join_tbls(hlifestyle_e, u_r, 1, hlifestyle_col_names)
# 6 - Advised by doctor or health worker to maintain a healthy body weight or to lose weight
hlifestyle_f_u_r <- join_tbls(hlifestyle_f, u_r, 1, hlifestyle_col_names)
# 7 - Advised by doctor or health worker to reduce sugary beverages in diet
hlifestyle_g_u_r <- join_tbls(hlifestyle_g, u_r, 1, hlifestyle_col_names)
```

<br>

```{r}
# 1
cbind(hlifestyle_a_m_w_b$m, select(hlifestyle_a_m_w_b$w, -agerange), select(hlifestyle_a_m_w_b$b, -agerange)) %>% final_tbl(.disaggregation = m_w_b, .s_amount = 3, .title = "Advised by doctor or health worker to quit using tobacco or don’t start", .colspan_val = 10)
```

<br>

```{r}
# 2
cbind(hlifestyle_b_m_w_b$m, select(hlifestyle_b_m_w_b$w, -agerange), select(hlifestyle_b_m_w_b$b, -agerange)) %>% final_tbl(.disaggregation = m_w_b, .s_amount = 3, .title = "Advised by doctor or health worker to reduce salt in the diet", .colspan_val = 10)
```

<br>

```{r}
# 3
cbind(hlifestyle_c_m_w_b$m, select(hlifestyle_c_m_w_b$w, -agerange), select(hlifestyle_c_m_w_b$b, -agerange)) %>% final_tbl(.disaggregation = m_w_b, .s_amount = 3, .title = "Advised by doctor or health worker to eat at least five servings of fruit and/or vegetables each day", .colspan_val = 10)
```

<br>

```{r}
# 4
cbind(hlifestyle_d_m_w_b$m, select(hlifestyle_d_m_w_b$w, -agerange), select(hlifestyle_d_m_w_b$b, -agerange)) %>% final_tbl(.disaggregation = m_w_b, .s_amount = 3, .title = "Advised by doctor or health worker to reduce fat in the diet", .colspan_val = 10)
```

<br>

```{r}
# 5
cbind(hlifestyle_e_m_w_b$m, select(hlifestyle_e_m_w_b$w, -agerange), select(hlifestyle_e_m_w_b$b, -agerange)) %>% final_tbl(.disaggregation = m_w_b, .s_amount = 3, .title = "Advised by doctor or health worker to start or do more physical activity", .colspan_val = 10)
```

<br>

```{r}
# 6
cbind(hlifestyle_f_m_w_b$m, select(hlifestyle_f_m_w_b$w, -agerange), select(hlifestyle_f_m_w_b$b, -agerange)) %>% final_tbl(.disaggregation = m_w_b, .s_amount = 3, .title = "Advised by doctor or health worker to maintain a healthy body weight or to lose weight", .colspan_val = 10)
```

<br>

```{r}
# 7
cbind(hlifestyle_g_m_w_b$m, select(hlifestyle_g_m_w_b$w, -agerange), select(hlifestyle_g_m_w_b$b, -agerange)) %>% final_tbl(.disaggregation = m_w_b, .s_amount = 3, .title = "Advised by doctor or health worker to reduce sugary beverages in diet", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 1
tbl_m_u_r <- rbind(hlifestyle_a_u_r$m_u, hlifestyle_a_u_r$m_r)
tbl_w_u_r <- rbind(hlifestyle_a_u_r$w_u, hlifestyle_a_u_r$w_r)
tbl_b_u_r <- rbind(hlifestyle_a_u_r$b_u, hlifestyle_a_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_tbl(.disaggregation = u_r, .s_amount = 3, .title = "Advised by doctor or health worker to quit using tobacco or don’t start by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 2
tbl_m_u_r <- rbind(hlifestyle_b_u_r$m_u, hlifestyle_b_u_r$m_r)
tbl_w_u_r <- rbind(hlifestyle_b_u_r$w_u, hlifestyle_b_u_r$w_r)
tbl_b_u_r <- rbind(hlifestyle_b_u_r$b_u, hlifestyle_b_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_tbl(.disaggregation = u_r, .s_amount = 3, .title = "Advised by doctor or health worker to reduce salt in the diet by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 3
tbl_m_u_r <- rbind(hlifestyle_c_u_r$m_u, hlifestyle_c_u_r$m_r)
tbl_w_u_r <- rbind(hlifestyle_c_u_r$w_u, hlifestyle_c_u_r$w_r)
tbl_b_u_r <- rbind(hlifestyle_c_u_r$b_u, hlifestyle_c_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_tbl(.disaggregation = u_r, .s_amount = 3, .title = "Advised by doctor or health worker to eat at least five servings of fruit and/or vegetables each day by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 4
tbl_m_u_r <- rbind(hlifestyle_d_u_r$m_u, hlifestyle_d_u_r$m_r)
tbl_w_u_r <- rbind(hlifestyle_d_u_r$w_u, hlifestyle_d_u_r$w_r)
tbl_b_u_r <- rbind(hlifestyle_d_u_r$b_u, hlifestyle_d_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_tbl(.disaggregation = u_r, .s_amount = 3, .title = "Advised by doctor or health worker to reduce fat in the diet by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 5
tbl_m_u_r <- rbind(hlifestyle_e_u_r$m_u, hlifestyle_e_u_r$m_r)
tbl_w_u_r <- rbind(hlifestyle_e_u_r$w_u, hlifestyle_e_u_r$w_r)
tbl_b_u_r <- rbind(hlifestyle_e_u_r$b_u, hlifestyle_e_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_tbl(.disaggregation = u_r, .s_amount = 3, .title = "Advised by doctor or health worker to start or do more physical activity by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 6
tbl_m_u_r <- rbind(hlifestyle_f_u_r$m_u, hlifestyle_f_u_r$m_r)
tbl_w_u_r <- rbind(hlifestyle_f_u_r$w_u, hlifestyle_f_u_r$w_r)
tbl_b_u_r <- rbind(hlifestyle_f_u_r$b_u, hlifestyle_f_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_tbl(.disaggregation = u_r, .s_amount = 3, .title = "Advised by doctor or health worker to maintain a healthy body weight or to lose weight by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 7
tbl_m_u_r <- rbind(hlifestyle_g_u_r$m_u, hlifestyle_g_u_r$m_r)
tbl_w_u_r <- rbind(hlifestyle_g_u_r$w_u, hlifestyle_g_u_r$w_r)
tbl_b_u_r <- rbind(hlifestyle_g_u_r$b_u, hlifestyle_g_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_tbl(.disaggregation = u_r, .s_amount = 3, .title = "Advised by doctor or health worker to reduce sugary beverages in diet by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 1
hlifestyle_a$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = hlifestyle_reg_col_names) %>% final_tbl(reg, 1, "Both sexes", "Advised by doctor or health worker to quit using tobacco or don’t start by region", 4)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 2
hlifestyle_b$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = hlifestyle_reg_col_names) %>% final_tbl(reg, 1, "Both sexes", "Advised by doctor or health worker to reduce salt in the diet by region", 4)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 3
hlifestyle_c$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = hlifestyle_reg_col_names) %>% final_tbl(reg, 1, "Both sexes", "Advised by doctor or health worker to eat at least five servings of fruit and/or vegetables each day by region", 4)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 4
hlifestyle_d$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = hlifestyle_reg_col_names) %>% final_tbl(reg, 1, "Both sexes", "Advised by doctor or health worker to reduce fat in the diet by region", 4)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 5
hlifestyle_e$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = hlifestyle_reg_col_names) %>% final_tbl(reg, 1, "Both sexes", "Advised by doctor or health worker to start or do more physical activity by region", 4)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 6
hlifestyle_f$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = hlifestyle_reg_col_names) %>% final_tbl(reg, 1, "Both sexes", "Advised by doctor or health worker to maintain a healthy body weight or to lose weight by region", 4)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 7
hlifestyle_g$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = hlifestyle_reg_col_names) %>% final_tbl(reg, 1, "Both sexes", "Advised by doctor or health worker to reduce sugary beverages in diet by region", 4)
```

<br>

**Analysis information**:

-   Questions used: H20a-g
-   R script name: Hlifestyle

***



<br> 

<br>
