---
title: "STEPS MDA Data Book"
author: "WHO NCD Office Moscow"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  word_document: default
  html_document:
    css: style.css
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
library(here)
library(huxtable)
library(tidyverse)
library(fs)
```

```{r source, include=FALSE}
lifestyle_data_dir <- here::here("DataBook", "Modules", "LifestyleAdvice")

# list all files in the directory
# fs::dir_ls(lifestyle_data_dir)

# only R files
r_files <- fs::dir_ls(lifestyle_data_dir, regexp = "\\.R$") 
# r_files

# read in just one R file for testing
# source(r_files[1])

# scale up to all R files with a map function from purrr
r_files %>% 
  map(source, encoding = "UTF-8", local = knitr::knit_global())
```

```{r databook_functions, echo=FALSE}
source(here("DataBook", "databook_functions.R"), encoding = "UTF-8", local = knitr::knit_global())
```

```{r}
m_w_b <- c("m","w","b")
u_r <- c("m_u","w_u","b_u","m_r","w_r","b_r")
```

# Lifestyle Advice

**Lifestyle advice**

Description: Percentage of respondents who received lifestyle advice from a doctor or health worker during the past three years among all respondents.

Instrument questions:

- During the past three years, has a doctor or other health worker advised you to do any of the following?

```{r hlifestyle_tbls}
# column names to use with huxtable
hlifestyle_col_names <- c("Age Group (years)", "n", "% Advised", "95% CI")
hlifestyle_reg_col_names <- c("Region", "n", "% Advised", "95% CI")

# men, women, both sexes
# 1 (a) - Advised by doctor or health worker to quit using tobacco or don’t start
hlifestyle_a_m_w_b <- join_m_w_b(hlifestyle_a, 1, hlifestyle_col_names)

# 2 (b) - Advised by doctor or health worker to reduce salt in the diet
hlifestyle_b_m_w_b <- join_m_w_b(hlifestyle_b, 1, hlifestyle_col_names)

# 3 (c) - Advised by doctor or health worker to eat at least five servings of fruit and/or vegetables each day
hlifestyle_c_m_w_b <- join_m_w_b(hlifestyle_c, 1, hlifestyle_col_names)

# 4 (d) - Advised by doctor or health worker to reduce fat in the diet
hlifestyle_d_m_w_b <- join_m_w_b(hlifestyle_d, 1, hlifestyle_col_names)

# 5 (e) - Advised by doctor or health worker to start or do more physical activity
hlifestyle_e_m_w_b <- join_m_w_b(hlifestyle_e, 1, hlifestyle_col_names)

# 6 (f) - Advised by doctor or health worker to maintain a healthy body weight or to lose weight
hlifestyle_f_m_w_b <- join_m_w_b(hlifestyle_f, 1, hlifestyle_col_names)

# 7 (g) - Advised by doctor or health worker to reduce sugary beverages in diet
hlifestyle_g_m_w_b <- join_m_w_b(hlifestyle_g, 1, hlifestyle_col_names)
```
```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# urban, rural
# 1 - Advised by doctor or health worker to quit using tobacco or don’t start
hlifestyle_a_u_r <- join_u_r(hlifestyle_a, 1, hlifestyle_col_names)
# 2 - Advised by doctor or health worker to reduce salt in the diet
hlifestyle_b_u_r <- join_u_r(hlifestyle_b, 1, hlifestyle_col_names)
# 3 - Advised by doctor or health worker to eat at least five servings of fruit and/or vegetables each day
hlifestyle_c_u_r <- join_u_r(hlifestyle_c, 1, hlifestyle_col_names)
# 4 - Advised by doctor or health worker to reduce fat in the diet
hlifestyle_d_u_r <- join_u_r(hlifestyle_d, 1, hlifestyle_col_names)
# 5 - Advised by doctor or health worker to start or do more physical activity
hlifestyle_e_u_r <- join_u_r(hlifestyle_e, 1, hlifestyle_col_names)
# 6 - Advised by doctor or health worker to maintain a healthy body weight or to lose weight
hlifestyle_f_u_r <- join_u_r(hlifestyle_f, 1, hlifestyle_col_names)
# 7 - Advised by doctor or health worker to reduce sugary beverages in diet
hlifestyle_g_u_r <- join_u_r(hlifestyle_g, 1, hlifestyle_col_names)
```

<br>

```{r}
# 1
cbind(hlifestyle_a_m_w_b$m, select(hlifestyle_a_m_w_b$w, -agerange), select(hlifestyle_a_m_w_b$b, -agerange)) %>% final_m_w_b_tbl(.s_amount = 3, .title = "Advised by doctor or health worker to quit using tobacco or don’t start", .colspan_val = 10)
```

<br>

```{r}
# 2
cbind(hlifestyle_b_m_w_b$m, select(hlifestyle_b_m_w_b$w, -agerange), select(hlifestyle_b_m_w_b$b, -agerange)) %>% final_m_w_b_tbl(.s_amount = 3, .title = "Advised by doctor or health worker to reduce salt in the diet", .colspan_val = 10)
```

<br>

```{r}
# 3
cbind(hlifestyle_c_m_w_b$m, select(hlifestyle_c_m_w_b$w, -agerange), select(hlifestyle_c_m_w_b$b, -agerange)) %>% final_m_w_b_tbl(.s_amount = 3, .title = "Advised by doctor or health worker to eat at least five servings of fruit and/or vegetables each day", .colspan_val = 10)
```

<br>

```{r}
# 4
cbind(hlifestyle_d_m_w_b$m, select(hlifestyle_d_m_w_b$w, -agerange), select(hlifestyle_d_m_w_b$b, -agerange)) %>% final_m_w_b_tbl(.s_amount = 3, .title = "Advised by doctor or health worker to reduce fat in the diet", .colspan_val = 10)
```

<br>

```{r}
# 5
cbind(hlifestyle_e_m_w_b$m, select(hlifestyle_e_m_w_b$w, -agerange), select(hlifestyle_e_m_w_b$b, -agerange)) %>% final_m_w_b_tbl(.s_amount = 3, .title = "Advised by doctor or health worker to start or do more physical activity", .colspan_val = 10)
```

<br>

```{r}
# 6
cbind(hlifestyle_f_m_w_b$m, select(hlifestyle_f_m_w_b$w, -agerange), select(hlifestyle_f_m_w_b$b, -agerange)) %>% final_m_w_b_tbl(.s_amount = 3, .title = "Advised by doctor or health worker to maintain a healthy body weight or to lose weight", .colspan_val = 10)
```

<br>

```{r}
# 7
cbind(hlifestyle_g_m_w_b$m, select(hlifestyle_g_m_w_b$w, -agerange), select(hlifestyle_g_m_w_b$b, -agerange)) %>% final_m_w_b_tbl(.s_amount = 3, .title = "Advised by doctor or health worker to reduce sugary beverages in diet", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 1
tbl_m_u_r <- rbind(hlifestyle_a_u_r$m_u, hlifestyle_a_u_r$m_r)
tbl_w_u_r <- rbind(hlifestyle_a_u_r$w_u, hlifestyle_a_u_r$w_r)
tbl_b_u_r <- rbind(hlifestyle_a_u_r$b_u, hlifestyle_a_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_u_r_tbl(.s_amount = 3, .title = "Advised by doctor or health worker to quit using tobacco or don’t start by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 2
tbl_m_u_r <- rbind(hlifestyle_b_u_r$m_u, hlifestyle_b_u_r$m_r)
tbl_w_u_r <- rbind(hlifestyle_b_u_r$w_u, hlifestyle_b_u_r$w_r)
tbl_b_u_r <- rbind(hlifestyle_b_u_r$b_u, hlifestyle_b_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_u_r_tbl(.s_amount = 3, .title = "Advised by doctor or health worker to reduce salt in the diet by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 3
tbl_m_u_r <- rbind(hlifestyle_c_u_r$m_u, hlifestyle_c_u_r$m_r)
tbl_w_u_r <- rbind(hlifestyle_c_u_r$w_u, hlifestyle_c_u_r$w_r)
tbl_b_u_r <- rbind(hlifestyle_c_u_r$b_u, hlifestyle_c_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_u_r_tbl(.s_amount = 3, .title = "Advised by doctor or health worker to eat at least five servings of fruit and/or vegetables each day by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 4
tbl_m_u_r <- rbind(hlifestyle_d_u_r$m_u, hlifestyle_d_u_r$m_r)
tbl_w_u_r <- rbind(hlifestyle_d_u_r$w_u, hlifestyle_d_u_r$w_r)
tbl_b_u_r <- rbind(hlifestyle_d_u_r$b_u, hlifestyle_d_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_u_r_tbl(.s_amount = 3, .title = "Advised by doctor or health worker to reduce fat in the diet by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 5
tbl_m_u_r <- rbind(hlifestyle_e_u_r$m_u, hlifestyle_e_u_r$m_r)
tbl_w_u_r <- rbind(hlifestyle_e_u_r$w_u, hlifestyle_e_u_r$w_r)
tbl_b_u_r <- rbind(hlifestyle_e_u_r$b_u, hlifestyle_e_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_u_r_tbl(.s_amount = 3, .title = "Advised by doctor or health worker to start or do more physical activity by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 6
tbl_m_u_r <- rbind(hlifestyle_f_u_r$m_u, hlifestyle_f_u_r$m_r)
tbl_w_u_r <- rbind(hlifestyle_f_u_r$w_u, hlifestyle_f_u_r$w_r)
tbl_b_u_r <- rbind(hlifestyle_f_u_r$b_u, hlifestyle_f_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_u_r_tbl(.s_amount = 3, .title = "Advised by doctor or health worker to maintain a healthy body weight or to lose weight by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 7
tbl_m_u_r <- rbind(hlifestyle_g_u_r$m_u, hlifestyle_g_u_r$m_r)
tbl_w_u_r <- rbind(hlifestyle_g_u_r$w_u, hlifestyle_g_u_r$w_r)
tbl_b_u_r <- rbind(hlifestyle_g_u_r$b_u, hlifestyle_g_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_u_r_tbl(.s_amount = 3, .title = "Advised by doctor or health worker to reduce sugary beverages in diet by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 1
hlifestyle_a$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = hlifestyle_reg_col_names) %>% final_m_w_b_tbl(1, "Both sexes", "Advised by doctor or health worker to quit using tobacco or don’t start by region", 4)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 2
hlifestyle_b$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = hlifestyle_reg_col_names) %>% final_m_w_b_tbl(1, "Both sexes", "Advised by doctor or health worker to reduce salt in the diet by region", 4)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 3
hlifestyle_c$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = hlifestyle_reg_col_names) %>% final_m_w_b_tbl(1, "Both sexes", "Advised by doctor or health worker to eat at least five servings of fruit and/or vegetables each day by region", 4)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 4
hlifestyle_d$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = hlifestyle_reg_col_names) %>% final_m_w_b_tbl(1, "Both sexes", "Advised by doctor or health worker to reduce fat in the diet by region", 4)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 5
hlifestyle_e$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = hlifestyle_reg_col_names) %>% final_m_w_b_tbl(1, "Both sexes", "Advised by doctor or health worker to start or do more physical activity by region", 4)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 6
hlifestyle_f$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = hlifestyle_reg_col_names) %>% final_m_w_b_tbl(1, "Both sexes", "Advised by doctor or health worker to maintain a healthy body weight or to lose weight by region", 4)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 7
hlifestyle_g$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = hlifestyle_reg_col_names) %>% final_m_w_b_tbl(1, "Both sexes", "Advised by doctor or health worker to reduce sugary beverages in diet by region", 4)
```

<br>

**Analysis information**:

-   Questions used: H20a-g
-   R script name: Hlifestyle

***



<br> 

<br>
