---
title: "STEPS MDA Data Book"
author: "WHO NCD Office Moscow"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  word_document: default
  html_document:
    css: style.css
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
library(here)
library(huxtable)
library(tidyverse)
library(fs)
```

```{r source, include=FALSE}
pa_data_dir <- here::here("DataBook", "Modules", "PhysicalActivity")

# list all files in the directory
# fs::dir_ls(pa_data_dir)

# only R files
r_files <- fs::dir_ls(pa_data_dir, regexp = "\\.R$") 
# r_files

# read in just one R file for testing
# source(r_files[1])

# scale up to all R files with a map function from purrr
r_files %>% 
  map(source, encoding = "UTF-8", local = knitr::knit_global())
```

```{r databook_functions, echo=FALSE}
source(here("DataBook", "databook_functions.R"), encoding = "UTF-8", local = knitr::knit_global())
```

```{r}
m_w_b <- c("m","w","b")
u_r <- c("m_u","w_u","b_u","m_r","w_r","b_r")
```

# Physical Activity

**Introduction**

A population's physical activity (or inactivity) can be described in different ways. The two most common ways are 

1. to estimate a population's mean or median physical activity using a continuous indicator such as MET-minutes per week or time spent in physical activity, and 
2. to classify certain percentages of a population in specific groups by setting up cut-points for a specific amount of physical activity.

When analyzing GPAQ data, both continuous as well as categorical indicators are used.

***

**Metabolic Equivalent (MET)**

METs (Metabolic Equivalents) are commonly used to express the intensity of physical activities, and are also used for the analysis of GPAQ data.

Applying MET values to activity levels allows us to calculate total physical activity. MET is the ratio of a person's working metabolic rate relative to the resting metabolic rate. One MET is defined as the energy cost of sitting quietly, and is equivalent to a caloric consumption of 1 kcal/kg/hour. For the analysis of GPAQ data, existing guidelines have been adopted: It is estimated that, compared to sitting quietly, a person's caloric consumption is four times as high when being moderately active, and eight times as high when being vigorously active.

Therefore, for the calculation of a person's total physical activity using GPAQ data, the following MET values are used:

+--------------+-------------------------------------+
| **Domain**   | **MET value**                       |
+--------------+-------------------------------------+
| Work         | -   Moderate MET value = 4.0        |
|              |                                     |
|              | -   Vigorous MET value = 8.0        |
+--------------+-------------------------------------+
| Transport    | Cycling and walking MET value = 4.0 |
+--------------+-------------------------------------+
| Recreation   | -   Moderate MET value = 4.0        |
|              |                                     |
|              | -   Vigorous MET value = 8.0        |
+--------------+-------------------------------------+

***

**WHO global recommendations on physical activity for health**

For the calculation of the categorical indicator on the recommended amount of physical activity for health, the total time spent in physical activity during a typical week and the intensity of the physical activity are taken into account.

Throughout a week, including activity for work, during transport and leisure time, adults should do at least

-   150 minutes of moderate-intensity physical activity OR
-   75 minutes of vigorous-intensity physical activity OR
-   An equivalent combination of moderate- and vigorous-intensity physical activity achieving at least 600 MET-minutes.

***

**Former recommendations for comparison purposes**

For comparison purposes, tables presenting cut-offs from former recommendations are also included in GPAQ data analysis.

The three levels of physical activity suggested for classifying populations were low, moderate, and high. The criteria for these levels are shown below.

**High** 

A person reaching any of the following criteria is classified in this category:

-   Vigorous-intensity activity on at least 3 days achieving a minimum of at least 1,500 MET-minutes/week OR
-   7 or more days of any combination of walking, moderate- or vigorous-intensity activities achieving a minimum of at least 3,000 MET-minutes per week.

**Moderate** 

A person not meeting the criteria for the "high" category, but meeting any of the following criteria is classified in this category:

-   3 or more days of vigorous-intensity activity of at least 20 minutes per day OR
-   5 or more days of moderate-intensity activity or walking of at least 30 minutes per day OR
-   5 or more days of any combination of walking, moderate- or vigorous-intensity activities achieving a minimum of at least 600 MET-minutes per week.

**Low** 

A person not meeting any of the above mentioned criteria falls in this category.

***

**Not meeting WHO recommendations on physical activity for health ("Insufficient physical activity")**

Description: Percentage of respondents not meeting WHO recommendations on physical activity for health (respondents doing less than 150 minutes of moderate-intensity physical activity per week, or equivalent).

Instrument questions:

-   activity at work
-   travel to and from places
-   recreational activities

```{r pnotmeetingrecs_c_tbls}
# column names to use with huxtable
pnotmeetingrecs_c_col_names <- c("Age Group (years)", "n", "% not meeting recs", "95% CI")
pnotmeetingrecs_c_reg_col_names <- c("Region", "n", "% not meeting recs", "95% CI")

# men, women, both sexes
pnotmeetingrecs_c_m_w_b <- join_m_w_b(pnotmeetingrecs_c, 1, pnotmeetingrecs_c_col_names)
```
```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# urban, rural
pnotmeetingrecs_c_u_r <- join_u_r(pnotmeetingrecs_c, 1, pnotmeetingrecs_c_col_names)
```

<br>

```{r}
cbind(pnotmeetingrecs_c_m_w_b$m, select(pnotmeetingrecs_c_m_w_b$w, -agerange), select(pnotmeetingrecs_c_m_w_b$b, -agerange)) %>% 
  final_m_w_b_tbl(.s_amount = 3, .title = "Not meeting WHO recommendations on physical activity for health", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
tbl_m_u_r <- rbind(pnotmeetingrecs_c_u_r$m_u, pnotmeetingrecs_c_u_r$m_r)
tbl_w_u_r <- rbind(pnotmeetingrecs_c_u_r$w_u, pnotmeetingrecs_c_u_r$w_r)
tbl_b_u_r <- rbind(pnotmeetingrecs_c_u_r$b_u, pnotmeetingrecs_c_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_u_r_tbl(.s_amount = 3, .title = "Not meeting WHO recommendations on physical activity for health by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
pnotmeetingrecs_c$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = pnotmeetingrecs_c_reg_col_names) %>% 
  final_m_w_b_tbl(1, "Both sexes", "Not meeting WHO recommendations on physical activity for health by region", 4) 
```

<br>

**Analysis information**:

-   Questions used: P1-P15b
-   R script name: Pnotmeetingrecs

***

**Not meeting WHO recommendations on physical activity for health ("Insufficient physical activity")**

Description: Respondents meeting WHO recommendations on physical activity for **additional** health benefits (physical activity ≥ 1200 MET-minutes/week).

Instrument questions:

-   activity at work
-   travel to and from places
-   recreational activities

```{r pnotmeetingrecs_mets1200_tbls}
# column names to use with huxtable
pnotmeetingrecs_mets1200_col_names <- c("Age Group (years)", "n", "% not meeting recs", "95% CI")
pnotmeetingrecs_mets1200_reg_col_names <- c("Region", "n", "% not meeting recs", "95% CI")

# men, women, both sexes
pnotmeetingrecs_mets1200_m_w_b <- join_m_w_b(pnotmeetingrecs_mets1200, 1, pnotmeetingrecs_mets1200_col_names)
```
```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# urban, rural
pnotmeetingrecs_mets1200_u_r <- join_u_r(pnotmeetingrecs_mets1200, 1, pnotmeetingrecs_mets1200_col_names)
```

<br>

```{r}
cbind(pnotmeetingrecs_mets1200_m_w_b$m, select(pnotmeetingrecs_mets1200_m_w_b$w, -agerange), select(pnotmeetingrecs_mets1200_m_w_b$b, -agerange)) %>% 
  final_m_w_b_tbl(.s_amount = 3, .title = "Meeting WHO recommendations on physical activity for additional health benefits", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
tbl_m_u_r <- rbind(pnotmeetingrecs_mets1200_u_r$m_u, pnotmeetingrecs_mets1200_u_r$m_r)
tbl_w_u_r <- rbind(pnotmeetingrecs_mets1200_u_r$w_u, pnotmeetingrecs_mets1200_u_r$w_r)
tbl_b_u_r <- rbind(pnotmeetingrecs_mets1200_u_r$b_u, pnotmeetingrecs_mets1200_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_u_r_tbl(.s_amount = 3, .title = "Meeting WHO recommendations on physical activity for additional health benefits by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
pnotmeetingrecs_mets1200$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = pnotmeetingrecs_mets1200_reg_col_names) %>% 
  final_m_w_b_tbl(1, "Both sexes", "Meeting WHO recommendations on physical activity for additional health benefits by region", 4) 
```

<br>

**Analysis information**:

-   Questions used: P1-P15b
-   R script name: Pnotmeetingrecs

***

**Levels of total physical activity according to former recommendations**

Description: Percentage of respondents classified into three categories of total physical activity according to former recommendations.

Instrument questions:

- activity at work
- travel to and from places
- recreational activities

```{r ptotallevels_c_tbls}

# column names to use with huxtable
ptotallevels_c_col_names <- c("Age Group (years)", "n", "% Low", "95% CI", "% Moderate", "95% CI", "% High", "95% CI")
ptotallevels_c_reg_col_names <- c("Region", "n", "% Low", "95% CI", "% Moderate", "95% CI", "% High", "95% CI")

# men, women, both sexes
ptotallevels_c_m_w_b <- join_m_w_b(ptotallevels_c, 3, ptotallevels_c_col_names)
```
```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# urban, rural
ptotallevels_c_u_r <- join_u_r(ptotallevels_c, 3, ptotallevels_c_col_names)
```

<br>

```{r}
ptotallevels_c_m_w_b$m %>% final_m_w_b_tbl(1, "Men", "Level of total physical activity according to former recommendations", 8) 
```

<br>

```{r}
ptotallevels_c_m_w_b$w %>% final_m_w_b_tbl(1, "Women", "Level of total physical activity according to former recommendations", 8)
```

<br>

```{r}
ptotallevels_c_m_w_b$b %>% final_m_w_b_tbl(1, "Both sexes", "Level of total physical activity according to former recommendations", 8)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
rbind(ptotallevels_c_u_r$m_u, ptotallevels_c_u_r$m_r) %>% 
  final_u_r_tbl(1, "Men", "Level of total physical activity according to former recommendations by type of settlement", 8) 
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
rbind(ptotallevels_c_u_r$w_u, ptotallevels_c_u_r$w_r) %>% 
  final_u_r_tbl(1, "Women", "Level of total physical activity according to former recommendations by type of settlement", 8)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
rbind(ptotallevels_c_u_r$b_u, ptotallevels_c_u_r$b_r) %>% 
  final_u_r_tbl(1, "Both sexes", "Level of total physical activity according to former recommendations by type of settlement", 8)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# region
ptotallevels_c$b_reg %>% unite_ci(.ci_amount = 3) %>% apply_hux(.col_names = ptotallevels_c_reg_col_names) %>% 
  final_m_w_b_tbl(1, "Both sexes", "Level of total physical activity according to former recommendations by region", 8)
```

<br>

**Analysis information**:

-   Questions used: P1-P15b
-   R script name: Ptotallevels

***

**Total physical activity - mean**

Description: Mean minutes of total physical activity on average per day.

Instrument questions:

- activity at work
- travel to and from places
- recreational activities

```{r ptotal_mn_tbls}
# column names to use with huxtable
ptotal_mn_col_names <- c("Age Group (years)", "n", "Mean minutes", "95% CI")
ptotal_mn_reg_col_names <- c("Region", "n", "Mean minutes", "95% CI")

# men, women, both sexes
ptotal_mn_m_w_b <- join_m_w_b(ptotal_mn, 1, ptotal_mn_col_names)
```
```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# urban, rural
ptotal_mn_u_r <- join_u_r(ptotal_mn, 1, ptotal_mn_col_names)
```

<br>

```{r}
cbind(ptotal_mn_m_w_b$m, select(ptotal_mn_m_w_b$w, -agerange), select(ptotal_mn_m_w_b$b, -agerange)) %>% 
  final_m_w_b_tbl(.s_amount = 3, .title = "Mean minutes of total physical activity on average per day", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
tbl_m_u_r <- rbind(ptotal_mn_u_r$m_u, ptotal_mn_u_r$m_r)
tbl_w_u_r <- rbind(ptotal_mn_u_r$w_u, ptotal_mn_u_r$w_r)
tbl_b_u_r <- rbind(ptotal_mn_u_r$b_u, ptotal_mn_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_u_r_tbl(.s_amount = 3, .title = "Mean minutes of total physical activity on average per day by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
ptotal_mn$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = ptotal_mn_reg_col_names) %>% 
  final_m_w_b_tbl(1, "Both sexes", "Mean minutes of total physical activity on average per day by region", 4) 
```

<br>

**Analysis information**:

-   Questions used: P1-P15b
-   R script name: Ptotal

***

**Total physical activity - median**

Description: Median minutes of total physical activity on average per day.

Instrument questions:

- activity at work
- travel to and from places
- recreational activities

```{r ptotal_md_tbls}
# column names to use with huxtable
ptotal_md_col_names <- c("Age Group (years)", "n", "Median minutes", "Inter-quartile range (P25-P75)")
ptotal_md_reg_col_names <- c("Region", "n", "Median minutes", "Inter-quartile range (P25-P75)")

# men, women, both sexes
ptotal_md_m_w_b <- join_m_w_b(ptotal_md, "q", ptotal_md_col_names)
```
```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# urban, rural
ptotal_md_u_r <- join_u_r(ptotal_md, "q", ptotal_md_col_names)
```

<br>

```{r}
cbind(ptotal_md_m_w_b$m, select(ptotal_md_m_w_b$w, -agerange), select(ptotal_md_m_w_b$b, -agerange)) %>% 
  final_m_w_b_tbl(.s_amount = 3, .title = "Median minutes of total physical activity on average per day", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
tbl_m_u_r <- rbind(ptotal_md_u_r$m_u, ptotal_md_u_r$m_r)
tbl_w_u_r <- rbind(ptotal_md_u_r$w_u, ptotal_md_u_r$w_r)
tbl_b_u_r <- rbind(ptotal_md_u_r$b_u, ptotal_md_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_u_r_tbl(.s_amount = 3, .title = "Median minutes of total physical activity on average per day by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
ptotal_md$b_reg %>% unite_ci(.ci_amount = "q") %>% apply_hux(.col_names = ptotal_md_reg_col_names) %>% 
  final_m_w_b_tbl(1, "Both sexes", "Median minutes of total physical activity on average per day by region", 4) 
```

<br>

**Analysis information**:

-   Questions used: P1-P15b
-   R script name: Ptotalmedian

***

**Domain-specific physical activity - mean**

Description: Mean minutes spent in work-, transport- and recreation-related physical activity on average per day.

Instrument questions:

- activity at work
- travel to and from places
- recreational activities

```{r psetspecific_mn_tbls}
# column names to use with huxtable
psetspecific_mn_col_names <- c("Age Group (years)", "n", "Mean minutes", "95% CI")
psetspecific_mn_reg_col_names <- c("Region", "n", "Mean minutes", "95% CI")

# men, women, both sexes
# 1 - Mean minutes of work-related physical activity on average per day
pworkday_mn_m_w_b <- join_m_w_b(psetspecific_pworkday_mn, 1, psetspecific_mn_col_names)
# 2 - Mean minutes of transport-related physical activity on average per day
ptravelday_mn_m_w_b <- join_m_w_b(psetspecific_ptravelday_mn, 1, psetspecific_mn_col_names)
# 3 - Mean minutes of recreation-related physical activity on average per day
precday_mn_m_w_b <- join_m_w_b(psetspecific_precday_mn, 1, psetspecific_mn_col_names)
```
```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# urban, rural
# 1 - Mean minutes of work-related physical activity on average per day
pworkday_mn_u_r <- join_u_r(psetspecific_pworkday_mn, 1, psetspecific_mn_col_names)
# 2 - Mean minutes of transport-related physical activity on average per day
ptravelday_mn_u_r <- join_u_r(psetspecific_ptravelday_mn, 1, psetspecific_mn_col_names)
# 3 - Mean minutes of recreation-related physical activity on average per day
precday_mn_u_r <- join_u_r(psetspecific_precday_mn, 1, psetspecific_mn_col_names)
```

<br>

```{r}
# 1
cbind(pworkday_mn_m_w_b$m, select(pworkday_mn_m_w_b$w, -agerange), select(pworkday_mn_m_w_b$b, -agerange)) %>% 
  final_m_w_b_tbl(.s_amount = 3, .title = "Mean minutes of work-related physical activity on average per day", .colspan_val = 10)
```

<br>

```{r}
# 2
cbind(ptravelday_mn_m_w_b$m, select(ptravelday_mn_m_w_b$w, -agerange), select(ptravelday_mn_m_w_b$b, -agerange)) %>% 
  final_m_w_b_tbl(.s_amount = 3, .title = "Mean minutes of transport-related physical activity on average per day", .colspan_val = 10)
```

<br>

```{r}
# 3
cbind(precday_mn_m_w_b$m, select(precday_mn_m_w_b$w, -agerange), select(precday_mn_m_w_b$b, -agerange)) %>% 
  final_m_w_b_tbl(.s_amount = 3, .title = "Mean minutes of recreation-related physical activity on average per day", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 1
tbl_m_u_r <- rbind(pworkday_mn_u_r$m_u, pworkday_mn_u_r$m_r)
tbl_w_u_r <- rbind(pworkday_mn_u_r$w_u, pworkday_mn_u_r$w_r)
tbl_b_u_r <- rbind(pworkday_mn_u_r$b_u, pworkday_mn_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_u_r_tbl(.s_amount = 3, .title = "Mean minutes of work-related physical activity on average per day by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 2
tbl_m_u_r <- rbind(ptravelday_mn_u_r$m_u, ptravelday_mn_u_r$m_r)
tbl_w_u_r <- rbind(ptravelday_mn_u_r$w_u, ptravelday_mn_u_r$w_r)
tbl_b_u_r <- rbind(ptravelday_mn_u_r$b_u, ptravelday_mn_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_u_r_tbl(.s_amount = 3, .title = "Mean minutes of transport-related physical activity on average per day by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 3
tbl_m_u_r <- rbind(precday_mn_u_r$m_u, precday_mn_u_r$m_r)
tbl_w_u_r <- rbind(precday_mn_u_r$w_u, precday_mn_u_r$w_r)
tbl_b_u_r <- rbind(precday_mn_u_r$b_u, precday_mn_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_u_r_tbl(.s_amount = 3, .title = "Mean minutes of recreation-related physical activity on average per day by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 1
psetspecific_pworkday_mn$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = psetspecific_mn_reg_col_names) %>% 
  final_m_w_b_tbl(1, "Both sexes", "Mean minutes of work-related physical activity on average per day by region", 4) 
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 2
psetspecific_ptravelday_mn$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = psetspecific_mn_reg_col_names) %>% 
  final_m_w_b_tbl(1, "Both sexes", "Mean minutes of transport-related physical activity on average per day by region", 4) 
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 3
psetspecific_precday_mn$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = psetspecific_mn_reg_col_names) %>% 
  final_m_w_b_tbl(1, "Both sexes", "Mean minutes of recreation-related physical activity on average per day by region", 4) 
```

<br>

**Analysis information**:

-   Questions used: P1-P15b
-   R script name: Psetspecific

***

**Domain-specific physical activity - median**

Description: Median minutes spent on average per day in work-, transport- and recreation-related physical activity.

Instrument questions:

- activity at work
- travel to and from places
- recreational activities

```{r psetspecific_md_tbls}
# column names to use with huxtable
psetspecific_md_col_names <- c("Age Group (years)", "n", "Median minutes", "95% CI")
psetspecific_md_reg_col_names <- c("Region", "n", "Median minutes", "95% CI")

# men, women, both sexes
# 1 - Median minutes of work-related physical activity on average per day
pworkday_md_m_w_b <- join_m_w_b(psetspecific_pworkday_md, "q", psetspecific_md_col_names)
# 2 - Median minutes of transport-related physical activity on average per day
ptravelday_md_m_w_b <- join_m_w_b(psetspecific_ptravelday_md, "q", psetspecific_md_col_names)
# 3 - Median minutes of recreation-related physical activity on average per day
precday_md_m_w_b <- join_m_w_b(psetspecific_precday_md, "q", psetspecific_md_col_names)
```
```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# urban, rural
# 1 - Median minutes of work-related physical activity on average per day
pworkday_md_u_r <- join_u_r(psetspecific_pworkday_md, "q", psetspecific_md_col_names)
# 2 - Median minutes of transport-related physical activity on average per day
ptravelday_md_u_r <- join_u_r(psetspecific_ptravelday_md, "q", psetspecific_md_col_names)
# 3 - Median minutes of recreation-related physical activity on average per day
precday_md_u_r <- join_u_r(psetspecific_precday_md, "q", psetspecific_md_col_names)
```

<br>

```{r}
# 1
cbind(pworkday_md_m_w_b$m, select(pworkday_md_m_w_b$w, -agerange), select(pworkday_md_m_w_b$b, -agerange)) %>% 
  final_m_w_b_tbl(.s_amount = 3, .title = "Median minutes of work-related physical activity on average per day", .colspan_val = 10)
```

<br>

```{r}
# 2
cbind(ptravelday_md_m_w_b$m, select(ptravelday_md_m_w_b$w, -agerange), select(ptravelday_md_m_w_b$b, -agerange)) %>% 
  final_m_w_b_tbl(.s_amount = 3, .title = "Median minutes of transport-related physical activity on average per day", .colspan_val = 10)
```

<br>

```{r}
# 3
cbind(precday_md_m_w_b$m, select(precday_md_m_w_b$w, -agerange), select(precday_md_m_w_b$b, -agerange)) %>% 
  final_m_w_b_tbl(.s_amount = 3, .title = "Median minutes of recreation-related physical activity on average per day", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 1
tbl_m_u_r <- rbind(pworkday_md_u_r$m_u, pworkday_md_u_r$m_r)
tbl_w_u_r <- rbind(pworkday_md_u_r$w_u, pworkday_md_u_r$w_r)
tbl_b_u_r <- rbind(pworkday_md_u_r$b_u, pworkday_md_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_u_r_tbl(.s_amount = 3, .title = "Median minutes of work-related physical activity on average per day by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 2
tbl_m_u_r <- rbind(ptravelday_md_u_r$m_u, ptravelday_md_u_r$m_r)
tbl_w_u_r <- rbind(ptravelday_md_u_r$w_u, ptravelday_md_u_r$w_r)
tbl_b_u_r <- rbind(ptravelday_md_u_r$b_u, ptravelday_md_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_u_r_tbl(.s_amount = 3, .title = "Median minutes of transport-related physical activity on average per day by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 3
tbl_m_u_r <- rbind(precday_md_u_r$m_u, precday_md_u_r$m_r)
tbl_w_u_r <- rbind(precday_md_u_r$w_u, precday_md_u_r$w_r)
tbl_b_u_r <- rbind(precday_md_u_r$b_u, precday_md_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_u_r_tbl(.s_amount = 3, .title = "Median minutes of recreation-related physical activity on average per day by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 1
psetspecific_pworkday_md$b_reg %>% unite_ci(.ci_amount = "q") %>% apply_hux(.col_names = psetspecific_md_reg_col_names) %>% 
  final_m_w_b_tbl(1, "Both sexes", "Median minutes of work-related physical activity on average per day by region", 4) 
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 2
psetspecific_ptravelday_md$b_reg %>% unite_ci(.ci_amount = "q") %>% apply_hux(.col_names = psetspecific_md_reg_col_names) %>% 
  final_m_w_b_tbl(1, "Both sexes", "Median minutes of transport-related physical activity on average per day by region", 4) 
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 3
psetspecific_precday_md$b_reg %>% unite_ci(.ci_amount = "q") %>% apply_hux(.col_names = psetspecific_md_reg_col_names) %>% 
  final_m_w_b_tbl(1, "Both sexes", "Median minutes of recreation-related physical activity on average per day by region", 4) 
```

<br>

**Analysis information**:

-   Questions used: P1-P15b
-   R script name: Psetspecific

***

**No physical activity by domain**

Description: Percentage of respondents classified as doing no work-, transport- or recreational-related physical activity.

Instrument questions:

- activity at work
- travel to and from places
- recreational activities

```{r pnoactivitybyset_tbls}
# column names to use with huxtable
# 1 - No work-related physical activity
pnoactivitybyset_work_col_names <- c("Age Group (years)", "n", "% no activity at work", "95% CI")
pnoactivitybyset_work_reg_col_names <- c("Region", "n", "% no activity at work", "95% CI")
# 2 - No transport-related physical activity
pnoactivitybyset_trans_col_names <- c("Age Group (years)", "n", "% no activity for transport", "95% CI")
pnoactivitybyset_trans_reg_col_names <- c("Region", "n", "% no activity for transport", "95% CI")
# 3 - No recreation-related physical activity
pnoactivitybyset_rec_col_names <- c("Age Group (years)", "n", "% no activity at recreation", "95% CI")
pnoactivitybyset_rec_reg_col_names <- c("Region", "n", "% no activity at recreation", "95% CI")

# men, women, both sexes
# 1 - No work-related physical activity
pnoactivitybyset_work_m_w_b <- join_m_w_b(pnoactivitybyset_work, 1, pnoactivitybyset_work_col_names)
# 2 - No transport-related physical activity
pnoactivitybyset_trans_m_w_b <- join_m_w_b(pnoactivitybyset_trans, 1, pnoactivitybyset_trans_col_names)
# 3 - No recreation-related physical activity
pnoactivitybyset_rec_m_w_b <- join_m_w_b(pnoactivitybyset_rec, 1, pnoactivitybyset_rec_col_names)
```
```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# urban, rural
# 1 - No work-related physical activity
pnoactivitybyset_work_u_r <- join_u_r(pnoactivitybyset_work, 1, pnoactivitybyset_work_col_names)
# 2 - No transport-related physical activity
pnoactivitybyset_trans_u_r <- join_u_r(pnoactivitybyset_trans, 1, pnoactivitybyset_trans_col_names)
# 3 - No recreation-related physical activity
pnoactivitybyset_rec_u_r <- join_u_r(pnoactivitybyset_rec, 1, pnoactivitybyset_rec_col_names)
```

<br>

```{r}
# 1
cbind(pnoactivitybyset_work_m_w_b$m, select(pnoactivitybyset_work_m_w_b$w, -agerange), select(pnoactivitybyset_work_m_w_b$b, -agerange)) %>% 
  final_m_w_b_tbl(.s_amount = 3, .title = "No work-related physical activity", .colspan_val = 10)
```

<br>

```{r}
# 2
cbind(pnoactivitybyset_trans_m_w_b$m, select(pnoactivitybyset_trans_m_w_b$w, -agerange), select(pnoactivitybyset_trans_m_w_b$b, -agerange)) %>% 
  final_m_w_b_tbl(.s_amount = 3, .title = "No transport-related physical activity", .colspan_val = 10)
```

<br>

```{r}
# 3
cbind(pnoactivitybyset_rec_m_w_b$m, select(pnoactivitybyset_rec_m_w_b$w, -agerange), select(pnoactivitybyset_rec_m_w_b$b, -agerange)) %>% 
  final_m_w_b_tbl(.s_amount = 3, .title = "No recreation-related physical activity", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 1
tbl_m_u_r <- rbind(pnoactivitybyset_work_u_r$m_u, pnoactivitybyset_work_u_r$m_r)
tbl_w_u_r <- rbind(pnoactivitybyset_work_u_r$w_u, pnoactivitybyset_work_u_r$w_r)
tbl_b_u_r <- rbind(pnoactivitybyset_work_u_r$b_u, pnoactivitybyset_work_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_u_r_tbl(.s_amount = 3, .title = "No work-related physical activity by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 2
tbl_m_u_r <- rbind(pnoactivitybyset_trans_u_r$m_u, pnoactivitybyset_trans_u_r$m_r)
tbl_w_u_r <- rbind(pnoactivitybyset_trans_u_r$w_u, pnoactivitybyset_trans_u_r$w_r)
tbl_b_u_r <- rbind(pnoactivitybyset_trans_u_r$b_u, pnoactivitybyset_trans_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_u_r_tbl(.s_amount = 3, .title = "No transport-related physical activity by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 3
tbl_m_u_r <- rbind(pnoactivitybyset_rec_u_r$m_u, pnoactivitybyset_rec_u_r$m_r)
tbl_w_u_r <- rbind(pnoactivitybyset_rec_u_r$w_u, pnoactivitybyset_rec_u_r$w_r)
tbl_b_u_r <- rbind(pnoactivitybyset_rec_u_r$b_u, pnoactivitybyset_rec_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_u_r_tbl(.s_amount = 3, .title = "No recreation-related physical activity by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 1
pnoactivitybyset_work$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = pnoactivitybyset_work_reg_col_names) %>% 
  final_m_w_b_tbl(1, "Both sexes", "No work-related physical activity by region", 4) 
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 2
pnoactivitybyset_trans$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = pnoactivitybyset_trans_reg_col_names) %>% 
  final_m_w_b_tbl(1, "Both sexes", "No transport-related physical activity by region", 4) 
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 3
pnoactivitybyset_rec$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = pnoactivitybyset_rec_reg_col_names) %>% 
  final_m_w_b_tbl(1, "Both sexes", "No recreation-related physical activity by region", 4) 
```

<br>

**Analysis information**:

-   Questions used: P1-P15b
-   R script name: Pnoactivitybyset

***


**Composition of total physical activity**

Description: Percentage of work, transport and recreational activity contributing to total activity.

Instrument questions:

- activity at work
- travel to and from places
- recreational activities

```{r pcomposition_tbls}

# column names to use with huxtable
pcomposition_col_names <- c("Age Group (years)", "n", "%", "95% CI", "%", "95% CI", "%", "95% CI")

pcomposition_reg_col_names <-
  c("Region", "n", "% Activity from work", "95% CI",
    "% Activity for transport", "95% CI", "% Activity during leisure time", "95% CI")

final_tbl_col_names <-
  c("Age Group (years)", "n", "% Activity from work", "95% CI",
    "% Activity for transport", "95% CI", "% Activity during leisure time", "95% CI")

# men, women, both sexes
# 1 - work
pcomposition_work_m_w_b <- join_m_w_b(pcomposition_work, 1, pcomposition_col_names)
# 2 - transport
pcomposition_trans_m_w_b <- join_m_w_b(pcomposition_trans, 1, pcomposition_col_names)
# 3 - recreation
pcomposition_rec_m_w_b <- join_m_w_b(pcomposition_rec, 1, pcomposition_col_names)
```
```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# urban, rural
# 1
pcomposition_work_u_r <- join_u_r(pcomposition_work, 1, pcomposition_col_names)
# 2
pcomposition_trans_u_r <- join_u_r(pcomposition_trans, 1, pcomposition_col_names)
# 3
pcomposition_rec_u_r <- join_u_r(pcomposition_rec, 1, pcomposition_col_names)
```

<br>

```{r}
# NOTE: SPECIFIC CASE OF JOINING TABLES FOR THIS INDICATOR
cbind(pcomposition_work_m_w_b$m, 
      select(pcomposition_trans_m_w_b$m, -c(agerange,n)), 
      select(pcomposition_rec_m_w_b$m, -c(agerange,n))) %>% 
  set_right_border(everywhere, c(4,6), 0) %>% 
  set_contents(1, value = final_tbl_col_names) %>% 
  final_m_w_b_tbl(1, "Men", "Composition of total physical activity", 8) 
```

<br>

```{r}
cbind(pcomposition_work_m_w_b$w, 
      select(pcomposition_trans_m_w_b$w, -c(agerange,n)), 
      select(pcomposition_rec_m_w_b$w, -c(agerange,n))) %>% 
  set_right_border(everywhere, c(4,6), 0) %>% 
  set_contents(1, value = final_tbl_col_names) %>%
  final_m_w_b_tbl(1, "Women", "Composition of total physical activity", 8) 
```

<br>

```{r}
cbind(pcomposition_work_m_w_b$b, 
      select(pcomposition_trans_m_w_b$b, -c(agerange,n)), 
      select(pcomposition_rec_m_w_b$b, -c(agerange,n))) %>% 
  set_right_border(everywhere, c(4,6), 0) %>% 
  set_contents(1, value = final_tbl_col_names) %>%
  final_m_w_b_tbl(1, "Both sexes", "Composition of total physical activity", 8) 
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
tbl_work_m_u_r <- rbind(pcomposition_work_u_r$m_u, pcomposition_work_u_r$m_r)
tbl_trans_m_u_r <- rbind(pcomposition_trans_u_r$m_u, pcomposition_trans_u_r$m_r)
tbl_rec_m_u_r <- rbind(pcomposition_rec_u_r$m_u, pcomposition_rec_u_r$m_r)

cbind(tbl_work_m_u_r, select(tbl_trans_m_u_r, -c(agerange2,n)), select(tbl_rec_m_u_r, -c(agerange2,n))) %>% 
  set_right_border(everywhere, c(4,6), 0) %>% set_contents(1, value = final_tbl_col_names) %>%
  final_u_r_tbl(1, "Men", "Composition of total physical activity by type of settlement", 8)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
tbl_work_w_u_r <- rbind(pcomposition_work_u_r$w_u, pcomposition_work_u_r$w_r)
tbl_trans_w_u_r <- rbind(pcomposition_trans_u_r$w_u, pcomposition_trans_u_r$w_r)
tbl_rec_w_u_r <- rbind(pcomposition_rec_u_r$w_u, pcomposition_rec_u_r$w_r)

cbind(tbl_work_w_u_r, select(tbl_trans_w_u_r, -c(agerange2,n)), select(tbl_rec_w_u_r, -c(agerange2,n))) %>% 
  set_right_border(everywhere, c(4,6), 0) %>% set_contents(1, value = final_tbl_col_names) %>%
  final_u_r_tbl(1, "Women", "Composition of total physical activity by type of settlement", 8)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
tbl_work_b_u_r <- rbind(pcomposition_work_u_r$b_u, pcomposition_work_u_r$b_r)
tbl_trans_b_u_r <- rbind(pcomposition_trans_u_r$b_u, pcomposition_trans_u_r$b_r)
tbl_rec_b_u_r <- rbind(pcomposition_rec_u_r$b_u, pcomposition_rec_u_r$b_r)

cbind(tbl_work_b_u_r, select(tbl_trans_b_u_r, -c(agerange2,n)), select(tbl_rec_b_u_r, -c(agerange2,n))) %>% 
  set_right_border(everywhere, c(4,6), 0) %>% set_contents(1, value = final_tbl_col_names) %>%
  final_u_r_tbl(1, "Both sexes", "Composition of total physical activity by type of settlement", 8)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# region
# 1 + 2 + 3
cbind(pcomposition_work$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = pcomposition_reg_col_names),
      select(pcomposition_trans$b_reg %>% 
               unite_ci(.ci_amount = 1) %>% 
               apply_hux(.col_names = pcomposition_reg_col_names), -c(region,n)),
      select(pcomposition_rec$b_reg %>% 
               unite_ci(.ci_amount = 1) %>% 
               apply_hux(.col_names = pcomposition_reg_col_names), -c(region,n))) %>% 
  set_right_border(everywhere, c(4,6), 0) %>% set_contents(1, value = pcomposition_reg_col_names) %>%
  final_m_w_b_tbl(1, "Both sexes", "Composition of total physical activity", 8)
```

<br>

**Analysis information**:

-   Questions used: P1-P15b
-   R script name: Pcomposition

***


**No vigorous physical activity**

Description: Percentage of respondents not engaging in vigorous physical activity.

Instrument questions:

- activity at work
- recreational activities

```{r pnovigorous_c_tbls}
# column names to use with huxtable
pnovigorous_c_col_names <- c("Age Group (years)", "n", "% no vigorous activity", "95% CI")
pnovigorous_c_reg_col_names <- c("Region", "n", "% no vigorous activity", "95% CI")

# men, women, both sexes
pnovigorous_c_m_w_b <- join_m_w_b(pnovigorous_c, 1, pnovigorous_c_col_names)
```
```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# urban, rural
pnovigorous_c_u_r <- join_u_r(pnovigorous_c, 1, pnovigorous_c_col_names)
```

<br>

```{r}
cbind(pnovigorous_c_m_w_b$m, select(pnovigorous_c_m_w_b$w, -agerange), select(pnovigorous_c_m_w_b$b, -agerange)) %>% 
  final_m_w_b_tbl(.s_amount = 3, .title = "No vigorous physical activity", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
tbl_m_u_r <- rbind(pnovigorous_c_u_r$m_u, pnovigorous_c_u_r$m_r)
tbl_w_u_r <- rbind(pnovigorous_c_u_r$w_u, pnovigorous_c_u_r$w_r)
tbl_b_u_r <- rbind(pnovigorous_c_u_r$b_u, pnovigorous_c_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_u_r_tbl(.s_amount = 3, .title = "No vigorous physical activity by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
pnovigorous_c$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = pnovigorous_c_reg_col_names) %>% 
  final_m_w_b_tbl(1, "Both sexes", "No vigorous physical activity by region", 4) 
```

<br>

**Analysis information**:

-   Questions used: P1-P15b
-   R script name: Pnovigorous

***

**Sedentary**

Description: Minutes spent in sedentary activities on a typical day.

Instrument questions:

- sedentary behaviour

```{r psedentary_tbls}
# column names to use with huxtable
psedentary_col_names <- c("Age Group (years)", "n", "Mean", "95% CI")

psedentary_reg_col_names <- 
  c("Region", "n", "Mean minutes", "95% CI", "Median minutes", "Inter-quartile range (P25-P75)")

final_tbl_col_names <- 
  c("Age Group (years)", "n", "Mean minutes", "95% CI", "Median minutes", "Inter-quartile range (P25-P75)")

# men, women, both sexes
# 1 - mean
psedentary_mn_m_w_b <- join_m_w_b(psedentary_mn, 1, psedentary_col_names)
# 2 - median
psedentary_md_m_w_b <- join_m_w_b(psedentary_md, "q", psedentary_col_names)
```
```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# urban, rural
# 1
psedentary_mn_u_r <- join_u_r(psedentary_mn, 1, psedentary_col_names)
# 2
psedentary_md_u_r <- join_u_r(psedentary_md, "q", psedentary_col_names)
```

<br>

```{r}
# NOTE: SPECIFIC CASE OF JOINING TABLES FOR THIS INDICATOR
cbind(psedentary_mn_m_w_b$m, 
      select(psedentary_md_m_w_b$m, -c(agerange,n))) %>% 
  set_right_border(everywhere, 4, 0) %>% 
  set_contents(1, value = final_tbl_col_names) %>% 
  final_m_w_b_tbl(1, "Men", "Minutes spent in sedentary activities on average per day", 6) 
```

<br>

```{r}
cbind(psedentary_mn_m_w_b$w, 
      select(psedentary_md_m_w_b$w, -c(agerange,n))) %>% 
  set_right_border(everywhere, 4, 0) %>% 
  set_contents(1, value = final_tbl_col_names) %>% 
  final_m_w_b_tbl(1, "Women", "Minutes spent in sedentary activities on average per day", 6) 
```

<br>

```{r}
cbind(psedentary_mn_m_w_b$b, 
      select(psedentary_md_m_w_b$b, -c(agerange,n))) %>% 
  set_right_border(everywhere, 4, 0) %>% 
  set_contents(1, value = final_tbl_col_names) %>% 
  final_m_w_b_tbl(1, "Both sexes", "Minutes spent in sedentary activities on average per day", 6) 
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
tbl_mn_m_u_r <- rbind(psedentary_mn_u_r$m_u, psedentary_mn_u_r$m_r)
tbl_md_m_u_r <- rbind(psedentary_md_u_r$m_u, psedentary_md_u_r$m_r)

cbind(tbl_mn_m_u_r, select(tbl_md_m_u_r, -c(agerange2,n))) %>% 
  set_right_border(everywhere, 4, 0) %>% set_contents(1, value = final_tbl_col_names) %>%
  final_u_r_tbl(1, "Men", "Minutes spent in sedentary activities on average per day by type of settlement", 6)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
tbl_mn_w_u_r <- rbind(psedentary_mn_u_r$w_u, psedentary_mn_u_r$w_r)
tbl_md_w_u_r <- rbind(psedentary_md_u_r$w_u, psedentary_md_u_r$w_r)

cbind(tbl_mn_w_u_r, select(tbl_md_w_u_r, -c(agerange2,n))) %>% 
  set_right_border(everywhere, 4, 0) %>% set_contents(1, value = final_tbl_col_names) %>%
  final_u_r_tbl(1, "Women", "Minutes spent in sedentary activities on average per day by type of settlement", 6)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
tbl_mn_b_u_r <- rbind(psedentary_mn_u_r$b_u, psedentary_mn_u_r$b_r)
tbl_md_b_u_r <- rbind(psedentary_md_u_r$b_u, psedentary_md_u_r$b_r)

cbind(tbl_mn_b_u_r, select(tbl_md_b_u_r, -c(agerange2,n))) %>% 
  set_right_border(everywhere, 4, 0) %>% set_contents(1, value = final_tbl_col_names) %>%
  final_u_r_tbl(1, "Both sexes", "Minutes spent in sedentary activities on average per day by type of settlement", 6)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# region
# mean + median
cbind(psedentary_mn$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = psedentary_col_names),
      select(psedentary_md$b_reg %>% 
               unite_ci(.ci_amount = "q") %>% 
               apply_hux(.col_names = psedentary_col_names), -c(region,n))) %>% 
  set_right_border(everywhere, 4, 0) %>% set_contents(1, value = psedentary_reg_col_names) %>%
  final_m_w_b_tbl(1, "Both sexes", "Minutes spent in sedentary activities on average per day", 6)
```

<br>

**Analysis information**:

-   Questions used: P16a-b
-   R script name: Psedentary

***


<br> 

<br>
