---
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  word_document: default
---

```{r setup, include=FALSE}
library(here)
library(huxtable)
library(tidyverse)
library(fs)
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
# Set a root directory for all chunks to be evaluated relative to rather than the document location
knitr::opts_knit$set(root.dir = here())
```

```{r source, include=FALSE}
here("DataBook", "Modules", "PhysicalMeasurements") %>% 
  # list all R files in the directory
  fs::dir_ls(regexp = "\\.R$") %>% 
  # scale up to all R files with a map function from purrr
  map(source, encoding = "UTF-8", local = knitr::knit_global())
```

---
title: "`r set_title`"
author: "`r set_author`"
---


# Physical Measurements

**Blood pressure**

Description: Mean blood pressure among all respondents, including those currently on medication for raised blood pressure.

Instrument questions:

- Reading 1-3 systolic and diastolic blood pressure.

```{r mbloodpressure_sbp_d_duration_tbls}

# column names to use with huxtable
mbloodpressure_col_names <- c("Age Group (years)", "n", "Mean", "95% CI")
mbloodpressure_reg_col_names <- c("Region", "n", "Mean", "95% CI")

# 1 - Mean systolic blood pressure (mmHg)
# men, women, both sexes
mbloodpressure_sbp_m_w_b <- join_tbls(mbloodpressure_sbp, m_w_b, 1, mbloodpressure_col_names)

# 2 - Mean diastolic blood pressure (mmHg)
# men, women, both sexes
mbloodpressure_dbp_m_w_b <- join_tbls(mbloodpressure_dbp, m_w_b, 1, mbloodpressure_col_names)
```
```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# urban, rural
# 1 - Mean systolic blood pressure (mmHg)
mbloodpressure_sbp_u_r <- join_tbls(mbloodpressure_sbp, u_r, 1, mbloodpressure_col_names)
# 2 - Mean diastolic blood pressure (mmHg)
mbloodpressure_dbp_u_r <- join_tbls(mbloodpressure_dbp, u_r, 1, mbloodpressure_col_names)
```

<br>

```{r}
# 1
cbind(mbloodpressure_sbp_m_w_b$m, select(mbloodpressure_sbp_m_w_b$w, -agerange), select(mbloodpressure_sbp_m_w_b$b, -agerange)) %>% final_tbl(.disaggregation = m_w_b, .s_amount = 3, .title = "Mean systolic blood pressure (mmHg)", .colspan_val = 10)
```

<br>

```{r}
# 2
cbind(mbloodpressure_dbp_m_w_b$m, select(mbloodpressure_dbp_m_w_b$w, -agerange), select(mbloodpressure_dbp_m_w_b$b, -agerange)) %>% final_tbl(.disaggregation = m_w_b, .s_amount = 3, .title = "Mean diastolic blood pressure (mmHg)", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 1
tbl_m_u_r <- rbind(mbloodpressure_sbp_u_r$m_u, mbloodpressure_sbp_u_r$m_r)
tbl_w_u_r <- rbind(mbloodpressure_sbp_u_r$w_u, mbloodpressure_sbp_u_r$w_r)
tbl_b_u_r <- rbind(mbloodpressure_sbp_u_r$b_u, mbloodpressure_sbp_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_tbl(.disaggregation = u_r, .s_amount = 3, .title = "Mean systolic blood pressure (mmHg) by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 2
tbl_m_u_r <- rbind(mbloodpressure_dbp_u_r$m_u, mbloodpressure_dbp_u_r$m_r)
tbl_w_u_r <- rbind(mbloodpressure_dbp_u_r$w_u, mbloodpressure_dbp_u_r$w_r)
tbl_b_u_r <- rbind(mbloodpressure_dbp_u_r$b_u, mbloodpressure_dbp_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_tbl(.disaggregation = u_r, .s_amount = 3, .title = "Mean diastolic blood pressure (mmHg) by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 1
mbloodpressure_sbp$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = mbloodpressure_reg_col_names) %>% final_tbl(reg, 1, "Both sexes", "Mean systolic blood pressure (mmHg) by region", 4)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 2
mbloodpressure_dbp$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = mbloodpressure_reg_col_names) %>% final_tbl(reg, 1, "Both sexes", "Mean diastolic blood pressure (mmHg) by region", 4)
```

<br>

**Analysis information**:

-   Questions used: M4a, M4b, M5a, M5b, M6a, M6b
-   R script name: Mbloodpressure

***

**Raised blood pressure**

Description: Percentage of respondents with raised blood pressure.

Instrument questions:

- Reading 1-3 systolic and diastolic blood pressure 
- During the past two weeks, have you been treated for raised blood pressure with drugs (medication) prescribed by a doctor or other health worker?

```{r mraisedbp_tbls}
# column names to use with huxtable
mraisedbp_col_names <- c("Age Group (years)", "n", "%", "95% CI")
mraisedbp_reg_col_names <- c("Region", "n", "%", "95% CI")

# men, women, both sexes
# 1 (a) - SBP ≥140 and/or DBP ≥ 90 mmHg
raisedbp_140_90_m_w_b <- join_tbls(raisedbp_140_90, m_w_b, 1, mraisedbp_col_names)

# 2 (b) - SBP ≥160 and/or DBP ≥ 100 mmHg
raisedbp_160_100_m_w_b <- join_tbls(raisedbp_160_100, m_w_b, 1, mraisedbp_col_names)

# 3 (c) - SBP ≥140 and/or DBP ≥ 90 mmHg or currently on medication for raised blood pressure
raisedbp_140_90_or_meds_m_w_b <- join_tbls(raisedbp_140_90_or_meds, m_w_b, 1, mraisedbp_col_names)

# 4 (d) - SBP ≥160 and/or DBP ≥ 100 mmHg or currently on medication for raised blood pressure
raisedbp_160_100_or_meds_m_w_b <- join_tbls(raisedbp_160_100_or_meds, m_w_b, 1, mraisedbp_col_names)
```
```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# urban, rural
# 1 - SBP ≥140 and/or DBP ≥ 90 mmHg
raisedbp_140_90_u_r <- join_tbls(raisedbp_140_90, u_r, 1, mraisedbp_col_names)
# 2 - SBP ≥160 and/or DBP ≥ 100 mmHg
raisedbp_160_100_u_r <- join_tbls(raisedbp_160_100, u_r, 1, mraisedbp_col_names)
# 3 - SBP ≥140 and/or DBP ≥ 90 mmHg or currently on medication for raised blood pressure
raisedbp_140_90_or_meds_u_r <- join_tbls(raisedbp_140_90_or_meds, u_r, 1, mraisedbp_col_names)
# 4 - SBP ≥160 and/or DBP ≥ 100 mmHg or currently on medication for raised blood pressure
raisedbp_160_100_or_meds_u_r <- join_tbls(raisedbp_160_100_or_meds, u_r, 1, mraisedbp_col_names)
```

<br>

```{r}
# 1
cbind(raisedbp_140_90_m_w_b$m, select(raisedbp_140_90_m_w_b$w, -agerange), select(raisedbp_140_90_m_w_b$b, -agerange)) %>% final_tbl(.disaggregation = m_w_b, .s_amount = 3, .title = "SBP ≥140 and/or DBP ≥ 90 mmHg", .colspan_val = 10)
```

<br>

```{r}
# 2
cbind(raisedbp_160_100_m_w_b$m, select(raisedbp_160_100_m_w_b$w, -agerange), select(raisedbp_160_100_m_w_b$b, -agerange)) %>% final_tbl(.disaggregation = m_w_b, .s_amount = 3, .title = "SBP ≥160 and/or DBP ≥ 100 mmHg", .colspan_val = 10)
```

<br>

```{r}
# 3
cbind(raisedbp_140_90_or_meds_m_w_b$m, select(raisedbp_140_90_or_meds_m_w_b$w, -agerange), select(raisedbp_140_90_or_meds_m_w_b$b, -agerange)) %>% final_tbl(.disaggregation = m_w_b, .s_amount = 3, .title = "SBP ≥140 and/or DBP ≥ 90 mmHg or currently on medication for raised blood pressure", .colspan_val = 10)
```

<br>

```{r}
# 4
cbind(raisedbp_160_100_or_meds_m_w_b$m, select(raisedbp_160_100_or_meds_m_w_b$w, -agerange), select(raisedbp_160_100_or_meds_m_w_b$b, -agerange)) %>% final_tbl(.disaggregation = m_w_b, .s_amount = 3, .title = "SBP ≥160 and/or DBP ≥ 100 mmHg or currently on medication for raised blood pressure", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 1
tbl_m_u_r <- rbind(raisedbp_140_90_u_r$m_u, raisedbp_140_90_u_r$m_r)
tbl_w_u_r <- rbind(raisedbp_140_90_u_r$w_u, raisedbp_140_90_u_r$w_r)
tbl_b_u_r <- rbind(raisedbp_140_90_u_r$b_u, raisedbp_140_90_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_tbl(.disaggregation = u_r, .s_amount = 3, .title = "SBP ≥140 and/or DBP ≥ 90 mmHg by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 2
tbl_m_u_r <- rbind(raisedbp_160_100_u_r$m_u, raisedbp_160_100_u_r$m_r)
tbl_w_u_r <- rbind(raisedbp_160_100_u_r$w_u, raisedbp_160_100_u_r$w_r)
tbl_b_u_r <- rbind(raisedbp_160_100_u_r$b_u, raisedbp_160_100_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_tbl(.disaggregation = u_r, .s_amount = 3, .title = "SBP ≥160 and/or DBP ≥ 100 mmHg by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 3
tbl_m_u_r <- rbind(raisedbp_140_90_or_meds_u_r$m_u, raisedbp_140_90_or_meds_u_r$m_r)
tbl_w_u_r <- rbind(raisedbp_140_90_or_meds_u_r$w_u, raisedbp_140_90_or_meds_u_r$w_r)
tbl_b_u_r <- rbind(raisedbp_140_90_or_meds_u_r$b_u, raisedbp_140_90_or_meds_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_tbl(.disaggregation = u_r, .s_amount = 3, .title = "SBP ≥140 and/or DBP ≥ 90 mmHg or currently on medication for raised blood pressure by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 4
tbl_m_u_r <- rbind(raisedbp_160_100_or_meds_u_r$m_u, raisedbp_160_100_or_meds_u_r$m_r)
tbl_w_u_r <- rbind(raisedbp_160_100_or_meds_u_r$w_u, raisedbp_160_100_or_meds_u_r$w_r)
tbl_b_u_r <- rbind(raisedbp_160_100_or_meds_u_r$b_u, raisedbp_160_100_or_meds_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_tbl(.disaggregation = u_r, .s_amount = 3, .title = "SBP ≥160 and/or DBP ≥ 100 mmHg or currently on medication for raised blood pressure by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 1
raisedbp_140_90$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = mraisedbp_reg_col_names) %>% final_tbl(reg, 1, "Both sexes", "SBP ≥140 and/or DBP ≥ 90 mmHg by region", 4)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 2
raisedbp_160_100$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = mraisedbp_reg_col_names) %>% final_tbl(reg, 1, "Both sexes", "SBP ≥160 and/or DBP ≥ 100 mmHg by region", 4)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 3
raisedbp_140_90_or_meds$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = mraisedbp_reg_col_names) %>% final_tbl(reg, 1, "Both sexes", "SBP ≥140 and/or DBP ≥ 90 mmHg or currently on medication for raised blood pressure by region", 4)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 4
raisedbp_160_100_or_meds$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = mraisedbp_reg_col_names) %>% final_tbl(reg, 1, "Both sexes", "SBP ≥160 and/or DBP ≥ 100 mmHg or currently on medication for raised blood pressure by region", 4)
```

<br>

**Analysis information**:

-   Questions used: H1, H2a, H3, M4a, M4b, M5a, M5b, M6a, M6b, M7
-   R script name: Mraisedbp

***

**Blood pressure diagnosis, treatment and control**

Description: Raised blood pressure diagnosis, treatment and control among those with raised blood pressure (SBP ≥ 140 and/or DBP ≥ 90 mmHg) or on medication for raised blood pressure.

Instrument questions:

- Have you ever had your blood pressure measured by a doctor or other health worker?
- Have you ever been told by a doctor or other health worker that you have raised blood pressure or hypertension?
- During the past two weeks, have you been treated for raised blood pressure with drugs (medication) prescribed by a doctor or other health worker?
- Reading 1-3 systolic and diastolic blood pressure

```{r htn_control_tbls}

# column names to use with huxtable
htn_control_col_names <- 
  c("Age Group (years)", "n", "% with raised blood pressure, not previously diagnosed", "95% CI", 
    "% with previously diagnosed raised blood pressure, not on medication", "95% CI", 
    "% with previously diagnosed raised blood pressure, on medication but not controlled", "95% CI", 
    "% with previously diagnosed raised blood pressure, on medication and blood pressure controlled", "95% CI")

# column names for region to use with huxtable
htn_control_reg_col_names <- 
  c("Region", "n", "% with raised blood pressure, not previously diagnosed", "95% CI", 
    "% with previously diagnosed raised blood pressure, not on medication", "95% CI", 
    "% with previously diagnosed raised blood pressure, on medication but not controlled", "95% CI", 
    "% with previously diagnosed raised blood pressure, on medication and blood pressure controlled", "95% CI")

# men, women, both sexes
htn_control_m_w_b <- join_tbls(htn_control, m_w_b, 4, htn_control_col_names)
```
```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# urban, rural
htn_control_u_r <- join_tbls(htn_control, u_r, 4, htn_control_col_names)
```

<br>

```{r}
htn_control_m_w_b$m %>% final_tbl(m_w_b, 1, "Men", "Raised blood pressure diagnosis, treatment and control among those with raised blood pressure (SBP ≥ 140 and/or DBP ≥ 90 mmHg) or on medication for raised blood pressure", 10)
```

<br>

```{r}
htn_control_m_w_b$w %>% final_tbl(m_w_b, 1, "Women", "Raised blood pressure diagnosis, treatment and control among those with raised blood pressure (SBP ≥ 140 and/or DBP ≥ 90 mmHg) or on medication for raised blood pressure", 10)
```

<br>

```{r}
htn_control_m_w_b$b %>% final_tbl(m_w_b, 1, "Both sexes", "Raised blood pressure diagnosis, treatment and control among those with raised blood pressure (SBP ≥ 140 and/or DBP ≥ 90 mmHg) or on medication for raised blood pressure", 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
rbind(htn_control_u_r$m_u, htn_control_u_r$m_r) %>% 
  final_tbl(u_r, 1, "Men", "Raised blood pressure diagnosis, treatment and control among those with raised blood pressure (SBP ≥ 140 and/or DBP ≥ 90 mmHg) or on medication for raised blood pressure by type of settlement", 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
rbind(htn_control_u_r$w_u, htn_control_u_r$w_r) %>% 
  final_tbl(u_r, 1, "Women", "Raised blood pressure diagnosis, treatment and control among those with raised blood pressure (SBP ≥ 140 and/or DBP ≥ 90 mmHg) or on medication for raised blood pressure by type of settlement", 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
rbind(htn_control_u_r$b_u, htn_control_u_r$b_r) %>% 
  final_tbl(u_r, 1, "Both sexes", "Raised blood pressure diagnosis, treatment and control among those with raised blood pressure (SBP ≥ 140 and/or DBP ≥ 90 mmHg) or on medication for raised blood pressure by type of settlement", 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# region
htn_control$b_reg %>% unite_ci(.ci_amount = 4) %>% apply_hux(.col_names = htn_control_reg_col_names) %>% 
  final_tbl(reg, 1, "Both sexes", "Raised blood pressure diagnosis, treatment and control among those with raised blood pressure (SBP ≥ 140 and/or DBP ≥ 90 mmHg) or on medication for raised blood pressure by region", 10) 
```

**Hypertension control (presented as in previous STEPS with three categories instead of current four)**

```{r bp_control_old_tbls}

# column names to use with huxtable
bp_control_old_col_names <- 
  c("Age Group (years)", "n", "% on medication and BP not raised", "95% CI", 
    "% on medication and BP raised", "95% CI", 
    "% not on medication and BP raised", "95% CI")

# column names for region to use with huxtable
bp_control_old_reg_col_names <- 
  c("Region", "n", "% on medication and BP not raised", "95% CI", 
    "% on medication and BP raised", "95% CI", 
    "% not on medication and BP raised", "95% CI")

# men, women, both sexes
bp_control_old_m_w_b <- join_tbls(bp_control_old, m_w_b, 3, bp_control_old_col_names)
```
```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# urban, rural
bp_control_old_u_r <- join_tbls(bp_control_old, u_r, 3, bp_control_old_col_names)
```

<br>

```{r}
bp_control_old_m_w_b$m %>% final_tbl(m_w_b, 1, "Men", "Raised blood pressure diagnosis, treatment and control among those with raised blood pressure (SBP ≥ 140 and/or DBP ≥ 90 mmHg) or on medication for raised blood pressure", 8)
```

<br>

```{r}
bp_control_old_m_w_b$w %>% final_tbl(m_w_b, 1, "Women", "Raised blood pressure diagnosis, treatment and control among those with raised blood pressure (SBP ≥ 140 and/or DBP ≥ 90 mmHg) or on medication for raised blood pressure", 8)
```

<br>

```{r}
bp_control_old_m_w_b$b %>% final_tbl(m_w_b, 1, "Both sexes", "Raised blood pressure diagnosis, treatment and control among those with raised blood pressure (SBP ≥ 140 and/or DBP ≥ 90 mmHg) or on medication for raised blood pressure", 8)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
rbind(bp_control_old_u_r$m_u, bp_control_old_u_r$m_r) %>% 
  final_tbl(u_r, 1, "Men", "Raised blood pressure diagnosis, treatment and control among those with raised blood pressure (SBP ≥ 140 and/or DBP ≥ 90 mmHg) or on medication for raised blood pressure by type of settlement", 8)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
rbind(bp_control_old_u_r$w_u, bp_control_old_u_r$w_r) %>% 
  final_tbl(u_r, 1, "Women", "Raised blood pressure diagnosis, treatment and control among those with raised blood pressure (SBP ≥ 140 and/or DBP ≥ 90 mmHg) or on medication for raised blood pressure by type of settlement", 8)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
rbind(bp_control_old_u_r$b_u, bp_control_old_u_r$b_r) %>% 
  final_tbl(u_r, 1, "Both sexes", "Raised blood pressure diagnosis, treatment and control among those with raised blood pressure (SBP ≥ 140 and/or DBP ≥ 90 mmHg) or on medication for raised blood pressure by type of settlement", 8)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# region
bp_control_old$b_reg %>% unite_ci(.ci_amount = 3) %>% apply_hux(.col_names = bp_control_old_reg_col_names) %>% 
  final_tbl(reg, 1, "Both sexes", "Raised blood pressure diagnosis, treatment and control among those with raised blood pressure (SBP ≥ 140 and/or DBP ≥ 90 mmHg) or on medication for raised blood pressure by region", 8) 
```

<br>

**Analysis information**:

-   Questions used: H1, H2a, H3, M4a, M4b, M5a, M5b, M6a, M6b, M7
-   R script name: Mraisedbp

***


**Mean heart rate**

Description: Mean heart rate (beats per minute).

Instrument questions:

- Reading 1-3 heart rate

```{r mheartrate_mn_tbls}
# column names to use with huxtable
mheartrate_mn_col_names <- c("Age Group (years)", "n", "Mean", "95% CI")
mheartrate_mn_reg_col_names <- c("Region", "n", "Mean", "95% CI")

# men, women, both sexes
mheartrate_mn_m_w_b <- join_tbls(mheartrate_mn, m_w_b, 1, mheartrate_mn_col_names)
```
```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# urban, rural
mheartrate_mn_u_r <- join_tbls(mheartrate_mn, u_r, 1, mheartrate_mn_col_names)
```

<br>

```{r}
cbind(mheartrate_mn_m_w_b$m, select(mheartrate_mn_m_w_b$w, -agerange), select(mheartrate_mn_m_w_b$b, -agerange)) %>% 
  final_tbl(.disaggregation = m_w_b, .s_amount = 3, .title = "Mean heart rate (beats per minute)", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
tbl_m_u_r <- rbind(mheartrate_mn_u_r$m_u, mheartrate_mn_u_r$m_r)
tbl_w_u_r <- rbind(mheartrate_mn_u_r$w_u, mheartrate_mn_u_r$w_r)
tbl_b_u_r <- rbind(mheartrate_mn_u_r$b_u, mheartrate_mn_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_tbl(.disaggregation = u_r, .s_amount = 3, .title = "Mean heart rate (beats per minute) by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
mheartrate_mn$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = mheartrate_mn_reg_col_names) %>% 
  final_tbl(reg, 1, "Both sexes", "Mean heart rate (beats per minute) by region", 4)
```

<br>

**Analysis information**:

-   Questions used: M16a, M16b, M16c
-   R script name: Mheartrate

***

**Height, weight and BMI**

Description: Mean height, weight, and body mass index among all respondents (excluding pregnant women).

Instrument questions:

- For women: Are you pregnant?
- Height
- Weight

```{r mbmi_tbls}
# column names to use with huxtable
mbmi_col_names <- c("Age Group (years)", "n", "Mean", "95% CI")
mbmi_reg_col_names <- c("Region", "n", "Mean", "95% CI")

# men, women, both sexes
# 1. Mean height (cm)
mbmi_m11_m_w_b <- join_tbls(mbmi_m11, m_w_b, 1, mbmi_col_names)
# 2. Mean weight (kg)
mbmi_m12_m_w_b <- join_tbls(mbmi_m12, m_w_b, 1, mbmi_col_names)
# 3. Mean BMI (kg/m2)
mbmi_m_w_b <- join_tbls(mbmi, m_w_b, 1, mbmi_col_names)
```
```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# urban, rural
# 1. Mean height (cm)
mbmi_m11_u_r <- join_tbls(mbmi_m11, u_r, 1, mbmi_col_names)
# 2. Mean weight (kg)
mbmi_m12_u_r <- join_tbls(mbmi_m12, u_r, 1, mbmi_col_names)
# 3. Mean BMI (kg/m2)
mbmi_u_r <- join_tbls(mbmi, u_r, 1, mbmi_col_names)
```

<br>

```{r}
# 1. Mean height (cm)
# ONLY MEN AND WOMEN INCLUDED
cbind(mbmi_m11_m_w_b$m, select(mbmi_m11_m_w_b$w, -agerange), select(mbmi_m11_m_w_b$b, -agerange)) %>% 
  final_tbl(.disaggregation = m_w_b, .s_amount = 3, .title = "Mean height (cm)", .colspan_val = 7) %>% select(c(1:7))
```

<br>

```{r}
# 2. Mean weight (kg)
# ONLY MEN AND WOMEN INCLUDED
cbind(mbmi_m12_m_w_b$m, select(mbmi_m12_m_w_b$w, -agerange), select(mbmi_m12_m_w_b$b, -agerange)) %>% 
  final_tbl(.disaggregation = m_w_b, .s_amount = 3, .title = "Mean weight (kg)", .colspan_val = 7) %>% select(c(1:7))
```

<br>

```{r}
# 3. Mean BMI (kg/m2)
cbind(mbmi_m_w_b$m, select(mbmi_m_w_b$w, -agerange), select(mbmi_m_w_b$b, -agerange)) %>% 
  final_tbl(.disaggregation = m_w_b, .s_amount = 3, .title = "Mean BMI (kg/m2)", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 1. Mean height (cm)
tbl_m_u_r <- rbind(mbmi_m11_u_r$m_u, mbmi_m11_u_r$m_r)
tbl_w_u_r <- rbind(mbmi_m11_u_r$w_u, mbmi_m11_u_r$w_r)
tbl_b_u_r <- rbind(mbmi_m11_u_r$b_u, mbmi_m11_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_tbl(.disaggregation = u_r, .s_amount = 3, .title = "Mean height (cm) by type of settlement", .colspan_val = 7) %>% select(c(1:7))
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 2. Mean weight (kg)
tbl_m_u_r <- rbind(mbmi_m12_u_r$m_u, mbmi_m12_u_r$m_r)
tbl_w_u_r <- rbind(mbmi_m12_u_r$w_u, mbmi_m12_u_r$w_r)
tbl_b_u_r <- rbind(mbmi_m12_u_r$b_u, mbmi_m12_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_tbl(.disaggregation = u_r, .s_amount = 3, .title = "Mean weight (kg) by type of settlement", .colspan_val = 7) %>% select(c(1:7))
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 3. Mean BMI (kg/m2)
tbl_m_u_r <- rbind(mbmi_u_r$m_u, mbmi_u_r$m_r)
tbl_w_u_r <- rbind(mbmi_u_r$w_u, mbmi_u_r$w_r)
tbl_b_u_r <- rbind(mbmi_u_r$b_u, mbmi_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_tbl(.disaggregation = u_r, .s_amount = 3, .title = "Mean BMI (kg/m2) by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 1. Mean height (cm)
# mbmi_m11$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = mbmi_reg_col_names) %>% 
#   final_tbl(reg, 1, "Both sexes", "Mean height (cm) by region", 4) 
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 2. Mean weight (kg)
# mbmi_m12$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = mbmi_reg_col_names) %>% 
#   final_tbl(reg, 1, "Both sexes", "Mean weight (kg) by region", 4) 
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 3. Mean BMI (kg/m2)
mbmi$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = mbmi_reg_col_names) %>% 
  final_tbl(reg, 1, "Both sexes", "Mean BMI (kg/m2) by region", 4) 
```

<br>

**Analysis information**:

-   Questions used: M8, M11, M12
-   R script name: Mbmi

***

**BMI categories**

Description: Percentage of respondents (excluding pregnant women) in each BMI category.

Instrument questions:

- For women: Are you pregnant?
- Height
- Weight

```{r mbmiclass_c_tbls}
# column names to use with huxtable
mbmiclass_c_col_names <- 
  c("Age Group (years)", "n", "% Under-weight <18.5", "95% CI", "% Normal weight 18.5-24.9", "95% CI", 
    "% BMI 25.0-29.9", "95% CI", "% Obese ≥30.0", "95% CI")

# column names for region to use with huxtable
mbmiclass_c_reg_col_names <- 
  c("Region", "n", "% Under-weight <18.5", "95% CI", "% Normal weight 18.5-24.9", "95% CI", 
    "% BMI 25.0-29.9", "95% CI", "% Obese ≥30.0", "95% CI")

# men, women, both sexes
mbmiclass_c_m_w_b <- join_tbls(mbmiclass_c, m_w_b, 4, mbmiclass_c_col_names)
```
```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# urban, rural
mbmiclass_c_u_r <- join_tbls(mbmiclass_c, u_r, 4, mbmiclass_c_col_names)
```

<br>

```{r}
mbmiclass_c_m_w_b$m %>% final_tbl(m_w_b, 1, "Men", "BMI classifications", 10)
```

<br>

```{r}
mbmiclass_c_m_w_b$w %>% final_tbl(m_w_b, 1, "Women", "BMI classifications", 10)
```

<br>

```{r}
mbmiclass_c_m_w_b$b %>% final_tbl(m_w_b, 1, "Both sexes", "BMI classifications", 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
rbind(mbmiclass_c_u_r$m_u, mbmiclass_c_u_r$m_r) %>% 
  final_tbl(u_r, 1, "Men", "BMI classifications by type of settlement", 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
rbind(mbmiclass_c_u_r$w_u, mbmiclass_c_u_r$w_r) %>% 
  final_tbl(u_r, 1, "Women", "BMI classifications by type of settlement", 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
rbind(mbmiclass_c_u_r$b_u, mbmiclass_c_u_r$b_r) %>% 
  final_tbl(u_r, 1, "Both sexes", "BMI classifications by type of settlement", 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# region
mbmiclass_c$b_reg %>% unite_ci(.ci_amount = 4) %>% apply_hux(.col_names = mbmiclass_c_reg_col_names) %>% 
  final_tbl(reg, 1, "Both sexes", "BMI classifications by region", 10) 
```

<br>

**Analysis information**:

-   Questions used: M8, M11, M12
-   R script name: Mbmiclass

***

**BMI ≥25**

Description: Percentage of respondents (excluding pregnant women) classified as overweight (BMI≥25).

Instrument questions:

- For women: Are you pregnant?
- Height
- Weight

```{r mbmiclass_d_tbls}
# column names to use with huxtable
mbmiclass_d_col_names <- c("Age Group (years)", "n", "% BMI≥25", "95% CI")
mbmiclass_d_reg_col_names <- c("Region", "n", "% BMI≥25", "95% CI")

# men, women, both sexes
mbmiclass_d_m_w_b <- join_tbls(mbmiclass_d, m_w_b, 1, mbmiclass_d_col_names)
```
```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# urban, rural
mbmiclass_d_u_r <- join_tbls(mbmiclass_d, u_r, 1, mbmiclass_d_col_names)
```

<br>

```{r}
cbind(mbmiclass_d_m_w_b$m, select(mbmiclass_d_m_w_b$w, -agerange), select(mbmiclass_d_m_w_b$b, -agerange)) %>% 
  final_tbl(.disaggregation = m_w_b, .s_amount = 3, .title = "BMI≥25", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
tbl_m_u_r <- rbind(mbmiclass_d_u_r$m_u, mbmiclass_d_u_r$m_r)
tbl_w_u_r <- rbind(mbmiclass_d_u_r$w_u, mbmiclass_d_u_r$w_r)
tbl_b_u_r <- rbind(mbmiclass_d_u_r$b_u, mbmiclass_d_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_tbl(.disaggregation = u_r, .s_amount = 3, .title = "BMI≥25 by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
mbmiclass_d$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = mbmiclass_d_reg_col_names) %>% 
  final_tbl(reg, 1, "Both sexes", "BMI≥25 by region", 4)
```

<br>

**Analysis information**:

-   Questions used: M8, M11, M12
-   R script name: Mbmiclass

***

**Waist circumference**

Description: Mean waist circumference among all respondents (excluding pregnant women).

Instrument questions:

- For women: Are you pregnant?
- Waist circumference measurement

```{r mwaist_tbls}
# column names to use with huxtable
mwaist_col_names <- c("Age Group (years)", "n", "Mean", "95% CI")
mwaist_reg_col_names <- c("Region", "n", "Mean", "95% CI")

# men, women, both sexes
mwaist_m_w_b <- join_tbls(mwaist, m_w_b, 1, mwaist_col_names)
```
```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# urban, rural
mwaist_u_r <- join_tbls(mwaist, u_r, 1, mwaist_col_names)
```

<br>

```{r}
# ONLY MEN AND WOMEN INCLUDED
cbind(mwaist_m_w_b$m, select(mwaist_m_w_b$w, -agerange), select(mwaist_m_w_b$b, -agerange)) %>% 
  final_tbl(.disaggregation = m_w_b, .s_amount = 3, .title = "Waist circumference (cm)", .colspan_val = 7) %>% select(c(1:7))
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
tbl_m_u_r <- rbind(mwaist_u_r$m_u, mwaist_u_r$m_r)
tbl_w_u_r <- rbind(mwaist_u_r$w_u, mwaist_u_r$w_r)
tbl_b_u_r <- rbind(mwaist_u_r$b_u, mwaist_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_tbl(.disaggregation = u_r, .s_amount = 3, .title = "Waist circumference (cm) by type of settlement", .colspan_val = 7) %>% select(c(1:7))
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# mwaist_m11$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = mwaist_reg_col_names) %>% 
#   final_tbl(reg, 1, "Both sexes", "Waist circumference (cm) by region", 4) 
```

<br>

**Analysis information**:

-   Questions used: M8, M14
-   R script name: Mwaist

***


**Hip circumference**

Description: Mean hip circumference among all respondents (excluding pregnant women).

Instrument questions:

- For women: Are you pregnant?
- Hip circumference measurement

```{r mhip_tbls}
# column names to use with huxtable
mhip_col_names <- c("Age Group (years)", "n", "Mean", "95% CI")
mhip_reg_col_names <- c("Region", "n", "Mean", "95% CI")

# men, women, both sexes
mhip_m_w_b <- join_tbls(mhip, m_w_b, 1, mhip_col_names)
```
```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# urban, rural
mhip_u_r <- join_tbls(mhip, u_r, 1, mhip_col_names)
```

<br>

```{r}
# ONLY MEN AND WOMEN INCLUDED
cbind(mhip_m_w_b$m, select(mhip_m_w_b$w, -agerange), select(mhip_m_w_b$b, -agerange)) %>% 
  final_tbl(.disaggregation = m_w_b, .s_amount = 3, .title = "Hip circumference (cm)", .colspan_val = 7) %>% select(c(1:7))
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
tbl_m_u_r <- rbind(mhip_u_r$m_u, mhip_u_r$m_r)
tbl_w_u_r <- rbind(mhip_u_r$w_u, mhip_u_r$w_r)
tbl_b_u_r <- rbind(mhip_u_r$b_u, mhip_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_tbl(.disaggregation = u_r, .s_amount = 3, .title = "Hip circumference (cm) by type of settlement", .colspan_val = 7) %>% select(c(1:7))
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# mhip_m11$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = mhip_reg_col_names) %>% 
#   final_tbl(reg, 1, "Both sexes", "Hip circumference (cm) by region", 4) 
```

<br>

**Analysis information**:

-   Questions used: M8, M15
-   R script name: Mhip

***


<br> 

<br>
