---
title: "STEPS MDA Data Book"
author: "WHO NCD Office Moscow"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  word_document: default
  html_document:
    css: style.css
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
library(here)
library(huxtable)
library(tidyverse)
library(fs)
```

```{r source, include=FALSE}
combined_risk_factors_data_dir <- here::here("DataBook", "Modules", "SummaryofCombinedRiskFactors")

# list all files in the directory
# fs::dir_ls(combined_risk_factors_data_dir)

# only R files
r_files <- fs::dir_ls(combined_risk_factors_data_dir, regexp = "\\.R$") 
# r_files

# read in just one R file for testing
# source(r_files[1])

# scale up to all R files with a map function from purrr
r_files %>% 
  map(source, encoding = "UTF-8", local = knitr::knit_global())
```

```{r databook_functions, echo=FALSE}
source(here("DataBook", "databook_functions.R"), encoding = "UTF-8", local = knitr::knit_global())
```

```{r}
m_w_b <- c("m","w","b")
u_r <- c("m_u","w_u","b_u","m_r","w_r","b_r")
```

# Summary of Combined Risk Factors

**Summary of Combined Risk Factors**

Description: Percentage of respondents with 0, 1–2, or 3–5 of the following risk factors:

- Current daily smoking
- Less than five servings of fruit and/or vegetables per day
- Not meeting WHO recommendations on physical activity for health (<150 minutes of moderate activity per week, or equivalent)
- Overweight or obese (BMI ≥ 25 kg/m2)
- Raised BP (SBP ≥ 140 and/or DBP ≥ 90 mmHg or currently on medication for raised BP).

Instrument questions: combined from Step 1 and Step 2

```{r raisedrisk_tbls}
# column names to use with huxtable
raisedrisk_col_names <- 
  c("Age Group (years)", "n", "% with 0 risk factors", "95% CI", "% with 1-2 risk factors", "95% CI", 
    "% with 3-5 risk factors", "95% CI")

# column names for region to use with huxtable
raisedrisk_reg_col_names <- 
  c("Region", "n", "% with 0 risk factors", "95% CI", "% with 1-2 risk factors", "95% CI", 
    "% with 3-5 risk factors", "95% CI")

# men, women, both sexes
raisedrisk_m_w_b <- join_m_w_b(raisedrisk, 3, raisedrisk_col_names)
```
```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# urban, rural
raisedrisk_u_r <- join_u_r(raisedrisk, 3, raisedrisk_col_names)
```

<br>

```{r}
raisedrisk_m_w_b$m %>% final_m_w_b_tbl(1, "Men", "Summary of Combined Risk Factors", 8)
```

<br>

```{r}
raisedrisk_m_w_b$w %>% final_m_w_b_tbl(1, "Women", "Summary of Combined Risk Factors", 8)
```

<br>

```{r}
raisedrisk_m_w_b$b %>% final_m_w_b_tbl(1, "Both sexes", "Summary of Combined Risk Factors", 8)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
rbind(raisedrisk_u_r$m_u, raisedrisk_u_r$m_r) %>% 
  final_u_r_tbl(1, "Men", "Summary of Combined Risk Factors by type of settlement", 8)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
rbind(raisedrisk_u_r$w_u, raisedrisk_u_r$w_r) %>% 
  final_u_r_tbl(1, "Women", "Summary of Combined Risk Factors by type of settlement", 8)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
rbind(raisedrisk_u_r$b_u, raisedrisk_u_r$b_r) %>% 
  final_u_r_tbl(1, "Both sexes", "Summary of Combined Risk Factors by type of settlement", 8)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# region
raisedrisk$b_reg %>% unite_ci(.ci_amount = 3) %>% apply_hux(.col_names = raisedrisk_reg_col_names) %>% 
  final_m_w_b_tbl(1, "Both sexes", "Summary of Combined Risk Factors by region", 8) 
```

<br>

**Analysis information**:

- Questions used: T1, T2, D1-D4, P1-P15b, M4a-M6b, M7, M8, M11, M12
- R script name: Raisedrisk

***



<br>
<br>
