---
title: "STEPS MDA Data Book"
author: "WHO NCD Office Moscow"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  word_document: default
  html_document:
    css: style.css
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
library(here)
library(huxtable)
library(tidyverse)
library(fs)
```

```{r source, include=FALSE}
tobacco_policy_data_dir <- here::here("DataBook", "Modules", "TobaccoPolicy")

# list all files in the directory
# fs::dir_ls(tobacco_policy_data_dir)

# only R files
r_files <- fs::dir_ls(tobacco_policy_data_dir, regexp = "\\.R$") 
# r_files

# read in just one R file for testing
# source(r_files[1])

# scale up to all R files with a map function from purrr
r_files %>% 
  map(source, encoding = "UTF-8", local = knitr::knit_global())
```

```{r databook_functions, echo=FALSE}
source(here("DataBook", "databook_functions.R"), encoding = "UTF-8", local = knitr::knit_global())
```

```{r}
m_w_b <- c("m","w","b")
u_r <- c("m_u","w_u","b_u","m_r","w_r","b_r")
title_u_r <- "by type of settlement"
title_reg <- "by region"
```

# Tobacco Policy

**Anti-cigarette information**

Description: Percentage of all respondents who noticed information in newspapers or magazines, television or radio about the dangers of smoking or that encourages quitting during the past 30 days.

Instrument questions:

- During the past 30 days, have you noticed information about the dangers of smoking cigarettes or that encourages quitting through the following media?
- Newspapers or magazines
- Television
- Radio

```{r tpdanger_c_d_e_tbls}
# column names to use with huxtable
tpdanger_col_names <- c("Age Group (years)", "n", "%", "95% CI")
tpdanger_reg_col_names <- c("Region", "n", "%", "95% CI")

# men, women, both sexes
# 1 - Noticed information in newspapers or magazines about dangers of smoking or that encourages quitting
tpdanger_c_m_w_b <- join_m_w_b(tpdanger_c, 1, tpdanger_col_names)
# 2 - Noticed information on television about dangers of smoking or that encourages quitting
tpdanger_d_m_w_b <- join_m_w_b(tpdanger_d, 1, tpdanger_col_names)
# 3 - Noticed information on the radio about dangers of smoking or that encourages quitting
tpdanger_e_m_w_b <- join_m_w_b(tpdanger_e, 1, tpdanger_col_names)
```
```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# urban, rural
tpdanger_c_u_r <- join_u_r(tpdanger_c, 1, tpdanger_col_names) # 1
tpdanger_d_u_r <- join_u_r(tpdanger_d, 1, tpdanger_col_names) # 2
tpdanger_e_u_r <- join_u_r(tpdanger_e, 1, tpdanger_col_names) # 3
```

<br>

```{r}
# 1
cbind(tpdanger_c_m_w_b$m, select(tpdanger_c_m_w_b$w, -agerange), select(tpdanger_c_m_w_b$b, -agerange)) %>% 
  final_m_w_b_tbl(.s_amount = 3, .title = "Noticed information in newspapers or magazines about dangers of smoking or that encourages quitting", .colspan_val = 10)
```

<br>

```{r}
# 2
cbind(tpdanger_d_m_w_b$m, select(tpdanger_d_m_w_b$w, -agerange), select(tpdanger_d_m_w_b$b, -agerange)) %>% 
  final_m_w_b_tbl(.s_amount = 3, .title = "Noticed information on television about dangers of smoking or that encourages quitting", .colspan_val = 10)
```

<br>

```{r}
# 3
cbind(tpdanger_e_m_w_b$m, select(tpdanger_e_m_w_b$w, -agerange), select(tpdanger_e_m_w_b$b, -agerange)) %>% 
  final_m_w_b_tbl(.s_amount = 3, .title = "Noticed information on the radio about dangers of smoking or that encourages quitting", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 1
tbl_m_u_r <- rbind(tpdanger_c_u_r$m_u, tpdanger_c_u_r$m_r)
tbl_w_u_r <- rbind(tpdanger_c_u_r$w_u, tpdanger_c_u_r$w_r)
tbl_b_u_r <- rbind(tpdanger_c_u_r$b_u, tpdanger_c_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_u_r_tbl(.s_amount = 3, .title = "Noticed information in newspapers or magazines about dangers of smoking or that encourages quitting by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 2
tbl_m_u_r <- rbind(tpdanger_d_u_r$m_u, tpdanger_d_u_r$m_r)
tbl_w_u_r <- rbind(tpdanger_d_u_r$w_u, tpdanger_d_u_r$w_r)
tbl_b_u_r <- rbind(tpdanger_d_u_r$b_u, tpdanger_d_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_u_r_tbl(.s_amount = 3, .title = "Noticed information on television about dangers of smoking or that encourages quitting by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 3
tbl_m_u_r <- rbind(tpdanger_e_u_r$m_u, tpdanger_e_u_r$m_r)
tbl_w_u_r <- rbind(tpdanger_e_u_r$w_u, tpdanger_e_u_r$w_r)
tbl_b_u_r <- rbind(tpdanger_e_u_r$b_u, tpdanger_e_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_u_r_tbl(.s_amount = 3, .title = "Noticed information on the radio about dangers of smoking or that encourages quitting by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 1
tpdanger_c$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = tpdanger_reg_col_names) %>% 
  final_m_w_b_tbl(.s_amount = 1, .s_val = "Both sexes", .title = "Noticed information in newspapers or magazines about dangers of smoking or that encourages quitting by region", .colspan_val = 4) 
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 2
tpdanger_d$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = tpdanger_reg_col_names) %>% 
  final_m_w_b_tbl(.s_amount = 1, .s_val = "Both sexes", .title = "Noticed information on television about dangers of smoking or that encourages quitting by region", .colspan_val = 4) 
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 3
tpdanger_e$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = tpdanger_reg_col_names) %>% 
  final_m_w_b_tbl(.s_amount = 1, .s_val = "Both sexes", .title = "Noticed information on the radio about dangers of smoking or that encourages quitting by region", .colspan_val = 4) 
```
<br>

**Analysis information**:

- Questions used: TP1a-c
- R script name: TPdanger

***

**Cigarette advertising**

Description: Percentage of all respondents who noticed advertisements or signs promoting cigarettes in stores where cigarettes are sold during the past 30 days.

Instrument questions:

- During the past 30 days, have you noticed any advertisements or signs promoting cigarettes in stores where cigarettes are sold?

```{r tpcigads_c_tbls}
# column names to use with huxtable
tpcigads_c_col_names <- c("Age Group (years)", "n", "%", "95% CI")
tpcigads_c_reg_col_names <- c("Region", "n", "%", "95% CI")

# men, women, both sexes
tpcigads_c_m_w_b <- join_m_w_b(tpcigads_c, 1, tpcigads_c_col_names)
```
```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# urban, rural
tpcigads_c_u_r <- join_u_r(tpcigads_c, 1, tpcigads_c_col_names)
```

<br>

```{r}
cbind(tpcigads_c_m_w_b$m, select(tpcigads_c_m_w_b$w, -agerange), select(tpcigads_c_m_w_b$b, -agerange)) %>% 
  final_m_w_b_tbl(.s_amount = 3, .title = "Noticed advertisements or signs promoting cigarettes in stores", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
tbl_m_u_r <- rbind(tpcigads_c_u_r$m_u, tpcigads_c_u_r$m_r)
tbl_w_u_r <- rbind(tpcigads_c_u_r$w_u, tpcigads_c_u_r$w_r)
tbl_b_u_r <- rbind(tpcigads_c_u_r$b_u, tpcigads_c_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_u_r_tbl(.s_amount = 3, .title = "Noticed advertisements or signs promoting cigarettes in stores by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
tpcigads_c$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = tpcigads_c_reg_col_names) %>% 
  final_m_w_b_tbl(1, "Both sexes", "Noticed advertisements or signs promoting cigarettes in stores by region", 4)
```
<br>

**Analysis information**:

- Questions used: TP2
- R script name: TPcigads

***

**Cigarette promotion**

Description: Percentage of all respondents who noticed cigarette promotions during the past 30 days.

Instrument questions:

- During the past 30 days, have you noticed any of the following types of cigarette promotions?

```{r tpcigpromos_a_b_c_d_e_f_tbls}
# column names to use with huxtable
tpcigpromos_col_names <- c("Age Group (years)", "n", "%", "95% CI")
tpcigpromos_reg_col_names <- c("Region", "n", "%", "95% CI")

# men, women, both sexes
# 1 - Noticed free samples of cigarettes
tpcigpromos_a_m_w_b <- join_m_w_b(tpcigpromos_a, 1, tpcigpromos_col_names)
# 2 - Noticed sale prices on cigarettes
tpcigpromos_b_m_w_b <- join_m_w_b(tpcigpromos_b, 1, tpcigpromos_col_names)
# 3 - Noticed coupons for cigarettes
tpcigpromos_c_m_w_b <- join_m_w_b(tpcigpromos_c, 1, tpcigpromos_col_names)
# 4 - Noticed free gifts or special discount offers on other products when buying cigarettes
tpcigpromos_d_m_w_b <- join_m_w_b(tpcigpromos_d, 1, tpcigpromos_col_names)
# 5 - Noticed clothing or other items with a cigarette brand name or logo
tpcigpromos_e_m_w_b <- join_m_w_b(tpcigpromos_e, 1, tpcigpromos_col_names)
# 6 - Noticed cigarette promotions in the mail
tpcigpromos_f_m_w_b <- join_m_w_b(tpcigpromos_f, 1, tpcigpromos_col_names)
```
```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# urban, rural
tpcigpromos_a_u_r <- join_u_r(tpcigpromos_a, 1, tpcigpromos_col_names) # 1
tpcigpromos_b_u_r <- join_u_r(tpcigpromos_b, 1, tpcigpromos_col_names) # 2
tpcigpromos_c_u_r <- join_u_r(tpcigpromos_c, 1, tpcigpromos_col_names) # 3
tpcigpromos_d_u_r <- join_u_r(tpcigpromos_d, 1, tpcigpromos_col_names) # 4
tpcigpromos_e_u_r <- join_u_r(tpcigpromos_e, 1, tpcigpromos_col_names) # 5
tpcigpromos_f_u_r <- join_u_r(tpcigpromos_f, 1, tpcigpromos_col_names) # 6
```

<br>

```{r}
# 1
cbind(tpcigpromos_a_m_w_b$m, select(tpcigpromos_a_m_w_b$w, -agerange), select(tpcigpromos_a_m_w_b$b, -agerange)) %>% 
  final_m_w_b_tbl(.s_amount = 3, .title = "Noticed free samples of cigarettes", .colspan_val = 10)
```

<br>

```{r}
# 2
cbind(tpcigpromos_b_m_w_b$m, select(tpcigpromos_b_m_w_b$w, -agerange), select(tpcigpromos_b_m_w_b$b, -agerange)) %>% 
  final_m_w_b_tbl(.s_amount = 3, .title = "Noticed sale prices on cigarettes", .colspan_val = 10)
```

<br>

```{r}
# 3
cbind(tpcigpromos_c_m_w_b$m, select(tpcigpromos_c_m_w_b$w, -agerange), select(tpcigpromos_c_m_w_b$b, -agerange)) %>% 
  final_m_w_b_tbl(.s_amount = 3, .title = "Noticed coupons for cigarettes", .colspan_val = 10)
```

<br>

```{r}
# 4
cbind(tpcigpromos_d_m_w_b$m, select(tpcigpromos_d_m_w_b$w, -agerange), select(tpcigpromos_d_m_w_b$b, -agerange)) %>% 
  final_m_w_b_tbl(.s_amount = 3, .title = "Noticed free gifts or special discount offers on other products when buying cigarettes", .colspan_val = 10)
```

<br>

```{r}
# 5
cbind(tpcigpromos_e_m_w_b$m, select(tpcigpromos_e_m_w_b$w, -agerange), select(tpcigpromos_e_m_w_b$b, -agerange)) %>% 
  final_m_w_b_tbl(.s_amount = 3, .title = "Noticed clothing or other items with a cigarette brand name or logo", .colspan_val = 10)
```

<br>

```{r}
# 6
cbind(tpcigpromos_f_m_w_b$m, select(tpcigpromos_f_m_w_b$w, -agerange), select(tpcigpromos_f_m_w_b$b, -agerange)) %>% 
  final_m_w_b_tbl(.s_amount = 3, .title = "Noticed cigarette promotions in the mail", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 1
tbl_m_u_r <- rbind(tpcigpromos_a_u_r$m_u, tpcigpromos_a_u_r$m_r)
tbl_w_u_r <- rbind(tpcigpromos_a_u_r$w_u, tpcigpromos_a_u_r$w_r)
tbl_b_u_r <- rbind(tpcigpromos_a_u_r$b_u, tpcigpromos_a_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_u_r_tbl(.s_amount = 3, .title = "Noticed free samples of cigarettes by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 2
tbl_m_u_r <- rbind(tpcigpromos_b_u_r$m_u, tpcigpromos_b_u_r$m_r)
tbl_w_u_r <- rbind(tpcigpromos_b_u_r$w_u, tpcigpromos_b_u_r$w_r)
tbl_b_u_r <- rbind(tpcigpromos_b_u_r$b_u, tpcigpromos_b_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_u_r_tbl(.s_amount = 3, .title = "Noticed sale prices on cigarettes by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 3
tbl_m_u_r <- rbind(tpcigpromos_c_u_r$m_u, tpcigpromos_c_u_r$m_r)
tbl_w_u_r <- rbind(tpcigpromos_c_u_r$w_u, tpcigpromos_c_u_r$w_r)
tbl_b_u_r <- rbind(tpcigpromos_c_u_r$b_u, tpcigpromos_c_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_u_r_tbl(.s_amount = 3, .title = "Noticed coupons for cigarettes by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 4
tbl_m_u_r <- rbind(tpcigpromos_d_u_r$m_u, tpcigpromos_d_u_r$m_r)
tbl_w_u_r <- rbind(tpcigpromos_d_u_r$w_u, tpcigpromos_d_u_r$w_r)
tbl_b_u_r <- rbind(tpcigpromos_d_u_r$b_u, tpcigpromos_d_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_u_r_tbl(.s_amount = 3, .title = "Noticed free gifts or special discount offers on other products when buying cigarettes by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 5
tbl_m_u_r <- rbind(tpcigpromos_e_u_r$m_u, tpcigpromos_e_u_r$m_r)
tbl_w_u_r <- rbind(tpcigpromos_e_u_r$w_u, tpcigpromos_e_u_r$w_r)
tbl_b_u_r <- rbind(tpcigpromos_e_u_r$b_u, tpcigpromos_e_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_u_r_tbl(.s_amount = 3, .title = "Noticed clothing or other items with a cigarette brand name or logo by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 6
tbl_m_u_r <- rbind(tpcigpromos_f_u_r$m_u, tpcigpromos_f_u_r$m_r)
tbl_w_u_r <- rbind(tpcigpromos_f_u_r$w_u, tpcigpromos_f_u_r$w_r)
tbl_b_u_r <- rbind(tpcigpromos_f_u_r$b_u, tpcigpromos_f_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_u_r_tbl(.s_amount = 3, .title = "Noticed cigarette promotions in the mail by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 1
tpcigpromos_a$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = tpcigpromos_reg_col_names) %>% 
  final_m_w_b_tbl(.s_amount = 1, .s_val = "Both sexes", .title = "Noticed free samples of cigarettes by region", .colspan_val = 4) 
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 2
tpcigpromos_b$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = tpcigpromos_reg_col_names) %>% 
  final_m_w_b_tbl(.s_amount = 1, .s_val = "Both sexes", .title = "Noticed sale prices on cigarettes by region", .colspan_val = 4) 
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 3
tpcigpromos_c$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = tpcigpromos_reg_col_names) %>% 
  final_m_w_b_tbl(.s_amount = 1, .s_val = "Both sexes", .title = "Noticed coupons for cigarettes by region", .colspan_val = 4) 
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 4
tpcigpromos_d$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = tpcigpromos_reg_col_names) %>% 
  final_m_w_b_tbl(.s_amount = 1, .s_val = "Both sexes", .title = "Noticed free gifts or special discount offers on other products when buying cigarettes by region", .colspan_val = 4) 
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 5
tpcigpromos_e$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = tpcigpromos_reg_col_names) %>% 
  final_m_w_b_tbl(.s_amount = 1, .s_val = "Both sexes", .title = "Noticed clothing or other items with a cigarette brand name or logo by region", .colspan_val = 4) 
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 6
tpcigpromos_f$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = tpcigpromos_reg_col_names) %>% 
  final_m_w_b_tbl(.s_amount = 1, .s_val = "Both sexes", .title = "Noticed cigarette promotions in the mail by region", .colspan_val = 4) 
```
<br>

**Analysis information**:

- Questions used: TP3a-TP3f
- R script name: TPcigpromos

***


**Cigarette package health warnings**

Description: Percentage of current smokers who noticed health warnings on cigarette packages during the past 30 days.

Instrument questions:

- During the past 30 days, did you notice any health warnings on cigarette packages?

```{r tpwarnings_c_tbls}
# column names to use with huxtable
tpwarnings_c_col_names <- c("Age Group (years)", "n", "%", "95% CI")
tpwarnings_c_reg_col_names <- c("Region", "n", "%", "95% CI")

# men, women, both sexes
tpwarnings_c_m_w_b <- join_m_w_b(tpwarnings_c, 1, tpwarnings_c_col_names)
```
```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# urban, rural
tpwarnings_c_u_r <- join_u_r(tpwarnings_c, 1, tpwarnings_c_col_names)
```

<br>

```{r}
cbind(tpwarnings_c_m_w_b$m, select(tpwarnings_c_m_w_b$w, -agerange), select(tpwarnings_c_m_w_b$b, -agerange)) %>% 
  final_m_w_b_tbl(.s_amount = 3, .title = "Current smokers who noticed health warnings on cigarette packages", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
tbl_m_u_r <- rbind(tpwarnings_c_u_r$m_u, tpwarnings_c_u_r$m_r)
tbl_w_u_r <- rbind(tpwarnings_c_u_r$w_u, tpwarnings_c_u_r$w_r)
tbl_b_u_r <- rbind(tpwarnings_c_u_r$b_u, tpwarnings_c_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_u_r_tbl(.s_amount = 3, .title = "Current smokers who noticed health warnings on cigarette packages by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
tpwarnings_c$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = tpwarnings_c_reg_col_names) %>% 
  final_m_w_b_tbl(1, "Both sexes", "Current smokers who noticed health warnings on cigarette packages by region", 4)
```
<br>

**Analysis information**:

- Questions used: TP4
- R script name: TPwarnings

***

**Quitting**

Description: Percentage of current smokers who noticed health warnings on cigarette packages during the past 30 days that thought about quitting due to the health warnings they saw.

Instrument questions:

- During the past 30 days, did you notice any health warnings on cigarette packages?
- During the past 30 days, have warning labels on cigarette packages led you to think about quitting?

```{r tpquitting_c_tbls}
# column names to use with huxtable
tpquitting_c_col_names <- c("Age Group (years)", "n", "%", "95% CI")
tpquitting_c_reg_col_names <- c("Region", "n", "%", "95% CI")

# men, women, both sexes
tpquitting_c_m_w_b <- join_m_w_b(tpquitting_c, 1, tpquitting_c_col_names)
```
```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# urban, rural
tpquitting_c_u_r <- join_u_r(tpquitting_c, 1, tpquitting_c_col_names)
```

<br>

```{r}
cbind(tpquitting_c_m_w_b$m, select(tpquitting_c_m_w_b$w, -agerange), select(tpquitting_c_m_w_b$b, -agerange)) %>% 
  final_m_w_b_tbl(.s_amount = 3, .title = "Current smokers who saw health warnings on cigarette packages that thought of quitting", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
tbl_m_u_r <- rbind(tpquitting_c_u_r$m_u, tpquitting_c_u_r$m_r)
tbl_w_u_r <- rbind(tpquitting_c_u_r$w_u, tpquitting_c_u_r$w_r)
tbl_b_u_r <- rbind(tpquitting_c_u_r$b_u, tpquitting_c_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_u_r_tbl(.s_amount = 3, .title = "Current smokers who saw health warnings on cigarette packages that thought of quitting by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
tpquitting_c$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = tpquitting_c_reg_col_names) %>% 
  final_m_w_b_tbl(1, "Both sexes", "Current smokers who saw health warnings on cigarette packages that thought of quitting by region", 4)
```
<br>

**Analysis information**:

- Questions used: TP4, TP5
- R script name: TPquitting

***

**Cigarette costs**

Description: Average price paid for 20 manufactured cigarettes, based on the last manufactured cigarette purchase.
Instrument questions:

- The last time you bought manufactured cigarettes for yourself, how many cigarettes did you buy in total?
- In total, how much money did you pay for this purchase?

```{r tpcost_priceper20cigs_tbls}
# column names to use with huxtable
tpcost_priceper20cigs_col_names <- c("Age Group (years)", "n", "Mean", "95% CI")
tpcost_priceper20cigs_reg_col_names <- c("Region", "n", "Mean", "95% CI")

# men, women, both sexes
tpcost_priceper20cigs_m_w_b <- join_m_w_b(tpcost_priceper20cigs, 1, tpcost_priceper20cigs_col_names)
```
```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# urban, rural
tpcost_priceper20cigs_u_r <- join_u_r(tpcost_priceper20cigs, 1, tpcost_priceper20cigs_col_names)
```

<br>

```{r}
cbind(tpcost_priceper20cigs_m_w_b$m, select(tpcost_priceper20cigs_m_w_b$w, -agerange), select(tpcost_priceper20cigs_m_w_b$b, -agerange)) %>% 
  final_m_w_b_tbl(.s_amount = 3, .title = "Average price paid for 20 manufactured cigarettes", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
tbl_m_u_r <- rbind(tpcost_priceper20cigs_u_r$m_u, tpcost_priceper20cigs_u_r$m_r)
tbl_w_u_r <- rbind(tpcost_priceper20cigs_u_r$w_u, tpcost_priceper20cigs_u_r$w_r)
tbl_b_u_r <- rbind(tpcost_priceper20cigs_u_r$b_u, tpcost_priceper20cigs_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_u_r_tbl(.s_amount = 3, .title = "Average price paid for 20 manufactured cigarettes by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
tpcost_priceper20cigs$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = tpcost_priceper20cigs_reg_col_names) %>% 
  final_m_w_b_tbl(1, "Both sexes", "Average price paid for 20 manufactured cigarettes by region", 4)
```
<br>

**Analysis information**:

- Questions used: TP6, TP7
- R script name: TPcost

***


<br>
<br>
