---
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  word_document: default
---

```{r setup, include=FALSE}
library(here)
library(huxtable)
library(tidyverse)
library(fs)
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
# Set a root directory for all chunks to be evaluated relative to rather than the document location
knitr::opts_knit$set(root.dir = here())
```

```{r source, include=FALSE}
here("DataBook", "Modules", "TobaccoUse") %>% 
  # list all R files in the directory
  fs::dir_ls(regexp = "\\.R$") %>% 
  # scale up to all R files with a map function from purrr
  map(source, encoding = "UTF-8", local = knitr::knit_global())
```

---
title: "`r set_title`"
author: "`r set_author`"
---


# Tobacco Use

**Current smoking**

Description: Current smokers among all respondents.

Instrument questions:

- Do you currently smoke any tobacco products, such as cigarettes, cigars, or pipes?

```{r tsmokestatus_d_tbls}
# prep the title
tsmokestatus_d_title <- "Percentage of current smokers"

# column names to use with huxtable
tsmokestatus_d_col_names <- c("Age Group (years)", "n", "% Current smoker", "95% CI")
tsmokestatus_d_reg_col_names <- c("Region", "n", "% Current smoker", "95% CI")

# men, women, both sexes
tsmokestatus_d_m_w_b <- join_tbls(tsmokestatus_d, m_w_b, 1, tsmokestatus_d_col_names)
```
```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# urban, rural
tsmokestatus_d_u_r <- join_tbls(tsmokestatus_d, u_r, 1, tsmokestatus_d_col_names)
```

<br>

```{r}
cbind(tsmokestatus_d_m_w_b$m, select(tsmokestatus_d_m_w_b$w, -agerange), select(tsmokestatus_d_m_w_b$b, -agerange)) %>% 
  final_tbl(.disaggregation = m_w_b, .s_amount = 3, .title = "Percentage of current smokers", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
tbl_m_u_r <- rbind(tsmokestatus_d_u_r$m_u, tsmokestatus_d_u_r$m_r)
tbl_w_u_r <- rbind(tsmokestatus_d_u_r$w_u, tsmokestatus_d_u_r$w_r)
tbl_b_u_r <- rbind(tsmokestatus_d_u_r$b_u, tsmokestatus_d_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_tbl(.disaggregation = u_r, .s_amount = 3, .title = "Percentage of current smokers by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
tsmokestatus_d$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = tsmokestatus_d_reg_col_names) %>% 
  final_tbl(.disaggregation = reg, .s_amount = 1, .s_val = "Both sexes", .title = "Percentage of current smokers by region", .colspan_val = 4) 
```
<br>

**Analysis information**:

- Questions used: T1, T2, T8
- R script name:  Tsmokestatus

***

**Smoking status**

Description: Smoking status of all respondents.

Instrument questions:

- Do you currently smoke any tobacco products, such as cigarettes, cigars, or pipes?
- Do you currently smoke tobacco products daily?
- In the past, did you ever smoke any tobacco products?

```{r tsmokestatus_c_tbls}
# prep the title
tsmokestatus_c_title <- "Smoking status"

# column names to use with huxtable
tsmokestatus_c_col_names <- c("Age Group (years)", "n", "% Daily", "95% CI", "% Non-daily", "95% CI", 
                            "% Former smoker", "95% CI", "% Never smoker", "95% CI")

# column names for region to use with huxtable
tsmokestatus_c_reg_col_names <- c("Region", "n", "% Daily", "95% CI", "% Non-daily", "95% CI", 
                                "% Former smoker", "95% CI", "% Never smoker", "95% CI")

# men, women, both sexes
tsmokestatus_c_m_w_b <- join_tbls(tsmokestatus_c, m_w_b, 4, tsmokestatus_c_col_names)
```
```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# urban, rural
tsmokestatus_c_u_r <- join_tbls(tsmokestatus_c, u_r, 4, tsmokestatus_c_col_names)
```

<br>

```{r}
tsmokestatus_c_m_w_b$m %>% final_tbl(m_w_b, 1, "Men", "Smoking status", 10)
```

<br>

```{r}
tsmokestatus_c_m_w_b$w %>% final_tbl(m_w_b, 1, "Women", "Smoking status", 10)
```

<br>

```{r}
tsmokestatus_c_m_w_b$b %>% final_tbl(m_w_b, 1, "Both sexes", "Smoking status", 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
rbind(tsmokestatus_c_u_r$m_u, tsmokestatus_c_u_r$m_r) %>% 
  final_tbl(u_r, 1, "Men", "Smoking status by type of settlement", 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
rbind(tsmokestatus_c_u_r$w_u, tsmokestatus_c_u_r$w_r) %>% 
  final_tbl(u_r, 1, "Women", "Smoking status by type of settlement", 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
rbind(tsmokestatus_c_u_r$b_u, tsmokestatus_c_u_r$b_r) %>% 
  final_tbl(u_r, 1, "Both sexes", "Smoking status by type of settlement", 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# region
tsmokestatus_c$b_reg %>% unite_ci(.ci_amount = 4) %>% apply_hux(.col_names = tsmokestatus_c_reg_col_names) %>% 
  final_tbl(reg, 1, "Both sexes", "Smoking status by region", 10) 
```
<br>

**Analysis information**:

- Questions used: T1, T2, T8
- R script name:  Tsmokestatus

***

**Daily smoking**

Description: Percentage of current daily smokers among smokers.

Instrument questions:

- Do you currently smoke any tobacco products, such as cigarettes, cigars, or pipes?
- Do you currently smoke tobacco products daily?

```{r tsmokefreq_c_tbls}

# column names to use with huxtable
tsmokefreq_c_col_names <- c("Age Group (years)", "n", "% Daily smokers", "95% CI")
tsmokefreq_c_reg_col_names <- c("Region", "n", "% Daily smokers", "95% CI")

# men, women, both sexes
tsmokefreq_c_m_w_b <- join_tbls(tsmokefreq_c, m_w_b, 1, tsmokefreq_c_col_names)
```
```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# urban, rural
tsmokefreq_c_u_r <- join_tbls(tsmokefreq_c, u_r, 1, tsmokefreq_c_col_names)
```

<br>

```{r}
cbind(tsmokefreq_c_m_w_b$m, select(tsmokefreq_c_m_w_b$w, -agerange), select(tsmokefreq_c_m_w_b$b, -agerange)) %>% 
  final_tbl(.disaggregation = m_w_b, .s_amount = 3, .title = "Current daily smokers among smokers", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
tbl_m_u_r <- rbind(tsmokefreq_c_u_r$m_u, tsmokefreq_c_u_r$m_r)
tbl_w_u_r <- rbind(tsmokefreq_c_u_r$w_u, tsmokefreq_c_u_r$w_r)
tbl_b_u_r <- rbind(tsmokefreq_c_u_r$b_u, tsmokefreq_c_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_tbl(.disaggregation = u_r, .s_amount = 3, .title = "Current daily smokers among smokers by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
tsmokefreq_c$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = tsmokefreq_c_reg_col_names) %>% 
  final_tbl(reg, 1, "Both sexes", "Current daily smokers among smokers by region", 4)
```
<br>

**Analysis information**:

- Questions used: T1, T2, T8
- R script name:  Tsmokefreq

***


**Initiation and duration  of smoking**

Description: Mean age of initiation and mean duration of smoking, in years, among daily smokers (no total age group for mean duration of smoking as age influences these values).

Instrument questions:

- Do you currently smoke any tobacco products, such as cigarettes, cigars, or pipes?
- Do you currently smoke tobacco products daily?
- How old were you when you first started smoking?
- Do you remember how long ago it was?

```{r tsmokeagetime_initiation_duration_tbls}

# column names to use with huxtable
tsmokeagetime_initiation_col_names <- c("Age Group (years)", "n", "Mean age", "95% CI")
tsmokeagetime_initiation_reg_col_names <- c("Region", "n", "Mean age", "95% CI")
tsmokeagetime_duration_col_names <- c("Age Group (years)", "n", "Mean duration", "95% CI")
tsmokeagetime_duration_reg_col_names <- c("Region", "n", "Mean duration", "95% CI")

# INITIATION PART
# men, women, both sexes
tsmokeagetime_initiation_m_w_b <- join_tbls(tsmokeagetime_initiation, m_w_b, 1, tsmokeagetime_initiation_col_names)

# DURATION PART
# men, women, both sexes
tsmokeagetime_duration_m_w_b <- join_tbls(tsmokeagetime_duration, m_w_b, 1, tsmokeagetime_duration_col_names)
```
```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# urban, rural
tsmokeagetime_initiation_u_r <- join_tbls(tsmokeagetime_initiation, u_r, 1, tsmokeagetime_initiation_col_names)
# urban, rural
tsmokeagetime_duration_u_r <- join_tbls(tsmokeagetime_duration, u_r, 1, tsmokeagetime_duration_col_names)
```

<br>

```{r}
cbind(tsmokeagetime_initiation_m_w_b$m, select(tsmokeagetime_initiation_m_w_b$w, -agerange), select(tsmokeagetime_initiation_m_w_b$b, -agerange)) %>% final_tbl(.disaggregation = m_w_b, .s_amount = 3, .title = "Mean age started smoking", .colspan_val = 10)
```

<br>

```{r}
cbind(tsmokeagetime_duration_m_w_b$m, select(tsmokeagetime_duration_m_w_b$w, -agerange), select(tsmokeagetime_duration_m_w_b$b, -agerange)) %>% final_tbl(.disaggregation = m_w_b, .s_amount = 3, .title = "Mean duration of smoking", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
tbl_m_u_r <- rbind(tsmokeagetime_initiation_u_r$m_u, tsmokeagetime_initiation_u_r$m_r)
tbl_w_u_r <- rbind(tsmokeagetime_initiation_u_r$w_u, tsmokeagetime_initiation_u_r$w_r)
tbl_b_u_r <- rbind(tsmokeagetime_initiation_u_r$b_u, tsmokeagetime_initiation_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_tbl(.disaggregation = u_r, .s_amount = 3, .title = "Mean age started smoking by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
tbl_m_u_r <- rbind(tsmokeagetime_duration_u_r$m_u, tsmokeagetime_duration_u_r$m_r)
tbl_w_u_r <- rbind(tsmokeagetime_duration_u_r$w_u, tsmokeagetime_duration_u_r$w_r)
tbl_b_u_r <- rbind(tsmokeagetime_duration_u_r$b_u, tsmokeagetime_duration_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_tbl(.disaggregation = u_r, .s_amount = 3, .title = "Mean duration of smoking by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
tsmokeagetime_initiation$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = tsmokeagetime_initiation_reg_col_names) %>% final_tbl(reg, 1, "Both sexes", "Mean age started smoking by region", 4)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
tsmokeagetime_duration$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = tsmokeagetime_duration_reg_col_names) %>% final_tbl(reg, 1, "Both sexes", "Mean duration of smoking by region", 4)
```
<br>

**Analysis information**:

- Questions used: T1, T2, T3, T4a-c
- R script name:  Tsmokeagetime

***

**Manufactured cigarette smokers**

Description: Percentage of smokers who use manufactured cigarettes among daily smokers and among current smokers.

Instrument questions:

- Do you currently smoke any tobacco products, such as cigarettes, cigars, or pipes?
- Do you currently smoke tobacco products daily?
- On average, how many of the following products do you smoke each day?

```{r tsmokeman_daily_nondaily_tbls}

# column names to use with huxtable
tsmokeman_daily_col_names <- c("Age Group (years)", "n", "Manufactured cigarette smoker", "95% CI")
tsmokeman_daily_reg_col_names <- c("Region", "n", "Manufactured cigarette smoker", "95% CI")
tsmokeman_nondaily_col_names <- c("Age Group (years)", "n", "Manufactured cigarette smoker", "95% CI")
tsmokeman_nondaily_reg_col_names <- c("Region", "n", "Manufactured cigarette smoker", "95% CI")

# DAILY PART
# men, women, both sexes
tsmokeman_daily_m_w_b <- join_tbls(tsmokeman_daily, m_w_b, 1, tsmokeman_daily_col_names)

# NONDAILY PART
# men, women, both sexes
tsmokeman_nondaily_m_w_b <- join_tbls(tsmokeman_nondaily, m_w_b, 1, tsmokeman_nondaily_col_names)
```
```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# urban, rural
tsmokeman_daily_u_r <- join_tbls(tsmokeman_daily, u_r, 1, tsmokeman_daily_col_names)
# urban, rural
tsmokeman_nondaily_u_r <- join_tbls(tsmokeman_nondaily, u_r, 1, tsmokeman_nondaily_col_names)
```

<br>

```{r}
cbind(tsmokeman_daily_m_w_b$m, select(tsmokeman_daily_m_w_b$w, -agerange), select(tsmokeman_daily_m_w_b$b, -agerange)) %>% 
  final_tbl(.disaggregation = m_w_b, .s_amount = 3, .title = "Manufactured cigarette smokers among daily smokers", .colspan_val = 10)
```

<br>

```{r}
cbind(tsmokeman_nondaily_m_w_b$m, select(tsmokeman_nondaily_m_w_b$w, -agerange), select(tsmokeman_nondaily_m_w_b$b, -agerange)) %>% 
  final_tbl(.disaggregation = m_w_b, .s_amount = 3, .title = "Manufactured cigarette smokers among current smokers", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
tbl_m_u_r <- rbind(tsmokeman_daily_u_r$m_u, tsmokeman_daily_u_r$m_r)
tbl_w_u_r <- rbind(tsmokeman_daily_u_r$w_u, tsmokeman_daily_u_r$w_r)
tbl_b_u_r <- rbind(tsmokeman_daily_u_r$b_u, tsmokeman_daily_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_tbl(.disaggregation = u_r, .s_amount = 3, .title = "Manufactured cigarette smokers among daily smokers by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
tbl_m_u_r <- rbind(tsmokeman_nondaily_u_r$m_u, tsmokeman_nondaily_u_r$m_r)
tbl_w_u_r <- rbind(tsmokeman_nondaily_u_r$w_u, tsmokeman_nondaily_u_r$w_r)
tbl_b_u_r <- rbind(tsmokeman_nondaily_u_r$b_u, tsmokeman_nondaily_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_tbl(.disaggregation = u_r, .s_amount = 3, .title = "Manufactured cigarette smokers among current smokers by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
tsmokeman_daily$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = tsmokeman_daily_reg_col_names) %>% 
  final_tbl(reg, 1, "Both sexes", "Manufactured cigarette smokers among daily smokers by region", 4)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
tsmokeman_nondaily$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = tsmokeman_nondaily_reg_col_names) %>% 
  final_tbl(reg, 1, "Both sexes", "Manufactured cigarette smokers among current smokers by region", 4)
```

<br>

**Analysis information**:

- Questions used: T1, T2, T5a, T5aw
- R script name:  Tsmokeman

***

**Amount of tobacco used among daily smokers by type**

Description: Mean amount of tobacco used by daily smokers per day, by type.

Instrument questions:

- Do you currently smoke any tobacco products, such as cigarettes, cigars, or pipes?
- Do you currently smoke tobacco products daily?
- On average, how many of the following products do you smoke each day?

```{r tsmoketype_tbls}

# column names to use with huxtable
tsmoketype_col_names <- c("Age Group (years)", "n", "Mean", "95% CI")
tsmoketype_reg_col_names <- c("Region", "n", "Mean", "95% CI")

# 1 - Mean # of manufactured cig.
# men, women, both sexes
tsmoketype_t5a_m_w_b <- join_tbls(tsmoketype_t5a, m_w_b, 1, tsmoketype_col_names)

# 2 - Mean # of hand-rolled cig.
# men, women, both sexes
tsmoketype_t5b_m_w_b <- join_tbls(tsmoketype_t5b, m_w_b, 1, tsmoketype_col_names)

# 3 - Mean # of pipes of tobacco
# men, women, both sexes
tsmoketype_t5c_m_w_b <- join_tbls(tsmoketype_t5c, m_w_b, 1, tsmoketype_col_names)

# 4 - Mean # of cigars, cheerots, cigarillos
# men, women, both sexes
tsmoketype_t5d_m_w_b <- join_tbls(tsmoketype_t5d, m_w_b, 1, tsmoketype_col_names)

# 5 - Mean # of shisha sessions
# men, women, both sexes
tsmoketype_t5e_m_w_b <- join_tbls(tsmoketype_t5e, m_w_b, 1, tsmoketype_col_names)

# 6 - Mean # of heated tobacco products
# men, women, both sexes
tsmoketype_t5f_m_w_b <- join_tbls(tsmoketype_t5f, m_w_b, 1, tsmoketype_col_names)

# 7 - Mean # of other type of tobacco
# men, women, both sexes
tsmoketype_t5g_m_w_b <- join_tbls(tsmoketype_t5g, m_w_b, 1, tsmoketype_col_names)
```
```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 1.
# urban, rural
tsmoketype_t5a_u_r <- join_tbls(tsmoketype_t5a, u_r, 1, tsmoketype_col_names)
# region
tsmoketype_t5a_b_reg <- unite_ci(tsmoketype_t5a$b_reg, .ci_amount = 1) %>% apply_hux(.col_names = tsmoketype_reg_col_names)
# 2.
# urban, rural
tsmoketype_t5b_u_r <- join_tbls(tsmoketype_t5b, u_r, 1, tsmoketype_col_names)
# region
tsmoketype_t5b_b_reg <- unite_ci(tsmoketype_t5b$b_reg, .ci_amount = 1) %>% apply_hux(.col_names = tsmoketype_reg_col_names)
# 3.
# urban, rural
tsmoketype_t5c_u_r <- join_tbls(tsmoketype_t5c, u_r, 1, tsmoketype_col_names)
# region
tsmoketype_t5c_b_reg <- unite_ci(tsmoketype_t5c$b_reg, .ci_amount = 1) %>% apply_hux(.col_names = tsmoketype_reg_col_names)
# 4.
# urban, rural
tsmoketype_t5d_u_r <- join_tbls(tsmoketype_t5d, u_r, 1, tsmoketype_col_names)
# region
tsmoketype_t5d_b_reg <- unite_ci(tsmoketype_t5d$b_reg, .ci_amount = 1) %>% apply_hux(.col_names = tsmoketype_reg_col_names)
# 5.
# urban, rural
tsmoketype_t5e_u_r <- join_tbls(tsmoketype_t5e, u_r, 1, tsmoketype_col_names)
# region
tsmoketype_t5e_b_reg <- unite_ci(tsmoketype_t5e$b_reg, .ci_amount = 1) %>% apply_hux(.col_names = tsmoketype_reg_col_names)
# 6.
# urban, rural
tsmoketype_t5f_u_r <- join_tbls(tsmoketype_t5f, u_r, 1, tsmoketype_col_names)
# region
tsmoketype_t5f_b_reg <- unite_ci(tsmoketype_t5f$b_reg, .ci_amount = 1) %>% apply_hux(.col_names = tsmoketype_reg_col_names)
# 7.
# urban, rural
tsmoketype_t5g_u_r <- join_tbls(tsmoketype_t5g, u_r, 1, tsmoketype_col_names)
# region
tsmoketype_t5g_b_reg <- unite_ci(tsmoketype_t5g$b_reg, .ci_amount = 1) %>% apply_hux(.col_names = tsmoketype_reg_col_names)
```

<br>

```{r}
cbind(tsmoketype_t5a_m_w_b$m, select(tsmoketype_t5b_m_w_b$m, -c(agerange,n)), select(tsmoketype_t5c_m_w_b$m, -c(agerange,n))) %>% 
  set_contents(1, everywhere, c("Age Group (years)", "n", "Mean # of manufactured cig.", "95% CI", 
                                "Mean # of hand-rolled cig.", "95% CI", 
                                "Mean # of pipes of tobacco", "95% CI")) %>% 
  set_right_border(row = everywhere, col = c(4,6), value = 0) %>% 
  final_tbl(m_w_b, 1, "Men", "Mean amount of tobacco used by daily smokers by type", 8)
```

<br>

```{r}
cbind(tsmoketype_t5d_m_w_b$m, select(tsmoketype_t5e_m_w_b$m, -c(agerange,n)), 
      select(tsmoketype_t5f_m_w_b$m, -c(agerange,n)), select(tsmoketype_t5g_m_w_b$m, -c(agerange,n))) %>% 
  set_contents(1, everywhere, c("Age Group (years)", "n", "Mean # of cigars, cheerots, cigarillos", "95% CI", 
                                "Mean # of shisha sessions", "95% CI", 
                                "Mean # of heated tobacco products", "95% CI",
                                "Mean # of other type of tobacco", "95% CI")) %>%
  set_right_border(row = everywhere, col = c(4,6,8), value = 0) %>% 
  final_tbl(m_w_b, 1, "Men", "Mean amount of tobacco used by daily smokers by type", 10)
```

<br>

```{r}
cbind(tsmoketype_t5a_m_w_b$w, select(tsmoketype_t5b_m_w_b$w, -c(agerange,n)), select(tsmoketype_t5c_m_w_b$w, -c(agerange,n))) %>% 
  set_contents(1, everywhere, c("Age Group (years)", "n", "Mean # of manufactured cig.", "95% CI", 
                                "Mean # of hand-rolled cig.", "95% CI", 
                                "Mean # of pipes of tobacco", "95% CI")) %>% 
  set_right_border(row = everywhere, col = c(4,6), value = 0) %>% 
  final_tbl(m_w_b, 1, "Women", "Mean amount of tobacco used by daily smokers by type", 8)
```

<br>

```{r}
cbind(tsmoketype_t5d_m_w_b$w, select(tsmoketype_t5e_m_w_b$w, -c(agerange,n)), 
      select(tsmoketype_t5f_m_w_b$w, -c(agerange,n)), select(tsmoketype_t5g_m_w_b$w, -c(agerange,n))) %>% 
  set_contents(1, everywhere, c("Age Group (years)", "n", "Mean # of cigars, cheerots, cigarillos", "95% CI", 
                                "Mean # of shisha sessions", "95% CI", 
                                "Mean # of heated tobacco products", "95% CI",
                                "Mean # of other type of tobacco", "95% CI")) %>%
  set_right_border(row = everywhere, col = c(4,6,8), value = 0) %>% 
  final_tbl(m_w_b, 1, "Women", "Mean amount of tobacco used by daily smokers by type", 10)
```

<br>

```{r}
cbind(tsmoketype_t5a_m_w_b$b, select(tsmoketype_t5b_m_w_b$b, -c(agerange,n)), select(tsmoketype_t5c_m_w_b$b, -c(agerange,n))) %>% 
  set_contents(1, everywhere, c("Age Group (years)", "n", "Mean # of manufactured cig.", "95% CI", 
                                "Mean # of hand-rolled cig.", "95% CI", 
                                "Mean # of pipes of tobacco", "95% CI")) %>% 
  set_right_border(row = everywhere, col = c(4,6), value = 0) %>% 
  final_tbl(m_w_b, 1, "Both sexes", "Mean amount of tobacco used by daily smokers by type", 8)
```

<br>

```{r}
cbind(tsmoketype_t5d_m_w_b$b, select(tsmoketype_t5e_m_w_b$b, -c(agerange,n)), 
      select(tsmoketype_t5f_m_w_b$b, -c(agerange,n)), select(tsmoketype_t5g_m_w_b$b, -c(agerange,n))) %>% 
  set_contents(1, everywhere, c("Age Group (years)", "n", "Mean # of cigars, cheerots, cigarillos", "95% CI", 
                                "Mean # of shisha sessions", "95% CI", 
                                "Mean # of heated tobacco products", "95% CI",
                                "Mean # of other type of tobacco", "95% CI")) %>%
  set_right_border(row = everywhere, col = c(4,6,8), value = 0) %>% 
  final_tbl(m_w_b, 1, "Both sexes", "Mean amount of tobacco used by daily smokers by type", 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
cbind(rbind(tsmoketype_t5a_u_r$m_u, tsmoketype_t5a_u_r$m_r), 
      select(rbind(tsmoketype_t5b_u_r$m_u, tsmoketype_t5b_u_r$m_r), -c(agerange2,n)), 
      select(rbind(tsmoketype_t5c_u_r$m_u, tsmoketype_t5c_u_r$m_r), -c(agerange2,n))) %>% 
  set_contents(1, everywhere, c("Age Group (years)", "n", "Mean # of manufactured cig.", "95% CI", 
                                "Mean # of hand-rolled cig.", "95% CI", 
                                "Mean # of pipes of tobacco", "95% CI")) %>% 
  set_right_border(row = everywhere, col = c(4,6), value = 0) %>% 
  final_tbl(u_r, 1, "Men", "Mean amount of tobacco used by daily smokers by type (and by type of settlement)", 8)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
cbind(rbind(tsmoketype_t5d_u_r$m_u, tsmoketype_t5d_u_r$m_r), 
      select(rbind(tsmoketype_t5e_u_r$m_u, tsmoketype_t5e_u_r$m_r), -c(agerange2,n)), 
      select(rbind(tsmoketype_t5f_u_r$m_u, tsmoketype_t5f_u_r$m_r), -c(agerange2,n)),
      select(rbind(tsmoketype_t5g_u_r$m_u, tsmoketype_t5g_u_r$m_r), -c(agerange2,n))) %>% 
  set_contents(1, everywhere, c("Age Group (years)", "n", "Mean # of cigars, cheerots, cigarillos", "95% CI", 
                                "Mean # of shisha sessions", "95% CI", 
                                "Mean # of heated tobacco products", "95% CI",
                                "Mean # of other type of tobacco", "95% CI")) %>%
  set_right_border(row = everywhere, col = c(4,6,8), value = 0) %>% 
  final_tbl(u_r, 1, "Men", "Mean amount of tobacco used by daily smokers by type (and by type of settlement)", 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
cbind(rbind(tsmoketype_t5a_u_r$w_u, tsmoketype_t5a_u_r$w_r), 
      select(rbind(tsmoketype_t5b_u_r$w_u, tsmoketype_t5b_u_r$w_r), -c(agerange2,n)), 
      select(rbind(tsmoketype_t5c_u_r$w_u, tsmoketype_t5c_u_r$w_r), -c(agerange2,n))) %>% 
  set_contents(1, everywhere, c("Age Group (years)", "n", "Mean # of manufactured cig.", "95% CI", 
                                "Mean # of hand-rolled cig.", "95% CI", 
                                "Mean # of pipes of tobacco", "95% CI")) %>% 
  set_right_border(row = everywhere, col = c(4,6), value = 0) %>% 
  final_tbl(u_r, 1, "Women", "Mean amount of tobacco used by daily smokers by type (and by type of settlement)", 8)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
cbind(rbind(tsmoketype_t5d_u_r$w_u, tsmoketype_t5d_u_r$w_r), 
      select(rbind(tsmoketype_t5e_u_r$w_u, tsmoketype_t5e_u_r$w_r), -c(agerange2,n)), 
      select(rbind(tsmoketype_t5f_u_r$w_u, tsmoketype_t5f_u_r$w_r), -c(agerange2,n)),
      select(rbind(tsmoketype_t5g_u_r$w_u, tsmoketype_t5g_u_r$w_r), -c(agerange2,n))) %>% 
  set_contents(1, everywhere, c("Age Group (years)", "n", "Mean # of cigars, cheerots, cigarillos", "95% CI", 
                                "Mean # of shisha sessions", "95% CI", 
                                "Mean # of heated tobacco products", "95% CI",
                                "Mean # of other type of tobacco", "95% CI")) %>%
  set_right_border(row = everywhere, col = c(4,6,8), value = 0) %>% 
  final_tbl(u_r, 1, "Women", "Mean amount of tobacco used by daily smokers by type (and by type of settlement)", 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
cbind(rbind(tsmoketype_t5a_u_r$b_u, tsmoketype_t5a_u_r$b_r), 
      select(rbind(tsmoketype_t5b_u_r$b_u, tsmoketype_t5b_u_r$b_r), -c(agerange2,n)), 
      select(rbind(tsmoketype_t5c_u_r$b_u, tsmoketype_t5c_u_r$b_r), -c(agerange2,n))) %>% 
  set_contents(1, everywhere, c("Age Group (years)", "n", "Mean # of manufactured cig.", "95% CI", 
                                "Mean # of hand-rolled cig.", "95% CI", 
                                "Mean # of pipes of tobacco", "95% CI")) %>% 
  set_right_border(row = everywhere, col = c(4,6), value = 0) %>% 
  final_tbl(u_r, 1, "Both sexes", "Mean amount of tobacco used by daily smokers by type (and by type of settlement)", 8)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
cbind(rbind(tsmoketype_t5d_u_r$b_u, tsmoketype_t5d_u_r$b_r), 
      select(rbind(tsmoketype_t5e_u_r$b_u, tsmoketype_t5e_u_r$b_r), -c(agerange2,n)), 
      select(rbind(tsmoketype_t5f_u_r$b_u, tsmoketype_t5f_u_r$b_r), -c(agerange2,n)),
      select(rbind(tsmoketype_t5g_u_r$b_u, tsmoketype_t5g_u_r$b_r), -c(agerange2,n))) %>% 
  set_contents(1, everywhere, c("Age Group (years)", "n", "Mean # of cigars, cheerots, cigarillos", "95% CI", 
                                "Mean # of shisha sessions", "95% CI", 
                                "Mean # of heated tobacco products", "95% CI",
                                "Mean # of other type of tobacco", "95% CI")) %>%
  set_right_border(row = everywhere, col = c(4,6,8), value = 0) %>% 
  final_tbl(u_r, 1, "Both sexes", "Mean amount of tobacco used by daily smokers by type (and by type of settlement)", 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
cbind(tsmoketype_t5a_b_reg, 
      select(tsmoketype_t5b_b_reg, -c(region,n)), 
      select(tsmoketype_t5c_b_reg, -c(region,n))) %>%
  set_contents(1, everywhere, c("Region", "n", "Mean # of manufactured cig.", "95% CI", 
                                "Mean # of hand-rolled cig.", "95% CI", 
                                "Mean # of pipes of tobacco", "95% CI")) %>% 
  set_right_border(row = everywhere, col = c(4,6), value = 0) %>% 
  final_tbl(reg, 1, "Both sexes", "Mean amount of tobacco used by daily smokers by type (and by region)", 8)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
cbind(tsmoketype_t5d_b_reg, 
      select(tsmoketype_t5e_b_reg, -c(region,n)), 
      select(tsmoketype_t5f_b_reg, -c(region,n)),
      select(tsmoketype_t5g_b_reg, -c(region,n))) %>% 
  set_contents(1, everywhere, c("Region", "n", "Mean # of cigars, cheerots, cigarillos", "95% CI", 
                                "Mean # of shisha sessions", "95% CI", 
                                "Mean # of heated tobacco products", "95% CI",
                                "Mean # of other type of tobacco", "95% CI")) %>%
  set_right_border(row = everywhere, col = c(4,6,8), value = 0) %>% 
  final_tbl(reg, 1, "Both sexes", "Mean amount of tobacco used by daily smokers by type (and by region)", 10)
```

<br>

**Analysis information**:

- Questions used: T1, T2, T5a-T5f
- R script name:  Tsmoketype

***

**Smoked tobacco consumption**

Description: Percentage of current smokers who smoke each of the following products.

Instrument questions:

- Do you currently smoke any tobacco products, such as cigarettes, cigars, or pipes?
- Do you currently smoke tobacco products daily?
- On average, how many of the following products do you smoke each day/week?

```{r tsmoketypeprev_nondaily_tbls}

# column names to use with huxtable
tsmoketypeprev_nondaily_col_names <- c("Age Group (years)", "n", "%", "95% CI")
tsmoketypeprev_nondaily_reg_col_names <- c("Region", "n", "%", "95% CI")

# 1 - Mean # of manufactured cig.
# men, women, both sexes
tsmoketypeprev_nondaily_t5a_m_w_b <- join_tbls(tsmoketypeprev_nondaily_t5a, m_w_b, 1, tsmoketypeprev_nondaily_col_names)

# 2 - Mean # of hand-rolled cig.
# men, women, both sexes
tsmoketypeprev_nondaily_t5b_m_w_b <- join_tbls(tsmoketypeprev_nondaily_t5b, m_w_b, 1, tsmoketypeprev_nondaily_col_names)

# 3 - Mean # of pipes of tobacco
# men, women, both sexes
tsmoketypeprev_nondaily_t5c_m_w_b <- join_tbls(tsmoketypeprev_nondaily_t5c, m_w_b, 1, tsmoketypeprev_nondaily_col_names)

# 4 - Mean # of cigars, cheerots, cigarillos
# men, women, both sexes
tsmoketypeprev_nondaily_t5d_m_w_b <- join_tbls(tsmoketypeprev_nondaily_t5d, m_w_b, 1, tsmoketypeprev_nondaily_col_names)

# 5 - Mean # of shisha sessions
# men, women, both sexes
tsmoketypeprev_nondaily_t5e_m_w_b <- join_tbls(tsmoketypeprev_nondaily_t5e, m_w_b, 1, tsmoketypeprev_nondaily_col_names)

# 6 - Mean # of heated tobacco products
# men, women, both sexes
tsmoketypeprev_nondaily_t5f_m_w_b <- join_tbls(tsmoketypeprev_nondaily_t5f, m_w_b, 1, tsmoketypeprev_nondaily_col_names)

# 7 - Mean # of other type of tobacco
# men, women, both sexes
tsmoketypeprev_nondaily_t5g_m_w_b <- join_tbls(tsmoketypeprev_nondaily_t5g, m_w_b, 1, tsmoketypeprev_nondaily_col_names)
```
```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 1.
# urban, rural
tsmoketypeprev_nondaily_t5a_u_r <- join_tbls(tsmoketypeprev_nondaily_t5a, u_r, 1, tsmoketypeprev_nondaily_col_names)
# region
tsmoketypeprev_nondaily_t5a_b_reg <- unite_ci(tsmoketypeprev_nondaily_t5a$b_reg, .ci_amount = 1) %>% apply_hux(.col_names = tsmoketypeprev_nondaily_reg_col_names)
# 2.
# urban, rural
tsmoketypeprev_nondaily_t5b_u_r <- join_tbls(tsmoketypeprev_nondaily_t5b, u_r, 1, tsmoketypeprev_nondaily_col_names)
# region
tsmoketypeprev_nondaily_t5b_b_reg <- unite_ci(tsmoketypeprev_nondaily_t5b$b_reg, .ci_amount = 1) %>% apply_hux(.col_names = tsmoketypeprev_nondaily_reg_col_names)
# 3.
# urban, rural
tsmoketypeprev_nondaily_t5c_u_r <- join_tbls(tsmoketypeprev_nondaily_t5c, u_r, 1, tsmoketypeprev_nondaily_col_names)
# region
tsmoketypeprev_nondaily_t5c_b_reg <- unite_ci(tsmoketypeprev_nondaily_t5c$b_reg, .ci_amount = 1) %>% apply_hux(.col_names = tsmoketypeprev_nondaily_reg_col_names)
# 4.
# urban, rural
tsmoketypeprev_nondaily_t5d_u_r <- join_tbls(tsmoketypeprev_nondaily_t5d, u_r, 1, tsmoketypeprev_nondaily_col_names)
# region
tsmoketypeprev_nondaily_t5d_b_reg <- unite_ci(tsmoketypeprev_nondaily_t5d$b_reg, .ci_amount = 1) %>% apply_hux(.col_names = tsmoketypeprev_nondaily_reg_col_names)
# 5.
# urban, rural
tsmoketypeprev_nondaily_t5e_u_r <- join_tbls(tsmoketypeprev_nondaily_t5e, u_r, 1, tsmoketypeprev_nondaily_col_names)
# region
tsmoketypeprev_nondaily_t5e_b_reg <- unite_ci(tsmoketypeprev_nondaily_t5e$b_reg, .ci_amount = 1) %>% apply_hux(.col_names = tsmoketypeprev_nondaily_reg_col_names)
# 6.
# urban, rural
tsmoketypeprev_nondaily_t5f_u_r <- join_tbls(tsmoketypeprev_nondaily_t5f, u_r, 1, tsmoketypeprev_nondaily_col_names)
# region
tsmoketypeprev_nondaily_t5f_b_reg <- unite_ci(tsmoketypeprev_nondaily_t5f$b_reg, .ci_amount = 1) %>% apply_hux(.col_names = tsmoketypeprev_nondaily_reg_col_names)
# 7.
# urban, rural
tsmoketypeprev_nondaily_t5g_u_r <- join_tbls(tsmoketypeprev_nondaily_t5g, u_r, 1, tsmoketypeprev_nondaily_col_names)
# region
tsmoketypeprev_nondaily_t5g_b_reg <- unite_ci(tsmoketypeprev_nondaily_t5g$b_reg, .ci_amount = 1) %>% apply_hux(.col_names = tsmoketypeprev_nondaily_reg_col_names)
```

<br>

```{r}
cbind(tsmoketypeprev_nondaily_t5a_m_w_b$m, 
      select(tsmoketypeprev_nondaily_t5b_m_w_b$m, -c(agerange,n_sum)), 
      select(tsmoketypeprev_nondaily_t5c_m_w_b$m, -c(agerange,n_sum))) %>% 
  set_contents(1, everywhere, c("Age Group (years)", "n", "% manufactured cig.", "95% CI", 
                                "% hand-rolled cig.", "95% CI", 
                                "% pipes of tobacco", "95% CI")) %>% 
  set_right_border(row = everywhere, col = c(4,6), value = 0) %>% 
  final_tbl(m_w_b, 1, "Men", "Percentage of current smokers smoking each of the following products", 8)
```

<br>

```{r}
cbind(tsmoketypeprev_nondaily_t5d_m_w_b$m, 
      select(tsmoketypeprev_nondaily_t5e_m_w_b$m, -c(agerange,n_sum)), 
      select(tsmoketypeprev_nondaily_t5f_m_w_b$m, -c(agerange,n_sum)), 
      select(tsmoketypeprev_nondaily_t5g_m_w_b$m, -c(agerange,n_sum))) %>% 
  set_contents(1, everywhere, c("Age Group (years)", "n", "% cigars, cheerots, cigarillos", "95% CI", 
                                "% shisha sessions", "95% CI", 
                                "% heated tobacco products", "95% CI",
                                "% other type of tobacco", "95% CI")) %>%
  set_right_border(row = everywhere, col = c(4,6,8), value = 0) %>% 
  final_tbl(m_w_b, 1, "Men", "Percentage of current smokers smoking each of the following products", 10)
```

<br>

```{r}
cbind(tsmoketypeprev_nondaily_t5a_m_w_b$w, select(tsmoketypeprev_nondaily_t5b_m_w_b$w, -c(agerange,n_sum)), select(tsmoketypeprev_nondaily_t5c_m_w_b$w, -c(agerange,n_sum))) %>% 
  set_contents(1, everywhere, c("Age Group (years)", "n", "% manufactured cig.", "95% CI", 
                                "% hand-rolled cig.", "95% CI", 
                                "% pipes of tobacco", "95% CI")) %>% 
  set_right_border(row = everywhere, col = c(4,6), value = 0) %>% 
  final_tbl(m_w_b, 1, "Women", "Percentage of current smokers smoking each of the following products", 8)
```

<br>

```{r}
cbind(tsmoketypeprev_nondaily_t5d_m_w_b$w, 
      select(tsmoketypeprev_nondaily_t5e_m_w_b$w, -c(agerange,n_sum)), 
      select(tsmoketypeprev_nondaily_t5f_m_w_b$w, -c(agerange,n_sum)), 
      select(tsmoketypeprev_nondaily_t5g_m_w_b$w, -c(agerange,n_sum))) %>% 
  set_contents(1, everywhere, c("Age Group (years)", "n", "% cigars, cheerots, cigarillos", "95% CI", 
                                "% shisha sessions", "95% CI", 
                                "% heated tobacco products", "95% CI",
                                "% other type of tobacco", "95% CI")) %>%
  set_right_border(row = everywhere, col = c(4,6,8), value = 0) %>% 
  final_tbl(m_w_b, 1, "Women", "Percentage of current smokers smoking each of the following products", 10)
```

<br>

```{r}
cbind(tsmoketypeprev_nondaily_t5a_m_w_b$b, 
      select(tsmoketypeprev_nondaily_t5b_m_w_b$b, -c(agerange,n_sum)), 
      select(tsmoketypeprev_nondaily_t5c_m_w_b$b, -c(agerange,n_sum))) %>% 
  set_contents(1, everywhere, c("Age Group (years)", "n", "% manufactured cig.", "95% CI", 
                                "% hand-rolled cig.", "95% CI", 
                                "% pipes of tobacco", "95% CI")) %>% 
  set_right_border(row = everywhere, col = c(4,6), value = 0) %>% 
  final_tbl(m_w_b, 1, "Both sexes", "Percentage of current smokers smoking each of the following products", 8)
```

<br>

```{r}
cbind(tsmoketypeprev_nondaily_t5d_m_w_b$b, 
      select(tsmoketypeprev_nondaily_t5e_m_w_b$b, -c(agerange,n_sum)), 
      select(tsmoketypeprev_nondaily_t5f_m_w_b$b, -c(agerange,n_sum)), 
      select(tsmoketypeprev_nondaily_t5g_m_w_b$b, -c(agerange,n_sum))) %>% 
  set_contents(1, everywhere, c("Age Group (years)", "n", "% cigars, cheerots, cigarillos", "95% CI", 
                                "% shisha sessions", "95% CI", 
                                "% heated tobacco products", "95% CI",
                                "% other type of tobacco", "95% CI")) %>%
  set_right_border(row = everywhere, col = c(4,6,8), value = 0) %>% 
  final_tbl(m_w_b, 1, "Both sexes", "Percentage of current smokers smoking each of the following products", 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
cbind(rbind(tsmoketypeprev_nondaily_t5a_u_r$m_u, tsmoketypeprev_nondaily_t5a_u_r$m_r), 
      select(rbind(tsmoketypeprev_nondaily_t5b_u_r$m_u, tsmoketypeprev_nondaily_t5b_u_r$m_r), -c(agerange2,n_sum)), 
      select(rbind(tsmoketypeprev_nondaily_t5c_u_r$m_u, tsmoketypeprev_nondaily_t5c_u_r$m_r), -c(agerange2,n_sum))) %>% 
  set_contents(1, everywhere, c("Age Group (years)", "n", "% manufactured cig.", "95% CI", 
                                "% hand-rolled cig.", "95% CI", 
                                "% pipes of tobacco", "95% CI")) %>% 
  set_right_border(row = everywhere, col = c(4,6), value = 0) %>% 
  final_tbl(u_r, 1, "Men", "Percentage of current smokers smoking each of the following products by type of settlement", 8)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
cbind(rbind(tsmoketypeprev_nondaily_t5d_u_r$m_u, tsmoketypeprev_nondaily_t5d_u_r$m_r), 
      select(rbind(tsmoketypeprev_nondaily_t5e_u_r$m_u, tsmoketypeprev_nondaily_t5e_u_r$m_r), -c(agerange2,n_sum)), 
      select(rbind(tsmoketypeprev_nondaily_t5f_u_r$m_u, tsmoketypeprev_nondaily_t5f_u_r$m_r), -c(agerange2,n_sum)),
      select(rbind(tsmoketypeprev_nondaily_t5g_u_r$m_u, tsmoketypeprev_nondaily_t5g_u_r$m_r), -c(agerange2,n_sum))) %>% 
  set_contents(1, everywhere, c("Age Group (years)", "n", "% cigars, cheerots, cigarillos", "95% CI", 
                                "% shisha sessions", "95% CI", 
                                "% heated tobacco products", "95% CI",
                                "% other type of tobacco", "95% CI")) %>%
  set_right_border(row = everywhere, col = c(4,6,8), value = 0) %>% 
  final_tbl(u_r, 1, "Men", "Percentage of current smokers smoking each of the following products by type of settlement", 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
cbind(rbind(tsmoketypeprev_nondaily_t5a_u_r$w_u, tsmoketypeprev_nondaily_t5a_u_r$w_r), 
      select(rbind(tsmoketypeprev_nondaily_t5b_u_r$w_u, tsmoketypeprev_nondaily_t5b_u_r$w_r), -c(agerange2,n_sum)), 
      select(rbind(tsmoketypeprev_nondaily_t5c_u_r$w_u, tsmoketypeprev_nondaily_t5c_u_r$w_r), -c(agerange2,n_sum))) %>% 
  set_contents(1, everywhere, c("Age Group (years)", "n", "% manufactured cig.", "95% CI", 
                                "% hand-rolled cig.", "95% CI", 
                                "% pipes of tobacco", "95% CI")) %>% 
  set_right_border(row = everywhere, col = c(4,6), value = 0) %>% 
  final_tbl(u_r, 1, "Women", "Percentage of current smokers smoking each of the following products by type of settlement", 8)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
cbind(rbind(tsmoketypeprev_nondaily_t5d_u_r$w_u, tsmoketypeprev_nondaily_t5d_u_r$w_r), 
      select(rbind(tsmoketypeprev_nondaily_t5e_u_r$w_u, tsmoketypeprev_nondaily_t5e_u_r$w_r), -c(agerange2,n_sum)), 
      select(rbind(tsmoketypeprev_nondaily_t5f_u_r$w_u, tsmoketypeprev_nondaily_t5f_u_r$w_r), -c(agerange2,n_sum)),
      select(rbind(tsmoketypeprev_nondaily_t5g_u_r$w_u, tsmoketypeprev_nondaily_t5g_u_r$w_r), -c(agerange2,n_sum))) %>% 
  set_contents(1, everywhere, c("Age Group (years)", "n", "% cigars, cheerots, cigarillos", "95% CI", 
                                "% shisha sessions", "95% CI", 
                                "% heated tobacco products", "95% CI",
                                "% other type of tobacco", "95% CI")) %>%
  set_right_border(row = everywhere, col = c(4,6,8), value = 0) %>% 
  final_tbl(u_r, 1, "Women", "Percentage of current smokers smoking each of the following products by type of settlement", 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
cbind(rbind(tsmoketypeprev_nondaily_t5a_u_r$b_u, tsmoketypeprev_nondaily_t5a_u_r$b_r), 
      select(rbind(tsmoketypeprev_nondaily_t5b_u_r$b_u, tsmoketypeprev_nondaily_t5b_u_r$b_r), -c(agerange2,n_sum)), 
      select(rbind(tsmoketypeprev_nondaily_t5c_u_r$b_u, tsmoketypeprev_nondaily_t5c_u_r$b_r), -c(agerange2,n_sum))) %>% 
  set_contents(1, everywhere, c("Age Group (years)", "n", "% manufactured cig.", "95% CI", 
                                "% hand-rolled cig.", "95% CI", 
                                "% pipes of tobacco", "95% CI")) %>% 
  set_right_border(row = everywhere, col = c(4,6), value = 0) %>% 
  final_tbl(u_r, 1, "Both sexes", "Percentage of current smokers smoking each of the following products by type of settlement", 8)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
cbind(rbind(tsmoketypeprev_nondaily_t5d_u_r$b_u, tsmoketypeprev_nondaily_t5d_u_r$b_r), 
      select(rbind(tsmoketypeprev_nondaily_t5e_u_r$b_u, tsmoketypeprev_nondaily_t5e_u_r$b_r), -c(agerange2,n_sum)), 
      select(rbind(tsmoketypeprev_nondaily_t5f_u_r$b_u, tsmoketypeprev_nondaily_t5f_u_r$b_r), -c(agerange2,n_sum)),
      select(rbind(tsmoketypeprev_nondaily_t5g_u_r$b_u, tsmoketypeprev_nondaily_t5g_u_r$b_r), -c(agerange2,n_sum))) %>% 
  set_contents(1, everywhere, c("Age Group (years)", "n", "% cigars, cheerots, cigarillos", "95% CI", 
                                "% shisha sessions", "95% CI", 
                                "% heated tobacco products", "95% CI",
                                "% other type of tobacco", "95% CI")) %>%
  set_right_border(row = everywhere, col = c(4,6,8), value = 0) %>% 
  final_tbl(u_r, 1, "Both sexes", "Percentage of current smokers smoking each of the following products by type of settlement", 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
cbind(tsmoketypeprev_nondaily_t5a_b_reg, 
      select(tsmoketypeprev_nondaily_t5b_b_reg, -c(region,n_sum)), 
      select(tsmoketypeprev_nondaily_t5c_b_reg, -c(region,n_sum))) %>%
  set_contents(1, everywhere, c("Region", "n", "% manufactured cig.", "95% CI", 
                                "% hand-rolled cig.", "95% CI", 
                                "% pipes of tobacco", "95% CI")) %>% 
  set_right_border(row = everywhere, col = c(4,6), value = 0) %>% 
  final_tbl(reg, 1, "Both sexes", "Percentage of current smokers smoking each of the following products by region", 8)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
cbind(tsmoketypeprev_nondaily_t5d_b_reg, 
      select(tsmoketypeprev_nondaily_t5e_b_reg, -c(region,n_sum)), 
      select(tsmoketypeprev_nondaily_t5f_b_reg, -c(region,n_sum)),
      select(tsmoketypeprev_nondaily_t5g_b_reg, -c(region,n_sum))) %>% 
  set_contents(1, everywhere, c("Region", "n", "% cigars, cheerots, cigarillos", "95% CI", 
                                "% shisha sessions", "95% CI", 
                                "% heated tobacco products", "95% CI",
                                "% other type of tobacco", "95% CI")) %>%
  set_right_border(row = everywhere, col = c(4,6,8), value = 0) %>% 
  final_tbl(reg, 1, "Both sexes", "Percentage of current smokers smoking each of the following products by region", 10)
```

<br>

**Analysis information**:

- Questions used: T1, T2, T5a-T5fw
- R script name:  Tsmoketypeprev

***

**Daily smoked tobacco consumption**

Description: Proportion of population who smoke each of the following products **daily**.

Instrument questions:

- Do you currently smoke any tobacco products, such as cigarettes, cigars, or pipes?
- Do you currently smoke tobacco products daily?
- On average, how many of the following products do you smoke each day?

```{r tsmoketypeprev_daily_tbls}

# column names to use with huxtable
tsmoketypeprev_daily_col_names <- c("Age Group (years)", "n", "%", "95% CI")
tsmoketypeprev_daily_reg_col_names <- c("Region", "n", "%", "95% CI")

# 1 - Mean # of manufactured cig.
# men, women, both sexes
tsmoketypeprev_daily_t5a_m_w_b <- join_tbls(tsmoketypeprev_daily_t5a, m_w_b, 1, tsmoketypeprev_daily_col_names)

# 2 - Mean # of hand-rolled cig.
# men, women, both sexes
tsmoketypeprev_daily_t5b_m_w_b <- join_tbls(tsmoketypeprev_daily_t5b, m_w_b, 1, tsmoketypeprev_daily_col_names)

# 3 - Mean # of pipes of tobacco
# men, women, both sexes
tsmoketypeprev_daily_t5c_m_w_b <- join_tbls(tsmoketypeprev_daily_t5c, m_w_b, 1, tsmoketypeprev_daily_col_names)

# 4 - Mean # of cigars, cheerots, cigarillos
# men, women, both sexes
tsmoketypeprev_daily_t5d_m_w_b <- join_tbls(tsmoketypeprev_daily_t5d, m_w_b, 1, tsmoketypeprev_daily_col_names)

# 5 - Mean # of shisha sessions
# men, women, both sexes
tsmoketypeprev_daily_t5e_m_w_b <- join_tbls(tsmoketypeprev_daily_t5e, m_w_b, 1, tsmoketypeprev_daily_col_names)

# 6 - Mean # of heated tobacco products
# men, women, both sexes
tsmoketypeprev_daily_t5f_m_w_b <- join_tbls(tsmoketypeprev_daily_t5f, m_w_b, 1, tsmoketypeprev_daily_col_names)

# 7 - Mean # of other type of tobacco
# men, women, both sexes
tsmoketypeprev_daily_t5g_m_w_b <- join_tbls(tsmoketypeprev_daily_t5g, m_w_b, 1, tsmoketypeprev_daily_col_names)
```
```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 1.
# urban, rural
tsmoketypeprev_daily_t5a_u_r <- join_tbls(tsmoketypeprev_daily_t5a, u_r, 1, tsmoketypeprev_daily_col_names)
# region
tsmoketypeprev_daily_t5a_b_reg <- unite_ci(tsmoketypeprev_daily_t5a$b_reg, .ci_amount = 1) %>% apply_hux(.col_names = tsmoketypeprev_daily_reg_col_names)
# 2.
# urban, rural
tsmoketypeprev_daily_t5b_u_r <- join_tbls(tsmoketypeprev_daily_t5b, u_r, 1, tsmoketypeprev_daily_col_names)
# region
tsmoketypeprev_daily_t5b_b_reg <- unite_ci(tsmoketypeprev_daily_t5b$b_reg, .ci_amount = 1) %>% apply_hux(.col_names = tsmoketypeprev_daily_reg_col_names)
# 3.
# urban, rural
tsmoketypeprev_daily_t5c_u_r <- join_tbls(tsmoketypeprev_daily_t5c, u_r, 1, tsmoketypeprev_daily_col_names)
# region
tsmoketypeprev_daily_t5c_b_reg <- unite_ci(tsmoketypeprev_daily_t5c$b_reg, .ci_amount = 1) %>% apply_hux(.col_names = tsmoketypeprev_daily_reg_col_names)
# 4.
# urban, rural
tsmoketypeprev_daily_t5d_u_r <- join_tbls(tsmoketypeprev_daily_t5d, u_r, 1, tsmoketypeprev_daily_col_names)
# region
tsmoketypeprev_daily_t5d_b_reg <- unite_ci(tsmoketypeprev_daily_t5d$b_reg, .ci_amount = 1) %>% apply_hux(.col_names = tsmoketypeprev_daily_reg_col_names)
# 5 .
# urban, rural
tsmoketypeprev_daily_t5e_u_r <- join_tbls(tsmoketypeprev_daily_t5e, u_r, 1, tsmoketypeprev_daily_col_names)
# region
tsmoketypeprev_daily_t5e_b_reg <- unite_ci(tsmoketypeprev_daily_t5e$b_reg, .ci_amount = 1) %>% apply_hux(.col_names = tsmoketypeprev_daily_reg_col_names)
# 6.
# urban, rural
tsmoketypeprev_daily_t5f_u_r <- join_tbls(tsmoketypeprev_daily_t5f, u_r, 1, tsmoketypeprev_daily_col_names)
# region
tsmoketypeprev_daily_t5f_b_reg <- unite_ci(tsmoketypeprev_daily_t5f$b_reg, .ci_amount = 1) %>% apply_hux(.col_names = tsmoketypeprev_daily_reg_col_names)
# 7.
# urban, rural
tsmoketypeprev_daily_t5g_u_r <- join_tbls(tsmoketypeprev_daily_t5g, u_r, 1, tsmoketypeprev_daily_col_names)
# region
tsmoketypeprev_daily_t5g_b_reg <- unite_ci(tsmoketypeprev_daily_t5g$b_reg, .ci_amount = 1) %>% apply_hux(.col_names = tsmoketypeprev_daily_reg_col_names)
```

<br>

```{r}
cbind(tsmoketypeprev_daily_t5a_m_w_b$m, select(tsmoketypeprev_daily_t5b_m_w_b$m, -c(agerange,n_sum)), select(tsmoketypeprev_daily_t5c_m_w_b$m, -c(agerange,n_sum))) %>% 
  set_contents(1, everywhere, c("Age Group (years)", "n", "% manufactured cig.", "95% CI", 
                                "% hand-rolled cig.", "95% CI", 
                                "% pipes of tobacco", "95% CI")) %>% 
  set_right_border(row = everywhere, col = c(4,6), value = 0) %>% 
  final_tbl(m_w_b, 1, "Men", "Proportion of population who smoke each of the following products daily", 8)
```

<br>

```{r}
cbind(tsmoketypeprev_daily_t5d_m_w_b$m, select(tsmoketypeprev_daily_t5e_m_w_b$m, -c(agerange,n_sum)), 
      select(tsmoketypeprev_daily_t5f_m_w_b$m, -c(agerange,n_sum)), 
      select(tsmoketypeprev_daily_t5g_m_w_b$m, -c(agerange,n_sum))) %>% 
  set_contents(1, everywhere, c("Age Group (years)", "n", "% cigars, cheerots, cigarillos", "95% CI", 
                                "% shisha sessions", "95% CI", 
                                "% heated tobacco products", "95% CI",
                                "% other type of tobacco", "95% CI")) %>%
  set_right_border(row = everywhere, col = c(4,6,8), value = 0) %>% 
  final_tbl(m_w_b, 1, "Men", "Proportion of population who smoke each of the following products daily", 10)
```

<br>

```{r}
cbind(tsmoketypeprev_daily_t5a_m_w_b$w, select(tsmoketypeprev_daily_t5b_m_w_b$w, -c(agerange,n_sum)), select(tsmoketypeprev_daily_t5c_m_w_b$w, -c(agerange,n_sum))) %>% 
  set_contents(1, everywhere, c("Age Group (years)", "n", "% manufactured cig.", "95% CI", 
                                "% hand-rolled cig.", "95% CI", 
                                "% pipes of tobacco", "95% CI")) %>% 
  set_right_border(row = everywhere, col = c(4,6), value = 0) %>% 
  final_tbl(m_w_b, 1, "Women", "Proportion of population who smoke each of the following products daily", 8)
```

<br>

```{r}
cbind(tsmoketypeprev_daily_t5d_m_w_b$w, select(tsmoketypeprev_daily_t5e_m_w_b$w, -c(agerange,n_sum)), 
      select(tsmoketypeprev_daily_t5f_m_w_b$w, -c(agerange,n_sum)), 
      select(tsmoketypeprev_daily_t5g_m_w_b$w, -c(agerange,n_sum))) %>% 
  set_contents(1, everywhere, c("Age Group (years)", "n", "% cigars, cheerots, cigarillos", "95% CI", 
                                "% shisha sessions", "95% CI", 
                                "% heated tobacco products", "95% CI",
                                "% other type of tobacco", "95% CI")) %>%
  set_right_border(row = everywhere, col = c(4,6,8), value = 0) %>% 
  final_tbl(m_w_b, 1, "Women", "Proportion of population who smoke each of the following products daily", 10)
```

<br>

```{r}
cbind(tsmoketypeprev_daily_t5a_m_w_b$b, select(tsmoketypeprev_daily_t5b_m_w_b$b, -c(agerange,n_sum)), select(tsmoketypeprev_daily_t5c_m_w_b$b, -c(agerange,n_sum))) %>% 
  set_contents(1, everywhere, c("Age Group (years)", "n", "% manufactured cig.", "95% CI", 
                                "% hand-rolled cig.", "95% CI", 
                                "% pipes of tobacco", "95% CI")) %>% 
  set_right_border(row = everywhere, col = c(4,6), value = 0) %>% 
  final_tbl(m_w_b, 1, "Both sexes", "Proportion of population who smoke each of the following products daily", 8)
```

<br>

```{r}
cbind(tsmoketypeprev_daily_t5d_m_w_b$b, select(tsmoketypeprev_daily_t5e_m_w_b$b, -c(agerange,n_sum)), 
      select(tsmoketypeprev_daily_t5f_m_w_b$b, -c(agerange,n_sum)), 
      select(tsmoketypeprev_daily_t5g_m_w_b$b, -c(agerange,n_sum))) %>% 
  set_contents(1, everywhere, c("Age Group (years)", "n", "% cigars, cheerots, cigarillos", "95% CI", 
                                "% shisha sessions", "95% CI", 
                                "% heated tobacco products", "95% CI",
                                "% other type of tobacco", "95% CI")) %>%
  set_right_border(row = everywhere, col = c(4,6,8), value = 0) %>% 
  final_tbl(m_w_b, 1, "Both sexes", "Proportion of population who smoke each of the following products daily", 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
cbind(rbind(tsmoketypeprev_daily_t5a_u_r$m_u, tsmoketypeprev_daily_t5a_u_r$m_r), 
      select(rbind(tsmoketypeprev_daily_t5b_u_r$m_u, tsmoketypeprev_daily_t5b_u_r$m_r), -c(agerange2,n_sum)), 
      select(rbind(tsmoketypeprev_daily_t5c_u_r$m_u, tsmoketypeprev_daily_t5c_u_r$m_r), -c(agerange2,n_sum))) %>% 
  set_contents(1, everywhere, c("Age Group (years)", "n", "% manufactured cig.", "95% CI", 
                                "% hand-rolled cig.", "95% CI", 
                                "% pipes of tobacco", "95% CI")) %>% 
  set_right_border(row = everywhere, col = c(4,6), value = 0) %>% 
  final_tbl(u_r, 1, "Men", "Proportion of population who smoke each of the following products daily by type of settlement", 8)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
cbind(rbind(tsmoketypeprev_daily_t5d_u_r$m_u, tsmoketypeprev_daily_t5d_u_r$m_r), 
      select(rbind(tsmoketypeprev_daily_t5e_u_r$m_u, tsmoketypeprev_daily_t5e_u_r$m_r), -c(agerange2,n_sum)), 
      select(rbind(tsmoketypeprev_daily_t5f_u_r$m_u, tsmoketypeprev_daily_t5f_u_r$m_r), -c(agerange2,n_sum)),
      select(rbind(tsmoketypeprev_daily_t5g_u_r$m_u, tsmoketypeprev_daily_t5g_u_r$m_r), -c(agerange2,n_sum))) %>% 
  set_contents(1, everywhere, c("Age Group (years)", "n", "% cigars, cheerots, cigarillos", "95% CI", 
                                "% shisha sessions", "95% CI", 
                                "% heated tobacco products", "95% CI",
                                "% other type of tobacco", "95% CI")) %>%
  set_right_border(row = everywhere, col = c(4,6,8), value = 0) %>% 
  final_tbl(u_r, 1, "Men", "Proportion of population who smoke each of the following products daily by type of settlement", 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
cbind(rbind(tsmoketypeprev_daily_t5a_u_r$w_u, tsmoketypeprev_daily_t5a_u_r$w_r), 
      select(rbind(tsmoketypeprev_daily_t5b_u_r$w_u, tsmoketypeprev_daily_t5b_u_r$w_r), -c(agerange2,n_sum)), 
      select(rbind(tsmoketypeprev_daily_t5c_u_r$w_u, tsmoketypeprev_daily_t5c_u_r$w_r), -c(agerange2,n_sum))) %>% 
  set_contents(1, everywhere, c("Age Group (years)", "n", "% manufactured cig.", "95% CI", 
                                "% hand-rolled cig.", "95% CI", 
                                "% pipes of tobacco", "95% CI")) %>% 
  set_right_border(row = everywhere, col = c(4,6), value = 0) %>% 
  final_tbl(u_r, 1, "Women", "Proportion of population who smoke each of the following products daily by type of settlement", 8)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
cbind(rbind(tsmoketypeprev_daily_t5d_u_r$w_u, tsmoketypeprev_daily_t5d_u_r$w_r), 
      select(rbind(tsmoketypeprev_daily_t5e_u_r$w_u, tsmoketypeprev_daily_t5e_u_r$w_r), -c(agerange2,n_sum)), 
      select(rbind(tsmoketypeprev_daily_t5f_u_r$w_u, tsmoketypeprev_daily_t5f_u_r$w_r), -c(agerange2,n_sum)),
      select(rbind(tsmoketypeprev_daily_t5g_u_r$w_u, tsmoketypeprev_daily_t5g_u_r$w_r), -c(agerange2,n_sum))) %>% 
  set_contents(1, everywhere, c("Age Group (years)", "n", "% cigars, cheerots, cigarillos", "95% CI", 
                                "% shisha sessions", "95% CI", 
                                "% heated tobacco products", "95% CI",
                                "% other type of tobacco", "95% CI")) %>%
  set_right_border(row = everywhere, col = c(4,6,8), value = 0) %>% 
  final_tbl(u_r, 1, "Women", "Proportion of population who smoke each of the following products daily by type of settlement", 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
cbind(rbind(tsmoketypeprev_daily_t5a_u_r$b_u, tsmoketypeprev_daily_t5a_u_r$b_r), 
      select(rbind(tsmoketypeprev_daily_t5b_u_r$b_u, tsmoketypeprev_daily_t5b_u_r$b_r), -c(agerange2,n_sum)), 
      select(rbind(tsmoketypeprev_daily_t5c_u_r$b_u, tsmoketypeprev_daily_t5c_u_r$b_r), -c(agerange2,n_sum))) %>% 
  set_contents(1, everywhere, c("Age Group (years)", "n", "% manufactured cig.", "95% CI", 
                                "% hand-rolled cig.", "95% CI", 
                                "% pipes of tobacco", "95% CI")) %>% 
  set_right_border(row = everywhere, col = c(4,6), value = 0) %>% 
  final_tbl(u_r, 1, "Both sexes", "Proportion of population who smoke each of the following products daily by type of settlement", 8)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
cbind(rbind(tsmoketypeprev_daily_t5d_u_r$b_u, tsmoketypeprev_daily_t5d_u_r$b_r), 
      select(rbind(tsmoketypeprev_daily_t5e_u_r$b_u, tsmoketypeprev_daily_t5e_u_r$b_r), -c(agerange2,n_sum)), 
      select(rbind(tsmoketypeprev_daily_t5f_u_r$b_u, tsmoketypeprev_daily_t5f_u_r$b_r), -c(agerange2,n_sum)),
      select(rbind(tsmoketypeprev_daily_t5g_u_r$b_u, tsmoketypeprev_daily_t5g_u_r$b_r), -c(agerange2,n_sum))) %>% 
  set_contents(1, everywhere, c("Age Group (years)", "n", "% cigars, cheerots, cigarillos", "95% CI", 
                                "% shisha sessions", "95% CI", 
                                "% heated tobacco products", "95% CI",
                                "% other type of tobacco", "95% CI")) %>%
  set_right_border(row = everywhere, col = c(4,6,8), value = 0) %>% 
  final_tbl(u_r, 1, "Both sexes", "Proportion of population who smoke each of the following products daily by type of settlement", 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
cbind(tsmoketypeprev_daily_t5a_b_reg, 
      select(tsmoketypeprev_daily_t5b_b_reg, -c(region,n_sum)), 
      select(tsmoketypeprev_daily_t5c_b_reg, -c(region,n_sum))) %>%
  set_contents(1, everywhere, c("Region", "n", "% manufactured cig.", "95% CI", 
                                "% hand-rolled cig.", "95% CI", 
                                "% pipes of tobacco", "95% CI")) %>% 
  set_right_border(row = everywhere, col = c(4,6), value = 0) %>% 
  final_tbl(reg, 1, "Both sexes", "Proportion of population who smoke each of the following products daily by region", 8)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
cbind(tsmoketypeprev_daily_t5d_b_reg, 
      select(tsmoketypeprev_daily_t5e_b_reg, -c(region,n_sum)), 
      select(tsmoketypeprev_daily_t5f_b_reg, -c(region,n_sum)),
      select(tsmoketypeprev_daily_t5g_b_reg, -c(region,n_sum))) %>% 
  set_contents(1, everywhere, c("Region", "n", "% cigars, cheerots, cigarillos", "95% CI", 
                                "% shisha sessions", "95% CI", 
                                "% heated tobacco products", "95% CI",
                                "% other type of tobacco", "95% CI")) %>%
  set_right_border(row = everywhere, col = c(4,6,8), value = 0) %>% 
  final_tbl(reg, 1, "Both sexes", "Proportion of population who smoke each of the following products daily by region", 10)
```

<br>

**Analysis information**:

- Questions used: T1, T2, T5a-T5fw
- R script name:  Tsmoketypeprev

***

**Frequency of daily cigarette smoking**

Description: Percentage of daily cigarette smokers smoking given quantities of manufactured or hand-rolled cigarettes per day.

Instrument questions:

- Do you currently smoke any tobacco products, such as cigarettes, cigars, or pipes?
- Do you currently smoke tobacco products daily?
- On average, how many of the following products do you smoke each day?

```{r tcig_tbls, echo=FALSE}

# column names to use with huxtable
tcig_col_names <- c("Age Group (years)", "n", "% <5 cigs.", "95% CI", "% 5-9 cigs.", "95% CI", 
                    "% 10-14 cigs.", "95% CI", "% 15-24 cigs.", "95% CI", "%  25 cigs.", "95% CI")

# column names for region to use with huxtable
tcig_reg_col_names <- c("Region", "n", "% <5 cigs.", "95% CI", "% 5-9 cigs.", "95% CI", 
                        "% 10-14 cigs.", "95% CI", "% 15-24 cigs.", "95% CI", "%  25 cigs.", "95% CI")

# men, women, both sexes
tcig_c_m_w_b <- join_tbls(tcig_c, m_w_b, 5, tcig_col_names)
```
```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# urban, rural
tcig_c_u_r <- join_tbls(tcig_c, u_r, 5, tcig_col_names)
```

<br>

```{r}
tcig_c_m_w_b$m %>% final_tbl(.disaggregation = m_w_b, .s_amount = 1, .s_val = "Men", .title = "Percentage of daily smokers smoking given quantities of manufactured or hand-rolled cigarettes per day", .colspan_val = 12)
```

<br>

```{r}
tcig_c_m_w_b$w %>% final_tbl(.disaggregation = m_w_b, .s_amount = 1, .s_val = "Women", .title = "Percentage of daily smokers smoking given quantities of manufactured or hand-rolled cigarettes per day", .colspan_val = 12)
```

<br>

```{r}
tcig_c_m_w_b$b %>% final_tbl(.disaggregation = m_w_b, .s_amount = 1, .s_val = "Both sexes", .title = "Percentage of daily smokers smoking given quantities of manufactured or hand-rolled cigarettes per day", .colspan_val = 12)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
rbind(tcig_c_u_r$m_u, tcig_c_u_r$m_r) %>% 
  final_tbl(.disaggregation = u_r, .s_amount = 1, .s_val = "Men", .title = "Percentage of daily smokers smoking given quantities of manufactured or hand-rolled cigarettes per day by type of settlement", .colspan_val = 12)

```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
rbind(tcig_c_u_r$w_u, tcig_c_u_r$w_r) %>% 
  final_tbl(.disaggregation = u_r, .s_amount = 1, .s_val = "Women", .title = "Percentage of daily smokers smoking given quantities of manufactured or hand-rolled cigarettes per day by type of settlement", .colspan_val = 12)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
rbind(tcig_c_u_r$b_u, tcig_c_u_r$b_r) %>% 
  final_tbl(.disaggregation = u_r, .s_amount = 1, .s_val = "Both sexes", .title = "Percentage of daily smokers smoking given quantities of manufactured or hand-rolled cigarettes per day by type of settlement", .colspan_val = 12)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# region
tcig_c$b_reg %>% unite_ci(.ci_amount = 5) %>% apply_hux(.col_names = tcig_reg_col_names) %>% 
  final_tbl(.disaggregation = reg, .s_amount = 1, .s_val = "Both sexes", .title = "Percentage of daily smokers smoking given quantities of manufactured or hand-rolled cigarettes per day by region", .colspan_val = 12)
```

<br>

**Analysis information**:

- Questions used: T1, T2, T5a, T5b
- R script name:  Tcig

***

**Former daily smokers and former smokers**

Description: Percentage of former daily smokers among all respondents and among ever daily smokers, and the mean duration, in years, since former smokers quit smoking.

Instrument questions:

- Do you currently smoke any tobacco products, such as cigarettes, cigars, or pipes?
- Do you currently smoke tobacco products daily?
- In the past did you ever smoke any tobacco products?
- In the past, did you ever smoke daily?
- How old were you when you stopped smoking?

```{r tsmokeexdaily_tbls}

# column names to use with huxtable
# 1. Former daily smokers (who dont smoke currently) among all respondents
# 2. Former daily smokers (who dont smoke currently) among ever daily smokers
tsmokeexdaily_col_names <- c("Age Group (years)", "n", "% Former daily smokers", "95% CI")
tsmokeexdaily_reg_col_names <- c("Region", "n", "% Former daily smokers", "95% CI")
# 3. Mean years since cessation
tsmokeexdaily_stop_col_names <- c("Age Group (years)", "n", "Mean years", "95% CI")
tsmokeexdaily_stop_reg_col_names <- c("Region", "n", "Mean years", "95% CI")

# 1.
# men, women, both sexes
tsmokeexdaily_c_m_w_b <- join_tbls(tsmokeexdaily_c, m_w_b, 1, tsmokeexdaily_col_names)
# 2.
# men, women, both sexes
tsmokeexdaily_everdaily_c_m_w_b <- join_tbls(tsmokeexdaily_everdaily_c, m_w_b, 1, tsmokeexdaily_col_names)
# 3. 
# men, women, both sexes
tsmokeexdaily_stop_m_w_b <- join_tbls(tsmokeexdaily_stop, m_w_b, 1, tsmokeexdaily_stop_col_names)
```
```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 1.
# urban, rural
tsmokeexdaily_c_u_r <- join_tbls(tsmokeexdaily_c, u_r, 1, tsmokeexdaily_col_names)
# 2.
# urban, rural
tsmokeexdaily_everdaily_c_u_r <- join_tbls(tsmokeexdaily_everdaily_c, u_r, 1, tsmokeexdaily_col_names)
# 3. 
# urban, rural
tsmokeexdaily_stop_u_r <- join_tbls(tsmokeexdaily_stop, u_r, 1, tsmokeexdaily_stop_col_names)
```

<br>

```{r}
cbind(tsmokeexdaily_c_m_w_b$m, select(tsmokeexdaily_c_m_w_b$w, -agerange), select(tsmokeexdaily_c_m_w_b$b, -agerange)) %>% 
  final_tbl(.disaggregation = m_w_b, .s_amount = 3, .title = "Former daily smokers (who dont smoke currently) among all respondents", .colspan_val = 10)
```

<br>

```{r}
cbind(tsmokeexdaily_everdaily_c_m_w_b$m, select(tsmokeexdaily_everdaily_c_m_w_b$w, -agerange), select(tsmokeexdaily_everdaily_c_m_w_b$b, -agerange)) %>% 
  final_tbl(.disaggregation = m_w_b, .s_amount = 3, .title = "Former daily smokers (who dont smoke currently) among ever daily smokers", .colspan_val = 10)
```

<br>

```{r}
cbind(tsmokeexdaily_stop_m_w_b$m, select(tsmokeexdaily_stop_m_w_b$w, -agerange), select(tsmokeexdaily_stop_m_w_b$b, -agerange)) %>% 
  final_tbl(.disaggregation = m_w_b, .s_amount = 3, .title = "Mean years since cessation", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
tbl_m_u_r <- rbind(tsmokeexdaily_c_u_r$m_u, tsmokeexdaily_c_u_r$m_r)
tbl_w_u_r <- rbind(tsmokeexdaily_c_u_r$w_u, tsmokeexdaily_c_u_r$w_r)
tbl_b_u_r <- rbind(tsmokeexdaily_c_u_r$b_u, tsmokeexdaily_c_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_tbl(.disaggregation = u_r, .s_amount = 3, .title = "Former daily smokers (who dont smoke currently) among all respondents by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
tbl_m_u_r <- rbind(tsmokeexdaily_everdaily_c_u_r$m_u, tsmokeexdaily_everdaily_c_u_r$m_r)
tbl_w_u_r <- rbind(tsmokeexdaily_everdaily_c_u_r$w_u, tsmokeexdaily_everdaily_c_u_r$w_r)
tbl_b_u_r <- rbind(tsmokeexdaily_everdaily_c_u_r$b_u, tsmokeexdaily_everdaily_c_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_tbl(.disaggregation = u_r, .s_amount = 3, .title = "Former daily smokers (who dont smoke currently) among ever daily smokers by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
tbl_m_u_r <- rbind(tsmokeexdaily_stop_u_r$m_u, tsmokeexdaily_stop_u_r$m_r)
tbl_w_u_r <- rbind(tsmokeexdaily_stop_u_r$w_u, tsmokeexdaily_stop_u_r$w_r)
tbl_b_u_r <- rbind(tsmokeexdaily_stop_u_r$b_u, tsmokeexdaily_stop_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_tbl(.disaggregation = u_r, .s_amount = 3, .title = "Mean years since cessation by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
tsmokeexdaily_c$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = tsmokeexdaily_reg_col_names) %>% 
  final_tbl(reg, 1, "Both sexes", "Former daily smokers (who dont smoke currently) among all respondents by region", 4)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
tsmokeexdaily_everdaily_c$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = tsmokeexdaily_reg_col_names) %>% 
  final_tbl(reg, 1, "Both sexes", "Former daily smokers (who dont smoke currently) among ever daily smokers by region", 4)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
tsmokeexdaily_stop$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = tsmokeexdaily_reg_col_names) %>% 
  final_tbl(reg, 1, "Both sexes", "Mean years since cessation by region", 4)
```

<br>

**Analysis information**:

- Questions used: T1, T2, T8, T9, T10, T11a-c
- R script name:  Tsmokeexdaily

***

**Cessation**

Description: Percentage of current smokers who have tried to stop smoking during the past 12 months.

Instrument questions:

- Do you currently smoke any tobacco products, such as cigarettes, cigars, or pipes?
- During the past 12 months, have you tried to stop smoking?

```{r tcessation_c_tbls}

# column names to use with huxtable
tcessation_c_col_names <- c("Age Group (years)", "n", "% Tried to stop smoking", "95% CI")
tcessation_c_reg_col_names <- c("Region", "n", "% Tried to stop smoking", "95% CI")

# men, women, both sexes
tcessation_c_m_w_b <- join_tbls(tcessation_c, m_w_b, 1, tcessation_c_col_names)
```
```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# urban, rural
tcessation_c_u_r <- join_tbls(tcessation_c, u_r, 1, tcessation_c_col_names)
```

<br>

```{r}
cbind(tcessation_c_m_w_b$m, select(tcessation_c_m_w_b$w, -agerange), select(tcessation_c_m_w_b$b, -agerange)) %>% 
  final_tbl(.disaggregation = m_w_b, .s_amount = 3, .title = "Current smokers who have tried to stop smoking", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
tbl_m_u_r <- rbind(tcessation_c_u_r$m_u, tcessation_c_u_r$m_r)
tbl_w_u_r <- rbind(tcessation_c_u_r$w_u, tcessation_c_u_r$w_r)
tbl_b_u_r <- rbind(tcessation_c_u_r$b_u, tcessation_c_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_tbl(.disaggregation = u_r, .s_amount = 3, .title = "Current smokers who have tried to stop smoking by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
tcessation_c$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = tcessation_c_reg_col_names) %>% 
  final_tbl(reg, 1, "Both sexes", "Current smokers who have tried to stop smoking by region", 4)
```
<br>

**Analysis information**:

- Questions used: T1, T2, T6
- R script name:  Tcessation

***

**Advice to stop smoking**

Description: Percentage of current smokers who have been advised by a doctor or other health worker to stop smoking, among those smokers who have had a visit to a doctor or other health worker in the past 12 months.

Instrument questions:

- Do you currently smoke any tobacco products, such as cigarettes, cigars, or pipes?
- During any visit to a doctor or other health worker in the past 12 months, were you advised to quit smoking tobacco?

```{r tcessation_d_tbls}

# column names to use with huxtable
tcessation_d_col_names <- c("Age Group (years)", "n", "% Advised to stop smoking", "95% CI")
tcessation_d_reg_col_names <- c("Region", "n", "% Advised to stop smoking", "95% CI")

# men, women, both sexes
tcessation_d_m_w_b <- join_tbls(tcessation_d, m_w_b, 1, tcessation_d_col_names)
```
```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# urban, rural
tcessation_d_u_r <- join_tbls(tcessation_d, u_r, 1, tcessation_d_col_names)
```

<br>

```{r}
cbind(tcessation_d_m_w_b$m, select(tcessation_d_m_w_b$w, -agerange), select(tcessation_d_m_w_b$b, -agerange)) %>% 
  final_tbl(.disaggregation = m_w_b, .s_amount = 3, .title = "Current smokers who have been advised by doctor to stop smoking", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
tbl_m_u_r <- rbind(tcessation_d_u_r$m_u, tcessation_d_u_r$m_r)
tbl_w_u_r <- rbind(tcessation_d_u_r$w_u, tcessation_d_u_r$w_r)
tbl_b_u_r <- rbind(tcessation_d_u_r$b_u, tcessation_d_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_tbl(.disaggregation = u_r, .s_amount = 3, .title = "Current smokers who have been advised by doctor to stop smoking by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
tcessation_d$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = tcessation_d_reg_col_names) %>% 
  final_tbl(reg, 1, "Both sexes", "Current smokers who have been advised by doctor to stop smoking by region", 4)
```

<br>

**Analysis information**:

- Questions used: T1, T2, T7
- R script name:  Tcessation

***

**Current users of smokeless tobacco**

Description: Percentage of current users of smokeless tobacco among all respondents.

Instrument questions:

- Do you currently use any smokeless tobacco such as [snuff, chewing tobacco, betel]?

```{r tsmokelessstatus_d_tbls}

# column names to use with huxtable
tsmokelessstatus_d_col_names <- c("Age Group (years)", "n", "% Current users", "95% CI")
tsmokelessstatus_d_reg_col_names <- c("Region", "n", "% Current users", "95% CI")

# men, women, both sexes
tsmokelessstatus_d_m_w_b <- join_tbls(tsmokelessstatus_d, m_w_b, 1, tsmokelessstatus_d_col_names)
```
```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# urban, rural
tsmokelessstatus_d_u_r <- join_tbls(tsmokelessstatus_d, u_r, 1, tsmokelessstatus_d_col_names)
```

<br>

```{r}
cbind(tsmokelessstatus_d_m_w_b$m, select(tsmokelessstatus_d_m_w_b$w, -agerange), select(tsmokelessstatus_d_m_w_b$b, -agerange)) %>% 
  final_tbl(.disaggregation = m_w_b, .s_amount = 3, .title = "Current users of smokeless tobacco", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
tbl_m_u_r <- rbind(tsmokelessstatus_d_u_r$m_u, tsmokelessstatus_d_u_r$m_r)
tbl_w_u_r <- rbind(tsmokelessstatus_d_u_r$w_u, tsmokelessstatus_d_u_r$w_r)
tbl_b_u_r <- rbind(tsmokelessstatus_d_u_r$b_u, tsmokelessstatus_d_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_tbl(.disaggregation = u_r, .s_amount = 3, .title = "Current users of smokeless tobacco by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
tsmokelessstatus_d$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = tsmokelessstatus_d_reg_col_names) %>% 
  final_tbl(reg, 1, "Both sexes", "Current users of smokeless tobacco by region", 4)
```

<br>

**Analysis information**:

- Questions used: T12, T13, T15
- R script name:  Tsmokelessstatus

***

**Status of smokeless tobacco use**

Description: Status of using smokeless tobacco among all respondents.

Instrument questions:

- Do you currently use any smokeless tobacco such as [snuff, chewing tobacco, betel]?
- Do you currently use smokeless tobacco products daily?
- In the past, did you ever use smokeless tobacco such as [snuff, chewing tobacco, betel]?

```{r tsmokelessstatus_c_tbls}

# column names to use with huxtable
tsmokelessstatus_c_col_names <- c("Age Group (years)", "n", "% Daily", "95% CI",
                                  "% Non-daily", "95% CI", "% Past user", "95% CI", "% Never used", "95% CI")
tsmokelessstatus_c_reg_col_names <- c("Region", "n", "% Daily", "95% CI",
                                      "% Non-daily", "95% CI", "% Past user", "95% CI", "% Never used", "95% CI")

# men, women, both sexes
tsmokelessstatus_c_m_w_b <- join_tbls(tsmokelessstatus_c, m_w_b, 4, tsmokelessstatus_c_col_names)
```
```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# urban, rural
tsmokelessstatus_c_u_r <- join_tbls(tsmokelessstatus_c, u_r, 4, tsmokelessstatus_c_col_names)
```

<br>

```{r}
tsmokelessstatus_c_m_w_b$m %>% final_tbl(m_w_b, 1, "Men", "Smokeless tobacco use", 10) %>% 
  insert_row(c("","","Current user","","","","Non user","","",""), after = 2) %>% 
  merge_cells(row = 3, col = c(7:10)) %>% merge_cells(row = 3, col = c(3:6)) %>% 
  set_right_border(row = 3, col = c(1:6), value = 0)
```

<br>

```{r}
tsmokelessstatus_c_m_w_b$w %>% final_tbl(m_w_b, 1, "Women", "Smokeless tobacco use", 10) %>% 
  insert_row(c("","","Current user","","","","Non user","","",""), after = 2) %>% 
  merge_cells(row = 3, col = c(7:10)) %>% merge_cells(row = 3, col = c(3:6)) %>% 
  set_right_border(row = 3, col = c(1:6), value = 0)
```

<br>

```{r}
tsmokelessstatus_c_m_w_b$b %>% final_tbl(m_w_b, 1, "Both sexes", "Smokeless tobacco use", 10) %>% 
  insert_row(c("","","Current user","","","","Non user","","",""), after = 2) %>% 
  merge_cells(row = 3, col = c(7:10)) %>% merge_cells(row = 3, col = c(3:6)) %>% 
  set_right_border(row = 3, col = c(1:6), value = 0)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
rbind(tsmokelessstatus_c_u_r$m_u, tsmokelessstatus_c_u_r$m_r) %>% 
  final_tbl(u_r, 1, "Men", "Smokeless tobacco use by type of settlement", 10) %>% 
  insert_row(c("","","Current user","","","","Non user","","",""), after = 2) %>% 
  merge_cells(row = 3, col = c(7:10)) %>% merge_cells(row = 3, col = c(3:6)) %>% 
  set_right_border(row = 3, col = c(1:6), value = 0)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
rbind(tsmokelessstatus_c_u_r$w_u, tsmokelessstatus_c_u_r$w_r) %>% 
  final_tbl(u_r, 1, "Women", "Smokeless tobacco use by type of settlement", 10) %>% 
  insert_row(c("","","Current user","","","","Non user","","",""), after = 2) %>% 
  merge_cells(row = 3, col = c(7:10)) %>% merge_cells(row = 3, col = c(3:6)) %>% 
  set_right_border(row = 3, col = c(1:6), value = 0)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
rbind(tsmokelessstatus_c_u_r$b_u, tsmokelessstatus_c_u_r$b_r) %>% 
  final_tbl(u_r, 1, "Both sexes", "Smokeless tobacco use by type of settlement", 10) %>% 
  insert_row(c("","","Current user","","","","Non user","","",""), after = 2) %>% 
  merge_cells(row = 3, col = c(7:10)) %>% merge_cells(row = 3, col = c(3:6)) %>% 
  set_right_border(row = 3, col = c(1:6), value = 0)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# region
tsmokelessstatus_c$b_reg %>% unite_ci(.ci_amount = 4) %>% apply_hux(.col_names = tsmokelessstatus_c_reg_col_names) %>% 
  final_tbl(reg, 1, "Both sexes", "Smokeless tobacco use by region", 10) %>% 
  insert_row(c("","","Current user","","","","Non user","","",""), after = 2) %>% 
  merge_cells(row = 3, col = c(7:10)) %>% merge_cells(row = 3, col = c(3:6)) %>% 
  set_right_border(row = 3, col = c(1:6), value = 0)
```

<br>

**Analysis information**:

- Questions used: T12, T13, T15
- R script name:  Tsmokelessstatus

***

**Former daily users of smokeless tobacco**

Description: Percentage of former daily users of smokeless tobacco among all respondents and among ever daily users.

Instrument questions:

- Do you currently use any smokeless tobacco such as [snuff, chewing tobacco, betel]?
- Do you currently use smokeless tobacco products daily?
- In the past, did you ever use smokeless tobacco such as [snuff, chewing tobacco, betel]?
- In the past, did you ever use smokeless tobacco such as [snuff, chewing tobacco, betel] daily?

```{r tsmokelessexdaily_tbls}

# column names to use with huxtable
# 1. Former daily smokeless tobacco users (who don't use tobacco currently) among all respondents
# 2. Former daily smokeless tobacco users (who dont use tobacco currently) among ever daily users
tsmokelessexdaily_col_names <- c("Age Group (years)", "n", "% Former daily users", "95% CI")
tsmokelessexdaily_reg_col_names <- c("Region", "n", "% Former daily users", "95% CI")

# 1.
# men, women, both sexes
tsmokelessexdaily_c_m_w_b <- join_tbls(tsmokelessexdaily_c, m_w_b, 1, tsmokelessexdaily_col_names)

# 2.
# men, women, both sexes
tsmokelessexdaily_everdaily_c_m_w_b <- join_tbls(tsmokelessexdaily_everdaily_c, m_w_b, 1, tsmokelessexdaily_col_names)
```
```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 1.
# urban, rural
tsmokelessexdaily_c_u_r <- join_tbls(tsmokelessexdaily_c, u_r, 1, tsmokelessexdaily_col_names)
# 2.
# urban, rural
tsmokelessexdaily_everdaily_c_u_r <- join_tbls(tsmokelessexdaily_everdaily_c, u_r, 1, tsmokelessexdaily_col_names)
```

<br>

```{r}
cbind(tsmokelessexdaily_c_m_w_b$m, select(tsmokelessexdaily_c_m_w_b$w, -agerange), select(tsmokelessexdaily_c_m_w_b$b, -agerange)) %>% 
  final_tbl(.disaggregation = m_w_b, .s_amount = 3, .title = "Former daily smokeless tobacco users (who don't use tobacco currently) among all respondents", .colspan_val = 10)
```

<br>

```{r}
cbind(tsmokelessexdaily_everdaily_c_m_w_b$m, select(tsmokelessexdaily_everdaily_c_m_w_b$w, -agerange), select(tsmokelessexdaily_everdaily_c_m_w_b$b, -agerange)) %>%
  final_tbl(.disaggregation = m_w_b, .s_amount = 3, .title = "Former daily smokeless tobacco users (who dont use tobacco currently) among ever daily users", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
tbl_m_u_r <- rbind(tsmokelessexdaily_c_u_r$m_u, tsmokelessexdaily_c_u_r$m_r)
tbl_w_u_r <- rbind(tsmokelessexdaily_c_u_r$w_u, tsmokelessexdaily_c_u_r$w_r)
tbl_b_u_r <- rbind(tsmokelessexdaily_c_u_r$b_u, tsmokelessexdaily_c_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_tbl(.disaggregation = u_r, .s_amount = 3, .title = "Former daily smokeless tobacco users (who don't use tobacco currently) among all respondents by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
tbl_m_u_r <- rbind(tsmokelessexdaily_everdaily_c_u_r$m_u, tsmokelessexdaily_everdaily_c_u_r$m_r)
tbl_w_u_r <- rbind(tsmokelessexdaily_everdaily_c_u_r$w_u, tsmokelessexdaily_everdaily_c_u_r$w_r)
tbl_b_u_r <- rbind(tsmokelessexdaily_everdaily_c_u_r$b_u, tsmokelessexdaily_everdaily_c_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>%
  final_tbl(.disaggregation = u_r, .s_amount = 3, .title = "Former daily smokeless tobacco users (who dont use tobacco currently) among ever daily users by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
tsmokelessexdaily_c$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = tsmokelessexdaily_reg_col_names) %>% 
  final_tbl(reg, 1, "Both sexes", "Former daily smokeless tobacco users (who don't use tobacco currently) among all respondents by region", 4)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
tsmokelessexdaily_everdaily_c$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = tsmokelessexdaily_reg_col_names) %>% 
  final_tbl(reg, 1, "Both sexes", "Former daily smokeless tobacco users (who dont use tobacco currently) among ever daily users by region", 4)
```

<br>

**Analysis information**:

- Questions used: T12, T13, T15, T16
- R script name:  Tsmokelessexdaily

***

**Current tobacco users**

Description: Percentage of daily and current (daily plus non-daily) tobacco users, includes smoking and smokeless, among all respondents.

Instrument questions:

- Do you currently smoke any tobacco products, such as cigarettes, cigars, or pipes?
- Do you currently smoke tobacco products daily?
- Do you currently use any smokeless tobacco such as [snuff, chewing tobacco, betel]?
- Do you currently use smokeless tobacco products daily?

```{r tdailyuser_tbls}

# column names to use with huxtable
# 1. Current tobacco users
tdailyuser_c_col_names <- c("Age Group (years)", "n", "% Current users", "95% CI")
tdailyuser_c_reg_col_names <- c("Region", "n", "% Current users", "95% CI")
# 2. Daily tobacco users
tdailyuser_d_col_names <- c("Age Group (years)", "n", "% Daily users", "95% CI")
tdailyuser_d_reg_col_names <- c("Region", "n", "% Daily users", "95% CI")

# 1.
# men, women, both sexes
tdailyuser_c_m_w_b <- join_tbls(tdailyuser_c, m_w_b, 1, tdailyuser_c_col_names)
# 2.
# men, women, both sexes
tdailyuser_d_c_m_w_b <- join_tbls(tdailyuser_d, m_w_b, 1, tdailyuser_d_col_names)
```
```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 1.
# urban, rural
tdailyuser_c_u_r <- join_tbls(tdailyuser_c, u_r, 1, tdailyuser_c_col_names)
# 2.
# urban, rural
tdailyuser_d_c_u_r <- join_tbls(tdailyuser_d, u_r, 1, tdailyuser_d_col_names)
```

<br>

```{r}
cbind(tdailyuser_c_m_w_b$m, select(tdailyuser_c_m_w_b$w, -agerange), select(tdailyuser_c_m_w_b$b, -agerange)) %>% 
  final_tbl(.disaggregation = m_w_b, .s_amount = 3, .title = "Current tobacco users", .colspan_val = 10)
```

<br>

```{r}
cbind(tdailyuser_d_c_m_w_b$m, select(tdailyuser_d_c_m_w_b$w, -agerange), select(tdailyuser_d_c_m_w_b$b, -agerange)) %>% 
  final_tbl(.disaggregation = m_w_b, .s_amount = 3, .title = "Daily tobacco users", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
tbl_m_u_r <- rbind(tdailyuser_c_u_r$m_u, tdailyuser_c_u_r$m_r)
tbl_w_u_r <- rbind(tdailyuser_c_u_r$w_u, tdailyuser_c_u_r$w_r)
tbl_b_u_r <- rbind(tdailyuser_c_u_r$b_u, tdailyuser_c_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_tbl(.disaggregation = u_r, .s_amount = 3, .title = "Current tobacco users by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
tbl_m_u_r <- rbind(tdailyuser_d_c_u_r$m_u, tdailyuser_d_c_u_r$m_r)
tbl_w_u_r <- rbind(tdailyuser_d_c_u_r$w_u, tdailyuser_d_c_u_r$w_r)
tbl_b_u_r <- rbind(tdailyuser_d_c_u_r$b_u, tdailyuser_d_c_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_tbl(.disaggregation = u_r, .s_amount = 3, .title = "Daily tobacco users by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
tdailyuser_c$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = tdailyuser_c_reg_col_names) %>% 
  final_tbl(reg, 1, "Both sexes", "Current tobacco users by region", 4)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
tdailyuser_d$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = tdailyuser_d_reg_col_names) %>% 
  final_tbl(reg, 1, "Both sexes", "Daily tobacco users by region", 4)
```

<br>

**Analysis information**:

- Questions used: T1, T2, T12, T13
- R script name:  Tdailyuser

***


**Exposure to second-hand smoke in home in past 30 days**

Description: Percentage of respondents exposed second-hand smoke in the home in the past 30 days.

Instrument questions:

- In the past 30 days, did someone smoke in your home?

```{r tetshome_tbls}

# column names to use with huxtable
tetshome_c_col_names <- c("Age Group (years)", "n", "% Exposed", "95% CI")
tetshome_c_reg_col_names <- c("Region", "n", "% Exposed", "95% CI")

# men, women, both sexes
tetshome_c_m_w_b <- join_tbls(tetshome_c, m_w_b, 1, tetshome_c_col_names)
```
```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# urban, rural
tetshome_c_u_r <- join_tbls(tetshome_c, u_r, 1, tetshome_c_col_names)
```

<br>

```{r}
cbind(tetshome_c_m_w_b$m, select(tetshome_c_m_w_b$w, -agerange), select(tetshome_c_m_w_b$b, -agerange)) %>% 
  final_tbl(.disaggregation = m_w_b, .s_amount = 3, .title = "Exposed to second-hand smoke in home during the past 30 days", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
tbl_m_u_r <- rbind(tetshome_c_u_r$m_u, tetshome_c_u_r$m_r)
tbl_w_u_r <- rbind(tetshome_c_u_r$w_u, tetshome_c_u_r$w_r)
tbl_b_u_r <- rbind(tetshome_c_u_r$b_u, tetshome_c_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_tbl(.disaggregation = u_r, .s_amount = 3, .title = "Exposed to second-hand smoke in home during the past 30 days by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
tetshome_c$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = tetshome_c_reg_col_names) %>% 
  final_tbl(reg, 1, "Both sexes", "Exposed to second-hand smoke in home during the past 30 days by region", 4)
```

<br>

**Analysis information**:

- Questions used: T17
- R script name:  Tetshome

***


**Exposure to second-hand smoke in the workplace in past 30 days**

Description: Percentage of respondents exposed to second-hand smoke in the workplace in the past 30 days.

Instrument questions:

- During the past 30 days, did someone smoke in closed areas in your workplace (in the building, in a work area or a specific office)?

```{r tetswork_tbls}

# column names to use with huxtable
tetswork_c_col_names <- c("Age Group (years)", "n", "% Exposed", "95% CI")
tetswork_c_reg_col_names <- c("Region", "n", "% Exposed", "95% CI")

# men, women, both sexes
tetswork_c_m_w_b <- join_tbls(tetswork_c, m_w_b, 1, tetswork_c_col_names)
```
```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# urban, rural
tetswork_c_u_r <- join_tbls(tetswork_c, u_r, 1, tetswork_c_col_names)
```

<br>

```{r}
cbind(tetswork_c_m_w_b$m, select(tetswork_c_m_w_b$w, -agerange), select(tetswork_c_m_w_b$b, -agerange)) %>% 
  final_tbl(.disaggregation = m_w_b, .s_amount = 3, .title = "Exposed to second-hand smoke in the workplace during the past 30 days", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
tbl_m_u_r <- rbind(tetswork_c_u_r$m_u, tetswork_c_u_r$m_r)
tbl_w_u_r <- rbind(tetswork_c_u_r$w_u, tetswork_c_u_r$w_r)
tbl_b_u_r <- rbind(tetswork_c_u_r$b_u, tetswork_c_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_tbl(.disaggregation = u_r, .s_amount = 3, .title = "Exposed to second-hand smoke in the workplace during the past 30 days by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
tetswork_c$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = tetswork_c_reg_col_names) %>% 
  final_tbl(reg, 1, "Both sexes", "Exposed to second-hand smoke in the workplace during the past 30 days by region", 4)
```

<br>

**Analysis information**:

- Questions used: T18
- R script name:  Tetswork

***

**Current e-cigarettes usage**

Description: Percentage of current users of electronic cigarettes among all respondents.

Instrument questions:

- Do you currently use electronic cigarettes?

```{r etstatus_d_tbls}

# column names to use with huxtable
etstatus_d_col_names <- c("Age Group (years)", "n", "% Current users", "95% CI")
etstatus_d_reg_col_names <- c("Region", "n", "% Current users", "95% CI")

# men, women, both sexes
etstatus_d_m_w_b <- join_tbls(etstatus_d, m_w_b, 1, etstatus_d_col_names)
```
```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# urban, rural
etstatus_d_u_r <- join_tbls(etstatus_d, u_r, 1, etstatus_d_col_names)
```

<br>

```{r}
cbind(etstatus_d_m_w_b$m, select(etstatus_d_m_w_b$w, -agerange), select(etstatus_d_m_w_b$b, -agerange)) %>% 
  final_tbl(.disaggregation = m_w_b, .s_amount = 3, .title = "Percentage of current users of e-cigarettes", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
tbl_m_u_r <- rbind(etstatus_d_u_r$m_u, etstatus_d_u_r$m_r)
tbl_w_u_r <- rbind(etstatus_d_u_r$w_u, etstatus_d_u_r$w_r)
tbl_b_u_r <- rbind(etstatus_d_u_r$b_u, etstatus_d_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_tbl(.disaggregation = u_r, .s_amount = 3, .title = "Percentage of current users of e-cigarettes by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
etstatus_d$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = etstatus_d_reg_col_names) %>% 
  final_tbl(reg, 1, "Both sexes", "Percentage of current users of e-cigarettes by region", 4)
```

<br>

**Analysis information**:

- Questions used: ET1
- R script name: ETStatus

***

**E-cigarettes usage status**

Description: E-cigarettes smoking status of all respondents.

Instrument questions:

- Do you currently use electronic cigarettes?
- Do you currently use electronic cigarettes daily?

```{r etstatus_c_tbls}

# column names to use with huxtable
etstatus_c_col_names <- c("Age Group (years)", "n", "% Daily", "95% CI",
                          "% Non-daily", "95% CI", "% Former user or never used", "95% CI")
etstatus_c_reg_col_names <- c("Region", "n", "% Daily", "95% CI",
                              "% Non-daily", "95% CI", "% Former user or never used", "95% CI")

# men, women, both sexes
etstatus_c_m_w_b <- join_tbls(etstatus_c, m_w_b, 3, etstatus_c_col_names)
```
```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# urban, rural
etstatus_c_u_r <- join_tbls(etstatus_c, u_r, 3, etstatus_c_col_names)
```

<br>

```{r}
etstatus_c_m_w_b$m %>% final_tbl(m_w_b, 1, "Men", "E-cigarettes usage status", 8) %>% 
  insert_row(c("","","Current user","","","","Non user",""), after = 2) %>% 
  merge_cells(row = 3, col = c(7:8)) %>% merge_cells(row = 3, col = c(3:6)) %>% 
  set_right_border(row = 3, col = c(1:6), value = 0)
```

<br>

```{r}
etstatus_c_m_w_b$w %>% final_tbl(m_w_b, 1, "Women", "E-cigarettes usage status", 8) %>% 
  insert_row(c("","","Current user","","","","Non user",""), after = 2) %>% 
  merge_cells(row = 3, col = c(7:8)) %>% merge_cells(row = 3, col = c(3:6)) %>% 
  set_right_border(row = 3, col = c(1:6), value = 0)
```

<br>

```{r}
etstatus_c_m_w_b$b %>% final_tbl(m_w_b, 1, "Both sexes", "E-cigarettes usage status", 8) %>% 
  insert_row(c("","","Current user","","","","Non user",""), after = 2) %>% 
  merge_cells(row = 3, col = c(7:8)) %>% merge_cells(row = 3, col = c(3:6)) %>% 
  set_right_border(row = 3, col = c(1:6), value = 0)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
rbind(etstatus_c_u_r$m_u, etstatus_c_u_r$m_r) %>% 
  final_tbl(u_r, 1, "Men", "E-cigarettes usage status by type of settlement", 8) %>% 
  insert_row(c("","","Current user","","","","Non user",""), after = 2) %>% 
  merge_cells(row = 3, col = c(7:8)) %>% merge_cells(row = 3, col = c(3:6)) %>% 
  set_right_border(row = 3, col = c(1:6), value = 0)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
rbind(etstatus_c_u_r$w_u, etstatus_c_u_r$w_r) %>% 
  final_tbl(u_r, 1, "Women", "E-cigarettes usage status by type of settlement", 8) %>% 
  insert_row(c("","","Current user","","","","Non user",""), after = 2) %>% 
  merge_cells(row = 3, col = c(7:8)) %>% merge_cells(row = 3, col = c(3:6)) %>% 
  set_right_border(row = 3, col = c(1:6), value = 0)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
rbind(etstatus_c_u_r$b_u, etstatus_c_u_r$b_r) %>% 
  final_tbl(u_r, 1, "Both sexes", "E-cigarettes usage status by type of settlement", 8) %>% 
  insert_row(c("","","Current user","","","","Non user",""), after = 2) %>% 
  merge_cells(row = 3, col = c(7:8)) %>% merge_cells(row = 3, col = c(3:6)) %>% 
  set_right_border(row = 3, col = c(1:6), value = 0)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# region
etstatus_c$b_reg %>% unite_ci(.ci_amount = 3) %>% apply_hux(.col_names = etstatus_c_reg_col_names) %>% 
  final_tbl(reg, 1, "Both sexes", "E-cigarettes usage status by region", 8) %>% 
  insert_row(c("","","Current user","","","","Non user",""), after = 2) %>% 
  merge_cells(row = 3, col = c(7:8)) %>% merge_cells(row = 3, col = c(3:6)) %>% 
  set_right_border(row = 3, col = c(1:6), value = 0)
```

<br>

**Analysis information**:

- Questions used: ET1, ET2
- R script name: ETStatus

***

**Daily e-cigarettes usage**

Description: Percentage of current daily users among users.

Instrument questions:

- Do you currently use electronic cigarettes?
- Do you currently use electronic cigarettes daily?

```{r etsmokefreq_c_tbls}

# column names to use with huxtable
etsmokefreq_c_col_names <- c("Age Group (years)", "n", "% Daily users", "95% CI")
etsmokefreq_c_reg_col_names <- c("Region", "n", "% Daily users", "95% CI")

# men, women, both sexes
etsmokefreq_c_m_w_b <- join_tbls(etsmokefreq_c, m_w_b, 1, etsmokefreq_c_col_names)
```
```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# urban, rural
etsmokefreq_c_u_r <- join_tbls(etsmokefreq_c, u_r, 1, etsmokefreq_c_col_names)
```

<br>

```{r}
cbind(etsmokefreq_c_m_w_b$m, select(etsmokefreq_c_m_w_b$w, -agerange), select(etsmokefreq_c_m_w_b$b, -agerange)) %>% 
  final_tbl(.disaggregation = m_w_b, .s_amount = 3, .title = "Current daily users among e-cigarettes users", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
tbl_m_u_r <- rbind(etsmokefreq_c_u_r$m_u, etsmokefreq_c_u_r$m_r)
tbl_w_u_r <- rbind(etsmokefreq_c_u_r$w_u, etsmokefreq_c_u_r$w_r)
tbl_b_u_r <- rbind(etsmokefreq_c_u_r$b_u, etsmokefreq_c_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_tbl(.disaggregation = u_r, .s_amount = 3, .title = "Current daily users among e-cigarettes users by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
etsmokefreq_c$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = etsmokefreq_c_reg_col_names) %>% 
  final_tbl(reg, 1, "Both sexes", "Current daily users among e-cigarettes users by region", 4)
```

<br>

**Analysis information**:

- Questions used: ET1, ET2
- R script name: ETSmokefreq

***

**Initiation and duration of using e-cigarettes**

Description: Mean age of initiation and mean duration of using, in years, among daily users (no total age group for mean duration of using as age influences these values).

Instrument questions:

- Do you currently use electronic cigarettes?
- Do you currently use electronic cigarettes daily?
- How old were you when you first started using electronic cigarettes?
- Do you remember how long ago it was?

```{r etsmokeagetime_initiation_duration_tbls}

# column names to use with huxtable
etsmokeagetime_initiation_col_names <- c("Age Group (years)", "n", "Mean age", "95% CI")
etsmokeagetime_initiation_reg_col_names <- c("Region", "n", "Mean age", "95% CI")
etsmokeagetime_duration_col_names <- c("Age Group (years)", "n", "Mean duration", "95% CI")
etsmokeagetime_duration_reg_col_names <- c("Region", "n", "Mean duration", "95% CI")

# INITIATION PART
# men, women, both sexes
etsmokeagetime_initiation_m_w_b <- join_tbls(etsmokeagetime_initiation, m_w_b, 1, etsmokeagetime_initiation_col_names)

# DURATION PART
# men, women, both sexes
etsmokeagetime_duration_m_w_b <- join_tbls(etsmokeagetime_duration, m_w_b, 1, etsmokeagetime_duration_col_names)
```
```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# urban, rural
etsmokeagetime_initiation_u_r <- join_tbls(etsmokeagetime_initiation, u_r, 1, etsmokeagetime_initiation_col_names)
# urban, rural
etsmokeagetime_duration_u_r <- join_tbls(etsmokeagetime_duration, u_r, 1, etsmokeagetime_duration_col_names)
```

<br>

```{r}
cbind(etsmokeagetime_initiation_m_w_b$m, select(etsmokeagetime_initiation_m_w_b$w, -agerange), select(etsmokeagetime_initiation_m_w_b$b, -agerange)) %>% final_tbl(.disaggregation = m_w_b, .s_amount = 3, .title = "Mean age started using e-cigarettes", .colspan_val = 10)
```

<br>

```{r}
cbind(etsmokeagetime_duration_m_w_b$m, select(etsmokeagetime_duration_m_w_b$w, -agerange), select(etsmokeagetime_duration_m_w_b$b, -agerange)) %>% final_tbl(.disaggregation = m_w_b, .s_amount = 3, .title = "Mean duration of using e-cigarettes", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
tbl_m_u_r <- rbind(etsmokeagetime_initiation_u_r$m_u, etsmokeagetime_initiation_u_r$m_r)
tbl_w_u_r <- rbind(etsmokeagetime_initiation_u_r$w_u, etsmokeagetime_initiation_u_r$w_r)
tbl_b_u_r <- rbind(etsmokeagetime_initiation_u_r$b_u, etsmokeagetime_initiation_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_tbl(.disaggregation = u_r, .s_amount = 3, .title = "Mean age started using e-cigarettes by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
tbl_m_u_r <- rbind(etsmokeagetime_duration_u_r$m_u, etsmokeagetime_duration_u_r$m_r)
tbl_w_u_r <- rbind(etsmokeagetime_duration_u_r$w_u, etsmokeagetime_duration_u_r$w_r)
tbl_b_u_r <- rbind(etsmokeagetime_duration_u_r$b_u, etsmokeagetime_duration_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_tbl(.disaggregation = u_r, .s_amount = 3, .title = "Mean duration of using e-cigarettes by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
etsmokeagetime_initiation$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = etsmokeagetime_initiation_reg_col_names) %>% final_tbl(reg, 1, "Both sexes", "Mean age started using e-cigarettes by region", 4)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
etsmokeagetime_duration$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = etsmokeagetime_duration_reg_col_names) %>% final_tbl(reg, 1, "Both sexes", "Mean duration of using e-cigarettes by region", 4)
```
<br>

**Analysis information**:

- Questions used: ET1, ET2, ET3, ET4
- R script name: ETSmokeagetime

***


**Current heated tobacco products usage**

Description: Percentage of current users of heated tobacco products among all respondents.

Instrument questions:

- Do you currently use heated tobacco products?

```{r htstatus_d_tbls}

# column names to use with huxtable
htstatus_d_col_names <- c("Age Group (years)", "n", "% Current users", "95% CI")
htstatus_d_reg_col_names <- c("Region", "n", "% Current users", "95% CI")

# men, women, both sexes
htstatus_d_m_w_b <- join_tbls(htstatus_d, m_w_b, 1, htstatus_d_col_names)
```
```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# urban, rural
htstatus_d_u_r <- join_tbls(htstatus_d, u_r, 1, htstatus_d_col_names)
```

<br>

```{r}
cbind(htstatus_d_m_w_b$m, select(htstatus_d_m_w_b$w, -agerange), select(htstatus_d_m_w_b$b, -agerange)) %>% 
  final_tbl(.disaggregation = m_w_b, .s_amount = 3, .title = "Percentage of current users of heated tobacco products", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
tbl_m_u_r <- rbind(htstatus_d_u_r$m_u, htstatus_d_u_r$m_r)
tbl_w_u_r <- rbind(htstatus_d_u_r$w_u, htstatus_d_u_r$w_r)
tbl_b_u_r <- rbind(htstatus_d_u_r$b_u, htstatus_d_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_tbl(.disaggregation = u_r, .s_amount = 3, .title = "Percentage of current users of heated tobacco products by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
htstatus_d$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = htstatus_d_reg_col_names) %>% 
  final_tbl(reg, 1, "Both sexes", "Percentage of current users of heated tobacco products by region", 4)
```

<br>

**Analysis information**:

- Questions used: HTP1
- R script name: HTStatus

***

**Heated tobacco products usage status**

Description: Heated tobacco products smoking status of all respondents.

Instrument questions:

- Do you currently use heated tobacco products?
- Do you currently use heated tobacco products daily?

```{r htstatus_c_tbls}

# column names to use with huxtable
htstatus_c_col_names <- c("Age Group (years)", "n", "% Daily", "95% CI",
                          "% Non-daily", "95% CI", "% Former user or never used", "95% CI")
htstatus_c_reg_col_names <- c("Region", "n", "% Daily", "95% CI",
                              "% Non-daily", "95% CI", "% Former user or never used", "95% CI")

# men, women, both sexes
htstatus_c_m_w_b <- join_tbls(htstatus_c, m_w_b, 3, htstatus_c_col_names)
```
```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# urban, rural
htstatus_c_u_r <- join_tbls(htstatus_c, u_r, 3, htstatus_c_col_names)
```

<br>

```{r}
htstatus_c_m_w_b$m %>% final_tbl(m_w_b, 1, "Men", "Heated tobacco products usage status", 8) %>% 
  insert_row(c("","","Current user","","","","Non user",""), after = 2) %>% 
  merge_cells(row = 3, col = c(7:8)) %>% merge_cells(row = 3, col = c(3:6)) %>% 
  set_right_border(row = 3, col = c(1:6), value = 0)
```

<br>

```{r}
htstatus_c_m_w_b$w %>% final_tbl(m_w_b, 1, "Women", "Heated tobacco products usage status", 8) %>% 
  insert_row(c("","","Current user","","","","Non user",""), after = 2) %>% 
  merge_cells(row = 3, col = c(7:8)) %>% merge_cells(row = 3, col = c(3:6)) %>% 
  set_right_border(row = 3, col = c(1:6), value = 0)
```

<br>

```{r}
htstatus_c_m_w_b$b %>% final_tbl(m_w_b, 1, "Both sexes", "Heated tobacco products usage status", 8) %>% 
  insert_row(c("","","Current user","","","","Non user",""), after = 2) %>% 
  merge_cells(row = 3, col = c(7:8)) %>% merge_cells(row = 3, col = c(3:6)) %>% 
  set_right_border(row = 3, col = c(1:6), value = 0)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
rbind(htstatus_c_u_r$m_u, htstatus_c_u_r$m_r) %>% 
  final_tbl(u_r, 1, "Men", "Heated tobacco products usage status by type of settlement", 8) %>% 
  insert_row(c("","","Current user","","","","Non user",""), after = 2) %>% 
  merge_cells(row = 3, col = c(7:8)) %>% merge_cells(row = 3, col = c(3:6)) %>% 
  set_right_border(row = 3, col = c(1:6), value = 0)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
rbind(htstatus_c_u_r$w_u, htstatus_c_u_r$w_r) %>% 
  final_tbl(u_r, 1, "Women", "Heated tobacco products usage status by type of settlement", 8) %>% 
  insert_row(c("","","Current user","","","","Non user",""), after = 2) %>% 
  merge_cells(row = 3, col = c(7:8)) %>% merge_cells(row = 3, col = c(3:6)) %>% 
  set_right_border(row = 3, col = c(1:6), value = 0)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
rbind(htstatus_c_u_r$b_u, htstatus_c_u_r$b_r) %>% 
  final_tbl(u_r, 1, "Both sexes", "Heated tobacco products usage status by type of settlement", 8) %>% 
  insert_row(c("","","Current user","","","","Non user",""), after = 2) %>% 
  merge_cells(row = 3, col = c(7:8)) %>% merge_cells(row = 3, col = c(3:6)) %>% 
  set_right_border(row = 3, col = c(1:6), value = 0)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# region
htstatus_c$b_reg %>% unite_ci(.ci_amount = 3) %>% apply_hux(.col_names = htstatus_c_reg_col_names) %>% 
  final_tbl(reg, 1, "Both sexes", "Heated tobacco products usage status by region", 8) %>% 
  insert_row(c("","","Current user","","","","Non user",""), after = 2) %>% 
  merge_cells(row = 3, col = c(7:8)) %>% merge_cells(row = 3, col = c(3:6)) %>% 
  set_right_border(row = 3, col = c(1:6), value = 0)
```

<br>

**Analysis information**:

- Questions used: HTP1, HTP2
- R script name: HTStatus

***

**Daily heated tobacco products usage**

Description: Percentage of current daily users among users.

Instrument questions:

- Do you currently use heated tobacco products?
- Do you currently use heated tobacco products daily?

```{r htsmokefreq_c_tbls}

# column names to use with huxtable
htsmokefreq_c_col_names <- c("Age Group (years)", "n", "% Daily users", "95% CI")
htsmokefreq_c_reg_col_names <- c("Region", "n", "% Daily users", "95% CI")

# men, women, both sexes
htsmokefreq_c_m_w_b <- join_tbls(htsmokefreq_c, m_w_b, 1, htsmokefreq_c_col_names)
```
```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# urban, rural
htsmokefreq_c_u_r <- join_tbls(htsmokefreq_c, u_r, 1, htsmokefreq_c_col_names)
```

<br>

```{r}
cbind(htsmokefreq_c_m_w_b$m, select(htsmokefreq_c_m_w_b$w, -agerange), select(htsmokefreq_c_m_w_b$b, -agerange)) %>% 
  final_tbl(.disaggregation = m_w_b, .s_amount = 3, .title = "Current daily users among heated tobacco products users", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
tbl_m_u_r <- rbind(htsmokefreq_c_u_r$m_u, htsmokefreq_c_u_r$m_r)
tbl_w_u_r <- rbind(htsmokefreq_c_u_r$w_u, htsmokefreq_c_u_r$w_r)
tbl_b_u_r <- rbind(htsmokefreq_c_u_r$b_u, htsmokefreq_c_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_tbl(.disaggregation = u_r, .s_amount = 3, .title = "Current daily users among heated tobacco products users by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
htsmokefreq_c$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = htsmokefreq_c_reg_col_names) %>% 
  final_tbl(reg, 1, "Both sexes", "Current daily users among heated tobacco products users by region", 4)
```

<br>

**Analysis information**:

- Questions used: HTP1, HTP2
- R script name: HTSmokefreq

***

**Initiation and duration of using heated tobacco products**

Description: Mean age of initiation and mean duration of using, in years, among daily users (no total age group for mean duration of using as age influences these values).

Instrument questions:

- Do you currently use heated tobacco products?
- Do you currently use heated tobacco products daily?
- How old were you when you first started using heated tobacco products?
- Do you remember how long ago it was?

```{r htsmokeagetime_initiation_duration_tbls}

# column names to use with huxtable
htsmokeagetime_initiation_col_names <- c("Age Group (years)", "n", "Mean age", "95% CI")
htsmokeagetime_initiation_reg_col_names <- c("Region", "n", "Mean age", "95% CI")
htsmokeagetime_duration_col_names <- c("Age Group (years)", "n", "Mean duration", "95% CI")
htsmokeagetime_duration_reg_col_names <- c("Region", "n", "Mean duration", "95% CI")

# INITIATION PART
# men, women, both sexes
htsmokeagetime_initiation_m_w_b <- join_tbls(htsmokeagetime_initiation, m_w_b, 1, htsmokeagetime_initiation_col_names)

# DURATION PART
# men, women, both sexes
htsmokeagetime_duration_m_w_b <- join_tbls(htsmokeagetime_duration, m_w_b, 1, htsmokeagetime_duration_col_names)
```
```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# urban, rural
htsmokeagetime_initiation_u_r <- join_tbls(htsmokeagetime_initiation, u_r, 1, htsmokeagetime_initiation_col_names)
# urban, rural
htsmokeagetime_duration_u_r <- join_tbls(htsmokeagetime_duration, u_r, 1, htsmokeagetime_duration_col_names)
```

<br>

```{r}
cbind(htsmokeagetime_initiation_m_w_b$m, select(htsmokeagetime_initiation_m_w_b$w, -agerange), select(htsmokeagetime_initiation_m_w_b$b, -agerange)) %>% final_tbl(.disaggregation = m_w_b, .s_amount = 3, .title = "Mean age started using heated tobacco products", .colspan_val = 10)
```

<br>

```{r}
cbind(htsmokeagetime_duration_m_w_b$m, select(htsmokeagetime_duration_m_w_b$w, -agerange), select(htsmokeagetime_duration_m_w_b$b, -agerange)) %>% final_tbl(.disaggregation = m_w_b, .s_amount = 3, .title = "Mean duration of using heated tobacco products", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
tbl_m_u_r <- rbind(htsmokeagetime_initiation_u_r$m_u, htsmokeagetime_initiation_u_r$m_r)
tbl_w_u_r <- rbind(htsmokeagetime_initiation_u_r$w_u, htsmokeagetime_initiation_u_r$w_r)
tbl_b_u_r <- rbind(htsmokeagetime_initiation_u_r$b_u, htsmokeagetime_initiation_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_tbl(.disaggregation = u_r, .s_amount = 3, .title = "Mean age started using heated tobacco products by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
tbl_m_u_r <- rbind(htsmokeagetime_duration_u_r$m_u, htsmokeagetime_duration_u_r$m_r)
tbl_w_u_r <- rbind(htsmokeagetime_duration_u_r$w_u, htsmokeagetime_duration_u_r$w_r)
tbl_b_u_r <- rbind(htsmokeagetime_duration_u_r$b_u, htsmokeagetime_duration_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_tbl(.disaggregation = u_r, .s_amount = 3, .title = "Mean duration of using heated tobacco products by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
htsmokeagetime_initiation$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = htsmokeagetime_initiation_reg_col_names) %>% final_tbl(reg, 1, "Both sexes", "Mean age started using heated tobacco products by region", 4)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
htsmokeagetime_duration$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = htsmokeagetime_duration_reg_col_names) %>% final_tbl(reg, 1, "Both sexes", "Mean duration of using heated tobacco products by region", 4)
```
<br>

**Analysis information**:

- Questions used: HTP1, HTP2, HTP3, HTP4
- R script name: HTSmokeagetime

***


<br>
<br>
